### 2022-10-10 Manuscript/manuscript.tex
set flow in intro

\documentclass[12pt, letterpaper, titlepage]{article}

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{setspace}

\usepackage[pagewise]{lineno}
%\linenumbers*[1]
% %% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
 \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
 \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
 \renewenvironment{#1}%
 {\linenomath\csname old#1\endcsname}%
 {\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
 \patchAmsMathEnvironmentForLineno{#1}%
 \patchAmsMathEnvironmentForLineno{#1*}}%

\AtBeginDocument{%
 \patchBothAmsMathEnvironmentsForLineno{equation}%
 \patchBothAmsMathEnvironmentsForLineno{align}%
 \patchBothAmsMathEnvironmentsForLineno{flalign}%
 \patchBothAmsMathEnvironmentsForLineno{alignat}%
 \patchBothAmsMathEnvironmentsForLineno{gather}%
 \patchBothAmsMathEnvironmentsForLineno{multline}%
}

% control floats
\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}

\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}

\title{On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit}

\author{Anthony Zeimbekakis\\
%   \href{mailto:anthony.zeimbekakis@uconn.edu}
% {\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
  Elizabeth Schifano\\
  Jun Yan\\[1ex]
  Department of Statistics, University of Connecticut\\
}
\date{}

\begin{document}
\maketitle

\doublespace

\begin{abstract}
The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit
tests for comparing a sample with a hypothesized parametric distribution.
Nevertheless, it has often been misused. The standard one-sample KS test applies
to independent, continuous data with a hypothesized distribution that is
completely specified. It is not uncommon, however, to see in the literature that
it was applied to dependent, discrete, or rounded data, with hypothesized
distributions containing estimated parameters. For example, it has been
``discovered'' multiple times that the test is too conservative when
hypothesized distribution has parameters that need to be estimated.
We demonstrate misuses of the one-sample KS test in
three scenarios through simulation studies:
1) the hypothesized distribution has unspecified parameters;
2) the data are serially dependent; and
3) a combination of the first two scenarios.
For each scenario, we provide remedies for practical applications.

\bigskip
\noindent\sc{Keywords}:
nonparametric bootstrap;
parametric bootstrap;
\end{abstract}

\section{Introduction}
\label{sec:intro}

The Kolmogorov-Smirnov (KS) test is one of the most popular goodness-of-fit
tests for comparing a sample with a hypothesized parametric distribution.
Let $X_1, ..., X_n$ be a random sample of size~$n$ from a continuous
distribution. The null hypothesis $H_0$ is that $X_i$'s follow distribution~$F$.
Let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function. The KS test statistic is
\begin{equation}
  \label{eq:ks_standard}
  D_n = \sup_x | F_{n}(x) - F(x) |.
\end{equation}
The asymptotic distribution of $D_n$ under $H_0$ is independent of the
distribution $F$. As $n \to \infty$, $\sqrt{n} D_n$ converges in distribution to
the supremum of standard Brownian bridge \citep{kolmogorov1933sulla}. For large
samples, the tests can be performed with a table \citep{smirnov1948table}.
Critical values for small samples ($n \le 35$) has also been given
\citep{Massey}. The KS test is available in popular
statistical software packages, such as function \texttt{ks.test} in R package
\textsf{stats} \citep{R, Marsaglia}.

The standard one-sample KS test applies to independent data with a continuous
hypothesized distribution that is completely specified. In practice, however, it
has often been applied without realizing that one or more of these assumptions
do not hold. For example, \citet{Noether} demonstrated the conservativeness of
the KS test when applied to discontinuous distributions. The null distribution
of the KS statistic is no longer distribution free. Computing the
exact and asymptotic distribution of $D_n$ is challenging. Fortunately, the null
distribution of the KS statistic when the underlying distribution is
discontinuous has been efficiently addressed by \citet{Dimitrova} with an
companion R package \textsf{KSgeneral}. Although a common misuse of KS test, the
issue with discontinuous or data is not our focus.

The standard KS test is not applicable when the hypothesized distribution
contains fitted parameters. \citet{Steinskog} ``discovers'' the change in power
when using estimated parameters and stresses caution in using the KS test in
such ways. In fact, \citet{Lilliefors} shows for the normal distribution that using the
standard table when values of the mean and standard deviation are estimated
yields extremely conservative results.
% JY: this paper set up a wrong target; they didn't even cite bootstrap!
% This is supported by \citet{Capasso},
% who concludes that failing to re-estimate the parameters may lead to wrong,
% overly-conservative approximations to the distributions of goodness-of-fit test
% statistics based on the empirical distribution function. \citet{Capasso} also
% notes that the impact of this mistake may turn out to be dramatic and does not
% vanish as the sample size increases.
This problem can be solved by parametric bootstrap \citep{Efron}, where
bootstrap samples of the testing statistics are constructed from samples
generated from the fitted hypothesized distribution. A nonparametric bootstrap
solution is not trivial because the a nonparametric bootstrap sample of the
observed data have ties, which would not happen for continuous distribution.
A nonparametric remedy was provided by \citet{Babu}, who derived the bias and
showed how to correct it. They further noted that both parametric and
non-parametric procedures lead to correct asymptotic levels.
% JY: Genest at al is not about our setting. \citet{Genest} provides
% validity for using parametric bootstrap with various goodness-of-fit tests.

The standard KS test does not apply to serially dependent data either. For
testing normality, \citet{Durilleul} demonstrated that a naive application of
the KS statistic is too liberal for medium-to-high positive serieal dependence,
and that for negative dependence, the behavior is asymmetrical. For remedies,
\citet{Weiss} provides a procedure that is applicable specifically for data
modeled by the second-order auto-regressive (AR) process where the AR parameters
are known. \citet{Lanzante} tests various strategies for dealing with temporal
dependence and concludes that a test based on Monte-Carlo simulations performed
the best. \jy{need some sentences to elaborate the issue and identify a gap in
  the literature.}

The contribution of this paper is a demonstration of misuses of the one-sample
KS test in three scenarios and their remedies in practice. The scenarios are
where:
1) the hypothesized distribution has unspecified parameters;
2) the data are serially dependent; and
3) a combination of the first two scenarios.
In each scenario, the misuse is performed and the impacts are shown. Then, a
remedy is detailed and performed alongside the misuse to show its positive
effects. In order to set up the demonstrations, simulated data is used
throughout. The remedies are also performed on various families of
distributions.

The rest of the paper is organized as follows. Section~\ref{sec:fitted}
investigates the scenario where the hypothesized distribution has unspecified
parameters. Both parametric and nonparametric bootstrap are available to fix the
issue. Section~\ref{sec:dependence} investigates the scenario where the data of
the empirical distribution is serially dependent. A bootstrap procedure
employing copulas to account for dependence is proposed as a working solution.
Section~\ref{sec:fittedwithdependence}
explores the case where a combination of the first two scenarios occurs. The
copula procedure can be adjusted for the use of fitted parameters as a remedy.
Section~\ref{sec:conclusion} concludes with a discussion.

\section{Unspecified Parameters}
\label{sec:fitted}

The null distribution of the KS statistic changes when the hypothesized
distribution contains fitted parameters.
\eds{what is the null distribution when not using fitted parameters}.
In this scenario, the null hypothesis
is $H_0$: the random sample $X_1, \ldots, X_n$ comes from a continuous
distribution $F_{\theta}$ with unspecified parameter vector $\theta$.
Let $\hat\theta_n$ be an estimator of $\theta$, which could be, for example, a
maximum likelihood estimator or moment estimator. The test statistic is
\begin{equation}
  \label{eq:ks_fitted}
  D = \sup_x | F_n(x) - F_{\hat\theta_n}(x) |.
\end{equation}
Since $F_{\hat\theta_n}$ is not the same as the true data generating
$F_\theta$, the null distribution of $D$ obtained in existing implementations in
software packages which assumes completely known $F_\theta$ no longer applies
\citep{Steinskog}.

To demonstrate the consequences of this problem, a simulation is performed. A
random sample $X_1, \ldots, X_n$ is generated from the standard normal
distribution with sample size $n = 100$. The p-values of $1000$ replicate tests
 of normality
are displayed in the Naive plot of Figure~\ref{fig:hist_fitted}.
\eds{how are these p-values calculated?}
Each KS test
was performed using fitted parameters, i.e., the hypothesized distribution is
$N(\bar X, s^2)$ where $\bar X$ is the sample mean and $s^2$ is the sample
variance. Since the data is truly generated from a standard normal distribution,
 %with
%seemingly all assumptions met,
a uniform distribution of $U(0, 1)$ would naively be expected for the p-values.
However this should only be expected when the KS test assumptions hold, and they
 do not due to using fitted parameters. Therefore,
there is notable deviation from the uniform distribution.

To fix the problem, parametric bootstrap can be used to approximate the null
distribution of the testing statistic.
\begin{enumerate}
  \item
    Draw a random sample $X_1^*,...,X_n^*$ from the fitted distribution
    $F_{\hat\theta_n}$
  \item
    Fit $F_\theta$ to the sample and obtain estimated $\hat\theta_n^*$
  \item
    Obtain the empirical distribution function $F_n^*$ of $X_1^*, \ldots,
    X_n^*$.
  \item
    Calculate bootstrap KS statistic
    \[
      D^* = \sup_x | F_n^* (x)- F_{\hat\theta_n}^*(x) |.
    \]
  \item
    Repeat the previous steps a large number $B$ times and use the empirical
    distribution of $D^*$ to approximate the null distribution of the observed
    statistic.
\end{enumerate}

Nonparametric bootstrap can also be used to approximate the null distribution
of the testing statistic. The procedure is similar, however the resampling is
performed with the empirical distribution instead of the fitted parametric
distribution and there is a correction for bias that is required
\citep{Babu}.
\begin{enumerate}
  \item
    Draw a random sample $X_1^*,...,X_n^*$ from the empirical distribution $F_n$
    with replacement
  \item
    Fit $F_\theta$ to the sample and obtain estimated $\hat\theta_n^*$
  \item
    Obtain the empirical distribution function of the random sample $F_n^*$
  \item
    Calculate bootstrap KS statistic
    \[
      D^* = \sup_x | F_n^* (x)- F_{\hat\theta_n}^*(x) - B_n(x) |.
    \]
    where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
    bias term \citep{Babu}
  \item
    Repeat the previous steps a large number $B$ times and use the empirical
    distribution of $D^*$ to approximate the null distribution of the observed
    statistic.
\end{enumerate}
The p-value can be calculated by counting the number of bootstrap KS
statistics greater than or equal to the observed KS statistic, and then dividing
by the number of bootstrap samples. Figure~\ref{fig:hist_fitted} displays the
results of from our simulations. We would expect the distribution of p-values
to be uniform in the case where the KS test holds its size. It is clear from the
figure that both parametric and nonparametric bootstrap processes correct for
the problem of fitted parameters. The plots for the bootstrapped p-values appear
to be $U(0,1)$, unlike the naive p-values.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_fitted}
  \caption{The Naive plot (left) is the histogram of p-values from the standard
  KS test with fitted parameters. The Parametric plot (middle) is the histogram
  of p-values from implementing parametric bootstrap. The Babu plot (right) is
  the histogram of p-values from implementing nonparametric bootstrap with a
  correction for bias. In each case, $1000$ replicate tests were performed on
  the standard normal distribution with sample size $n = 100$. $B = 1000$
  bootstrap samples are obtained for each test. \eds{perhaps use density hist vs
	freq. hist (here and elsewhere)?}}
  \label{fig:hist_fitted}
\end{figure}

\section{Serially Dependent Data}
\label{sec:dependence}

The KS test also displays issues in the case of dependent data. As mentioned, an
assumption of the test is that the data is independent. Real data, however,
is often temporally or spatially dependent and the results of a goodness-of-fit
test would be valuable. When the KS test is performed on dependent data it
performs poorly. In this situation, the null hypothesis is $H_0$: the random
sample $X_1, \ldots, X_n$ come from a continuous distribution $F$ where $F$ has
completely specified parameters. The test statistic is the same as
Equation~\eqref{eq:ks_standard}. However, since the data is dependent, the null
hypothesis is wrong and must be corrected.
\eds{null hypothesis or null distribution? or both?}
This is demonstrated with a
simulation in Figure~\ref{fig:hist_correlation}. Data is generated from a
first-order autoregressive model (AR(1)) with a standard normal distribution.
P-values are gathered from $1000$ replicate tests for different levels of the
AR coefficient $\psi$, varying from $(-3,3)$.
\eds{how are these p-values calculated?}
In the presence of serially
dependent data, the distribution of p-values no longer follows $U(0, 1)$ as
would be expected of a valid test. The results echo those of \citet{Durilleul}
that the KS statistic is too liberal in the presence of positive
autocorrelation, and that the behavior is asymmetrical for negative
 autocorrelation.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_correlation}
  \caption{Each histogram is a plot of the p-values of standard KS tests
  performed on dependent data simulated from an AR(1) process of the standard
  normal distribution. The titles represent the various levels of the AR
  coefficient $\psi$ tested. The sample size is $n = 100$ and $1000$ replicate
  tests were performed for each AR coefficient.}
  \label{fig:hist_correlation}
\end{figure}

In order to correct this, we can employ a parametric bootstrap procedure which
assumes a working serial dependence structure through copulas. A copula is a
multivariate distribution with standard uniform marginal distributions, which
completely characterizes the dependence structure of a multivariate
distribution \citep{Copula, Hofert}. For simplicity, we assume a normal copula
with an AR(1) structure to characterize the serial dependence of the
observations. The AR(1) parameter $r$ of the normal copula is set to match the
sample serial Spearman's rho of the observed data.
\eds{What is the difference between $\psi$ and $r$?}
The procedure is as
follows.

\begin{enumerate}
\item
  Generate $Z_1, \ldots, Z_n$ from an AR(1) process with autocorrelation
  coefficient $r$ such that the $Z_i$'s are $N(0, 1)$ variables.
\item
  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i)]$, where $\Phi$ is the
  distribution function of $N(0, 1)$, $i = 1, \ldots, n$, whose first-order
  sample Spearman's rho matches that of the observed data.
\item
  Obtain the empirical distribution function $F_n^*$ of the bootstrap sample
  $X_1^*, \ldots, X_n^*$.
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x \lvert F_n^* (x)- F(x) \rvert.
  \]
\item
  Repeat the previous steps a large number $B$ times and use the empirical
    distribution of the $B$ test statistics to approximate
    the null distribution of the observed statistic.
\end{enumerate}

Throughout the simulation we assume a working AR(1) dependence structure
regardless of the true dependence. If the true dependence is indeed a normal
copula with an AR(1) structure, this method is exact. When the true dependence
is not AR(1), it may still give a reasonable approximation that can be useful
for practical purposes. This is demonstrated with different dependence
structures in Figure~\ref{fig:hist_ma1_arma_ar2_D}.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_ar1_D}
  \caption{The Naive plot (left) is the histogram of p-values from the
  standard KS test. The Copula plot (right) is the histogram of p-values from
  implementing parametric bootstrap with copulas for dependence. In each case,
  $1000$ replicate tests were performed with the data generated from an AR(1)
  process of the standard normal distribution with $\psi = .5$. The sample size
  is $n = 100$ and $B = 1000$ bootstrap samples are obtained for each test.}
  \label{fig:hist_ar1_D}
\end{figure}

Figure~\ref{fig:hist_ar1_D} displays the results of the copula remedy for
dependent data. The data is generated from the standard normal distribution with
an AR(1) dependence structure where $\psi = .5$. The copula used is to model
dependence is the normal copula. The distribution of p-values is again expected
to be $U(0, 1)$ for a valid test. The Naive plot is clearly not uniform and
reinforces the results shown in Figure~\ref{fig:hist_correlation}. The Copula
plot, which implements the aforementioned procedure to correct for dependence
in the data, appears to be uniform and restores the size of the KS test.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_ma1_arma_ar2_D}
  \caption{The Naive plots are the histograms of p-values from the standard KS
  test. The Copula plots are the histograms of p-values from parametric
  bootstrap with copulas for dependence. The data is generated from an MA(1)
  process (left) with $\theta = .5$, ARMA(1, 1) process (middle) with $\psi =
  .5$ and $\theta = .3$, and AR(2) process (right) with $\psi = (.5, .3)$ of the
  standard normal distribution. In each case, $1000$ replicate tests were
  performed with sample size $n = 100$ and $B = 1000$ bootstrap samples.}
  \label{fig:hist_ma1_arma_ar2_D}
\end{figure}

The procedure detailed in this section can also provide a reasonable
approximation in cases where the true dependence structure is not far from
AR(1). Figure~\ref{fig:hist_ma1_arma_ar2_D} shows the distribution of p-values
for dependence structures MA(1), ARMA(1, 1), and AR(2). As expected,
naively performing the KS test without correcting for dependence provides plots
of p-values that deviate from the uniform distribution. In the case of MA(1)
and ARMA(1, 1), the true dependence structure is close enough to our
assumption of AR(1) that the bootstrap procedure provides a reasonable
approximation. However, the AR(2) copula plot shows the limitation of this
technique as no AR(1) process can approximate an AR(2) process unless the
second-order coefficient is close to zero.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_gamma_gev_D}
  \caption{The Naive plots are the histograms of p-values from the standard KS
  test. The Copula plots are the histograms of p-values from parametric
  bootstrap with copulas for dependence. The data is generated from $Gamma(3,
  1)$ (left) and $GEV(0, .2, 1)$ (right) with a correlation coefficient of $r =
  0.5$. In each case, $1000$ replicate tests were performed with sample size $n
  = 100$ and $B = 1000$ bootstrap samples.}
  \label{fig:hist_gamma_gev_D}
\end{figure}

To further demonstrate the effectiveness of the procedure, we perform similar
simulations on other families of distributions.
Figure~\ref{fig:hist_gamma_gev_D} displays the results of tests using dependent
data generated from the gamma and the generalized extreme value distributions.
The procedure corrects the distribution of p-values for both distributions and
is shown to be applicable regardless of the family of distribution tested.

\section{Unspecified Parameters and Serially Dependent Data}
\label{sec:fittedwithdependence}

The procedure demonstrated in Section~\ref{sec:dependence} works when the data
is dependent and the hypothesized distribution is completely specified. However,
this is not practical. In practice we do not know the parameters of the
hypothesized distribution. Therefore, it is valuable to have a procedure that
corrects for both fitted parameters and serially dependent data. The remedy
using copulas can be modified to be effective in the case where both assumptions
must be violated. The null hypothesis is equivalent to Section~\ref{sec:fitted}
and the test statistic is equal to Equation~\eqref{eq:ks_fitted}. The bootstrap
procedure in Section~\ref{sec:fitted} is no longer valid because the serial
dependence is not accounted for. Let $r$ be the AR(1) coefficient of the normal
copula that matches the sample first-order Spearman's rho of the observed data
as obtained by the \texttt{iRho} function in the \textsf{copula} package
\citep{Copula}. We propose the following bootstrap procedure to assess the
significance of the observed KS statistic.

\begin{enumerate}
\item
  Generate $Z_1, \ldots, Z_n$ from an AR(1) process with autocorrelation
  coefficient $r$ such that the $Z_i$'s are $N(0, 1)$ variables.
\item
  Form a bootstrap sample $X_i^* = F^{-1}_{\hat\theta_n} [\Phi(Z_i)]$,
  $i = 1, \ldots, n$, whose first-order sample Spearman's rho matches that of
  the observed data.
\item
  Fit $F_\theta$ to the sample $X_1^*, \ldots, X_n^*$ and obtain estimator
  $\hat\theta_n^*$
\item
  Obtain the empirical distribution function $F_n^*$ of the bootstrap sample
  $X_1^*, \ldots, X_n^*$.
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x \lvert F_n^* (x)- F_{\hat\theta_n^*}(x) \rvert.
  \]
\item
  Repeat the previous steps a large number $B$ times and use the empirical
    distribution of the $B$ test statistics to approximate
    the null distribution of the observed statistic.
\end{enumerate}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_ar1_FD}
  \caption{The Super Naive plot (left) is the histogram of p-values from the
  standard KS test with fitted parameters. The Naive Parametric plot (middle) is
  the histogram of p-values from implementing parametric bootstrap. The Copula
  plot is the histogram of p-values from implementing parametric bootstrap with
  copulas for dependence and correcting for fitted parameters. In each case,
  $1000$ replicate tests were performed with the data generated from an AR(1)
  process of the standard normal distribution with $\psi = .5$. The sample size
  is $n = 100$ and $B = 1000$ bootstrap samples are obtained for each test.}
  \label{fig:hist_ar1_FD}
\end{figure}

Figure~\ref{fig:hist_ar1_FD} shows the results of our simulation on data
simulated from an AR(1) process. As should be expected, naively fitting
parameters while providing no adjustment for dependent data invalidates the KS
test. As well, only using the parametric bootstrap remedy for fitted parameters
from Section~\ref{sec:fitted} seems to provide weaker results than the
copula remedy presented above. The results show that copula remedy generates
uniform p-values and restores the size of the KS test.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_ma1_arma_ar2_FD}
  \caption{The Super Naive plots (left) are the histograms of p-values from the
  standard KS test with fitted parameters. The Naive Parametric plots (middle)
  are the histograms of p-values from implementing parametric bootstrap. The
  Copula plots (bottom) are the histograms of p-values from implementing
  parametric bootstrap with copulas for dependence and correcting for fitted
  parameters. The data is generated from an MA(1) process (left) with
  $\theta = .5$, ARMA(1, 1) process (middle) with $\psi = .5$ and $\theta = .3$,
  and AR(2) process (right) with $\psi = (.5, .3)$ of the standard normal
  distribution. In each case, $1000$ replicate tests were performed with sample
  size $n = 100$ and $B = 1000$ bootstrap samples.}
  \label{fig:hist_ma1_arma_ar2_FD}
\end{figure}

Similar to Section~\ref{sec:dependence}, the copula approach is not a complete
solution. Regardless of the true dependence in the data we assume an AR(1)
dependence structure by taking the lag-1 sample auto-spearman rho. However, we
can show that as long as the AR(1) assumption is a close approximation, the
correction still provides a reasonable approximation that can be useful for
practical purposes. Figure~\ref{fig:hist_ma1_arma_ar2_FD} shows the results of the
procedure performed on data generated with dependence structures of  MA(1),
ARMA(1, 1), and AR(2). Naively fitting parameters and not adjusting for
dependence clearly deviates from a uniform distribution of p-values. Parametric
bootstrap provides some correction but does not account for dependence, so
therefore the results of the copula remedy are more accurate and favorable.
In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough
to our assumption of AR(1) that the results are reasonable. AR(2) however
appears to be just far enough from our assumption, showing a limitation of the
procedure.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_gamma_gev_FD}
  \caption{The Super Naive plots (left) are the histograms of p-values from the
  standard KS test with fitted parameters. The Naive Parametric plots (middle)
  are the histograms of p-values from implementing parametric bootstrap. The
  Copula plots are the histograms of p-values from implementing parametric
  bootstrap with copulas for dependence and correcting for fitted parameters.
  The data is generated from $Gamma(3, 1)$ (left) and $GEV(0, .2, 1)$ (right)
  with a correlation coefficient of $r = 0.5$. In each case, $1000$ replicate
  tests were performed with sample size $n = 100$ and $B = 1000$ bootstrap
  samples.}
  \label{fig:hist_gamma_gev_FD}
\end{figure}

It is also possible to apply our procedure to other families of distributions.
The data in Figure~\ref{fig:hist_gamma_gev_FD} is generated from the gamma and
generalized extreme value distributions. The results are favorable and show that
the procedure outlined as a remedy for fitted parameters and spatially dependent
can be adapted for various families of distributions.

\section{Conclusion}
\label{sec:conclusion}

The KS test has base assumptions that the hypothesized distribution is
completely specified and the data is independent. When these assumptions are
violated, the test is no longer accurate and remedies must be performed. In the
case of fitted parameters, parametric and non-parametric bootstrap can restore
the size of the test. A bias correction is required if the non-parametric form
is used \citep{Babu}. In the case of \eds{serially} dependent data, a procedure
using bootstrap
with copulas to model dependency shows positive results. When both assumptions
are violated, i.e., where the data has \eds{serial} dependence and parameters
must
be fitted, an adjusted copula procedure also shows positive results. The tests
appear effective for a variety of families of distributions. The copula remedy
is not a complete solution and has limitations. Regardless of the true
dependence, we assume an AR(1) dependence structure. Therefore, if the AR(1)
dependence structure is a close approximation of the truth, the approach can work.
However, in cases such as AR(2), if the approximation is too far from the true
dependence structure the approach does not completely remedy the issue. As well,
tests were only performed with the normal copula. It is possible that other
copulas could provide stronger results based on the true dependence of the data.

\bibliographystyle{asa}
\bibliography{citations}

\end{document}

### 2022-10-24 manuscript/manuscript.tex
smoothed intro

--- 2022-10-10 Manuscript/manuscript.tex
@@
 The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit
-tests for comparing a sample with a hypothesized parametric distribution.
+tests for comparing a sample with a hypothesized continuous distribution.
 Nevertheless, it has often been misused. The standard one-sample KS test applies
@@
 \bigskip
-\noindent\sc{Keywords}:
+\noindent{\sc Keywords}:
 nonparametric bootstrap;
-parametric bootstrap;
+parametric bootstrap.
 \end{abstract}
@@
 
-The standard KS test is not applicable when the hypothesized distribution
-contains fitted parameters. \citet{Steinskog} ``discovers'' the change in power
-when using estimated parameters and stresses caution in using the KS test in
-such ways. In fact, \citet{Lilliefors} shows for the normal distribution that using the
-standard table when values of the mean and standard deviation are estimated
-yields extremely conservative results.
-% JY: this paper set up a wrong target; they didn't even cite bootstrap!
-% This is supported by \citet{Capasso},
-% who concludes that failing to re-estimate the parameters may lead to wrong,
-% overly-conservative approximations to the distributions of goodness-of-fit test
-% statistics based on the empirical distribution function. \citet{Capasso} also
-% notes that the impact of this mistake may turn out to be dramatic and does not
-% vanish as the sample size increases.
-This problem can be solved by parametric bootstrap \citep{Efron}, where
+When the hypothesized distribution contains fitted parameters, as is the case in
+most goodness-of-fit test settings, the standard KS test is not applicable.
+\citet{Steinskog} ``discovers'' the change in power
+when using fitted parameters and stresses caution in using the KS test in
+such ways. In fact, using fitted parameters in place of the true parameters in
+KS test is long known to yield extremely conservative results
+\citep[e.g.,][]{Lilliefors}. This problem can be solved by parametric
+bootstrap \citep{efron1985bootstrap, hall1991two}, where
 bootstrap samples of the testing statistics are constructed from samples
@@
 solution is not trivial because the a nonparametric bootstrap sample of the
-observed data have ties, which would not happen for continuous distribution.
-A nonparametric remedy was provided by \citet{Babu}, who derived the bias and
+observed data have ties, which would not happen for continuous distributions.
+\citet{Babu} derived the bias of standard nonparametric bootstrap and
 showed how to correct it. They further noted that both parametric and
 non-parametric procedures lead to correct asymptotic levels.
-% JY: Genest at al is not about our setting. \citet{Genest} provides
-% validity for using parametric bootstrap with various goodness-of-fit tests.
 
-The standard KS test does not apply to serially dependent data either. For
-testing normality, \citet{Durilleul} demonstrated that a naive application of
+The standard KS test does not apply to serially dependent data either. The
+distribution of the KS statistic would have a higher variance for positively
+dependent data than that derived when the data are independent because of a
+smaller effective sample size. For example, for
+testing normality, \citet{Durilleul} demonstrates that a naive application of
 the KS statistic is too liberal for medium-to-high positive serieal dependence,
@@
 dependence and concludes that a test based on Monte-Carlo simulations performed
-the best. \jy{need some sentences to elaborate the issue and identify a gap in
-  the literature.}
+the best. When additionally the hypothesized distribution contains unknown
+parameters, the standard KS test becomes even further inapplicable.
 
@@
 \end{document}
+%%% LocalWords: 
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% ispell-personal-dictionary: ".aspell.en.pws"
+%%% fill-column: 80
+%%% eval: (auto-fill-mode 1)
+%%% End:

### 2022-10-24 manuscript/manuscript.tex
smoothed section 2

@@
   \label{eq:ks_standard}
-  D_n = \sup_x | F_{n}(x) - F(x) |.
+  D_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
 \end{equation}
 The asymptotic distribution of $D_n$ under $H_0$ is independent of the
-distribution $F$. As $n \to \infty$, $\sqrt{n} D_n$ converges in distribution to
+distribution~$F$. As $n \to \infty$, $D_n$ converges in distribution to
 the supremum of standard Brownian bridge \citep{kolmogorov1933sulla}. For large
@@
 
-The null distribution of the KS statistic changes when the hypothesized
-distribution contains fitted parameters.
-\eds{what is the null distribution when not using fitted parameters}.
-In this scenario, the null hypothesis
-is $H_0$: the random sample $X_1, \ldots, X_n$ comes from a continuous
-distribution $F_{\theta}$ with unspecified parameter vector $\theta$.
-Let $\hat\theta_n$ be an estimator of $\theta$, which could be, for example, a
-maximum likelihood estimator or moment estimator. The test statistic is
+The null hypothesis of a goodness-of-fit test is often a composite hypothesis
+instead of a single hypothesis. That is, the hypothesized distribution is a
+family of distributions with unspecified parameters instead of a specific member
+in this family. Let $F_\theta$ be a family of distributions indexed by parameter
+vector~$\theta$. The null hypothesis is
+\[
+  H_0: \text{the random sample $X_1, \ldots, X_n$
+    comes from a distribution $F_\theta$ with some $\theta$.}
+\]
+Since $\theta$ is unknown, one would naturally estimate $\theta$ by
+$\hat\theta_n$ from, for example, maximum likelihood or methods of moments. The
+KS statistic would then be computed as
 \begin{equation}
   \label{eq:ks_fitted}
-  D = \sup_x | F_n(x) - F_{\hat\theta_n}(x) |.
+  D_n = \sqrt{n} \sup_x | F_n(x) - F_{\hat\theta_n}(x) |.
 \end{equation}
-Since $F_{\hat\theta_n}$ is not the same as the true data generating
-$F_\theta$, the null distribution of $D$ obtained in existing implementations in
-software packages which assumes completely known $F_\theta$ no longer applies
-\citep{Steinskog}.
+An overly large $D_n$ still indicates evidence to reject~$H_0$. To get the
+p-value of the observed $D_n$, however, the null distribution is not the same as the
+of $D_n$, however, is no longer the same as that in the standard
+case~\eqref{eq:ks_standard}. If the same null distribution were used, one would
+be testing a different $H_0$ that the random sample comes from the specific
+member distribution $F_{\hat\theta}$.
 
-To demonstrate the consequences of this problem, a simulation is performed. A
-random sample $X_1, \ldots, X_n$ is generated from the standard normal
-distribution with sample size $n = 100$. The p-values of $1000$ replicate tests
- of normality
-are displayed in the Naive plot of Figure~\ref{fig:hist_fitted}.
-\eds{how are these p-values calculated?}
-Each KS test
-was performed using fitted parameters, i.e., the hypothesized distribution is
+The consequence of using the wrong null distribution for the KS statistic $D_n$
+in~\eqref{eq:ks_fitted} can be illustrated through a simple simulation study. A
+random sample $X_1, \ldots, X_n$ was generated from the standard normal
+distribution with sample size $n = 100$. The sample mean and sample standard
+deviation were used as $\hat\theta_n$. The p-value of the testing
+statistic~$D_n$ in~\eqref{eq:ks_fitted} was obtained by naively calling the
+\texttt{ks.test} function in~R with the fitted normal distribution as the
+hypothesized distribution. That is, the hypothesized distribution was
 $N(\bar X, s^2)$ where $\bar X$ is the sample mean and $s^2$ is the sample
-variance. Since the data is truly generated from a standard normal distribution,
- %with
-%seemingly all assumptions met,
-a uniform distribution of $U(0, 1)$ would naively be expected for the p-values.
-However this should only be expected when the KS test assumptions hold, and they
- do not due to using fitted parameters. Therefore,
-there is notable deviation from the uniform distribution.
+variance. This experiment was repeated for 1000 times and the histogram of the
+1000 p-values are displayed in Figure~\ref{fig:hist_fitted}. If the test were
+valid, the p-values would be uniformly distributed in the unit
+interval. Clearly, the pattern of the 1000 p-values are very different from what
+one would expect to see from a 1000 draws from the standard uniform
+distribution.
 
 To fix the problem, parametric bootstrap can be used to approximate the null
-distribution of the testing statistic.
+distribution of the testing statistic~$D_n$. For a large number~$B$, the
+parametric bootstrap procedure is as follows.
 \begin{enumerate}
@@
 \item
-    Obtain the empirical distribution function $F_n^*$ of $X_1^*, \ldots,
-    X_n^*$.
+  Obtain the empirical distribution function $F_n^*$ of
+  $X_1^*, \ldots,  X_n^*$.
 \item
@@
   \[
-      D^* = \sup_x | F_n^* (x)- F_{\hat\theta_n}^*(x) |.
+    D_n^* = \sqrt{n} \sup_x | F_n^* (x)- F_{\hat\theta_n}^*(x) |.
   \]
 \item
-    Repeat the previous steps a large number $B$ times and use the empirical
+  Repeat the previous steps $B$ times and use the empirical
   distribution of $D^*$ to approximate the null distribution of the observed
@@
 \end{enumerate}
+The p-value of $D_n$ is approximated by the proportion of $D_n^*$'s that are
+greater than or equal to~$D_n$.
 
 Nonparametric bootstrap can also be used to approximate the null distribution
-of the testing statistic. The procedure is similar, however the resampling is
-performed with the empirical distribution instead of the fitted parametric
-distribution and there is a correction for bias that is required
-\citep{Babu}.
+of the testing statistic with the bias correction from \citet{Babu}. The
+procedure is as follows.
 \begin{enumerate}
@@
 \end{enumerate}
-The p-value can be calculated by counting the number of bootstrap KS
-statistics greater than or equal to the observed KS statistic, and then dividing
-by the number of bootstrap samples. Figure~\ref{fig:hist_fitted} displays the
-results of from our simulations. We would expect the distribution of p-values
-to be uniform in the case where the KS test holds its size. It is clear from the
-figure that both parametric and nonparametric bootstrap processes correct for
-the problem of fitted parameters. The plots for the bootstrapped p-values appear
-to be $U(0,1)$, unlike the naive p-values.
+The p-value of $D_n$ is, again, approximated by the proportion of $D_n^*$'s that
+are greater than or equal to~$D_n$.
 
@@
 \end{figure}
+
+In the same simulation study, p-values were obtained for the 1000 replicates
+with both the parametric and nonparametric bootstrap procedures. The center and
+right panels of Figure~\ref{fig:hist_fitted} display the histograms of the 1000
+p-values from the parametric and nonparametric bootstrap procedures,
+respectively. This time, both samples of the p-values appear to come from the
+standard uniform distributions.
 

### 2022-10-31 manuscript/manuscript.tex
further smoothing for section 2

@@
 An overly large $D_n$ still indicates evidence to reject~$H_0$. To get the
-p-value of the observed $D_n$, however, the null distribution is not the same as the
-of $D_n$, however, is no longer the same as that in the standard
+p-value of the observed $D_n$, however, the null distribution is not the same as
+that in the standard
 case~\eqref{eq:ks_standard}. If the same null distribution were used, one would
-be testing a different $H_0$ that the random sample comes from the specific
-member distribution $F_{\hat\theta}$.
+be testing a different~$H_0$ that the random sample comes from the specific
+member distribution~$F_{\hat\theta}$ instead of the family~$F_\theta$.
 
@@
 statistic~$D_n$ in~\eqref{eq:ks_fitted} was obtained by naively calling the
-\texttt{ks.test} function in~R with the fitted normal distribution as the
+\texttt{ks.test()} function in~R with the fitted normal distribution as the
 hypothesized distribution. That is, the hypothesized distribution was
@@
 interval. Clearly, the pattern of the 1000 p-values are very different from what
-one would expect to see from a 1000 draws from the standard uniform
+one would expect to see from 1000 draws from the standard uniform
 distribution.
@@
 To fix the problem, parametric bootstrap can be used to approximate the null
-distribution of the testing statistic~$D_n$. For a large number~$B$, the
-parametric bootstrap procedure is as follows.
+distribution of the testing statistic~$D_n$:
 \begin{enumerate}
@@
 \item
-  Fit $F_\theta$ to the sample and obtain estimated $\hat\theta_n^*$
+  Fit $F_\theta$ to the sample and obtain estimate $\hat\theta_n^*$ of $\theta$.
 \item
@@
 \item
-  Repeat the previous steps $B$ times and use the empirical
+  Repeat the previous steps a large number~$B$ times and use the empirical
   distribution of $D^*$ to approximate the null distribution of the observed
@@
 Nonparametric bootstrap can also be used to approximate the null distribution
-of the testing statistic with the bias correction from \citet{Babu}. The
-procedure is as follows.
+of the testing statistic with the bias correction from \citet{Babu}:
 \begin{enumerate}
@@
 \end{figure}
+
+\jy{Anthony, could you label the panels as ``Parametric bootstrap'' and
+  ``Nonparametric bootstrap'' for the center and right panels?}
 

### 2022-10-31 Code/babu.R
test with effectiver sample size

@@ -42,3 +42,26 @@ ks.np.babu <- function(x, B = 1000) {
          statistic = stat, stat.b = stat.b)
 }
     
+## test for effective sample size
+ks.eff <- function(x) {
+    Fn <- ecdf(x)
+    Gn <- ecdf.leftcont(x)
+    mu <- mean(x); ss <- sd(x)
+    Ftheta <- pnorm(x, mu, ss)
+    Bn1 <- Fn(x) - Ftheta
+    Bn2 <- Gn(x) - Ftheta
+    d1 <- abs(Bn1)
+    d2 <- abs(Bn2)
+    stat <- max(d1, d2)
+    n <- coda::effectiveSize(x)
+    ## two-sided
+    pval <- 1 - .Call(stats:::C_pKS2, sqrt(n) * stat, tol = 1e-06)
+    list(p.value = pval, statistic = stat, neff = n)
+}
+
+do1rep <- function(phi = 0.5, n = 1000) {
+    x <- arima.sim(model = list(ar = phi), n = n, sd = sqrt(1 - phi^2))
+    ks.eff(x)$p.value
+}
+
+

### 2022-11-14 manuscript/manuscript.tex
minor
smoothed early section 3

@@
 Critical values for small samples ($n \le 35$) has also been given
-\citep{Massey}. The KS test is available in popular
+\citep{massey1951kolmogorov}. The KS test is available in popular
 statistical software packages, such as function \texttt{ks.test} in R package
-\textsf{stats} \citep{R, Marsaglia}.
+\textsf{stats} \citep{R, marsaglia2003evaluating}.
 
@@
 has often been applied without realizing that one or more of these assumptions
-do not hold. For example, \citet{Noether} demonstrated the conservativeness of
+do not hold. For example, \citet{noether1963note} showed the conservativeness of
 the KS test when applied to discontinuous distributions. The null distribution
@@
 exact and asymptotic distribution of $D_n$ is challenging. Fortunately, the null
-distribution of the KS statistic when the underlying distribution is
-discontinuous has been efficiently addressed by \citet{Dimitrova} with an
+distribution of the KS statistic for discontinuous distributions has been
+efficiently addressed by \citet{dimitrova2020computing} with an
 companion R package \textsf{KSgeneral}. Although a common misuse of KS test, the
@@
 
-When the hypothesized distribution contains fitted parameters, as is the case in
-most goodness-of-fit test settings, the standard KS test is not applicable.
-\citet{Steinskog} ``discovers'' the change in power
+When the hypothesized distribution~$F$ contains unspecified parameters, as is
+the case in most goodness-of-fit test settings, the standard KS test is not
+applicable. \citet{steinskog2007cautionary} ``discovers'' the change in power
 when using fitted parameters and stresses caution in using the KS test in
@@
 KS test is long known to yield extremely conservative results
-\citep[e.g.,][]{Lilliefors}. This problem can be solved by parametric
-bootstrap \citep{efron1985bootstrap, hall1991two}, where
+\citep[e.g.,][]{lilliefors1967kolmogorov}. This problem can be solved by
+parametric bootstrap \citep{efron1985bootstrap, hall1991two}, where
 bootstrap samples of the testing statistics are constructed from samples
@@
 observed data have ties, which would not happen for continuous distributions.
-\citet{Babu} derived the bias of standard nonparametric bootstrap and
+\citet{babu2004goodness} derived the bias of standard nonparametric bootstrap and
 showed how to correct it. They further noted that both parametric and
@@
 
-The standard KS test does not apply to serially dependent data either. The
+The standard KS test does not apply to stationary yet dependent data either. The
 distribution of the KS statistic would have a higher variance for positively
 dependent data than that derived when the data are independent because of a
-smaller effective sample size. For example, for
-testing normality, \citet{Durilleul} demonstrates that a naive application of
+smaller effective sample size. For example, for testing normality,
+\citet{durilleul1992lack} demonstrates that a naive application of
 the KS statistic is too liberal for medium-to-high positive serieal dependence,
 and that for negative dependence, the behavior is asymmetrical. For remedies,
-\citet{Weiss} provides a procedure that is applicable specifically for data
+\citet{weiss1978modification} provides a procedure that is applicable specifically for data
 modeled by the second-order auto-regressive (AR) process where the AR parameters
-are known. \citet{Lanzante} tests various strategies for dealing with temporal
+are known. \citet{lanzante2021testing} tests various strategies for dealing with temporal
 dependence and concludes that a test based on Monte-Carlo simulations performed
@@
 An overly large $D_n$ still indicates evidence to reject~$H_0$. To get the
-p-value of the observed $D_n$, however, the null distribution is not the same as
-that in the standard
+p-value of the observed $D_n$, however, note that the null distribution is not
+the same as that in the standard
 case~\eqref{eq:ks_standard}. If the same null distribution were used, one would
@@
 Nonparametric bootstrap can also be used to approximate the null distribution
-of the testing statistic with the bias correction from \citet{Babu}:
+of the testing statistic with the bias correction from \citet{babu2004goodness}:
 \begin{enumerate}
@@
   where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
-  bias term \citep{Babu}
+  bias term \citep{babu2004goodness}
 \item
@@
   \includegraphics[width=\textwidth]{hist_fitted}
-  \caption{The Naive plot (left) is the histogram of p-values from the standard
-  KS test with fitted parameters. The Parametric plot (middle) is the histogram
-  of p-values from implementing parametric bootstrap. The Babu plot (right) is
-  the histogram of p-values from implementing nonparametric bootstrap with a
-  correction for bias. In each case, $1000$ replicate tests were performed on
-  the standard normal distribution with sample size $n = 100$. $B = 1000$
-  bootstrap samples are obtained for each test. \eds{perhaps use density hist vs
+  \caption{Histograms of p-values for the KS test with unspecified parameters in
+    the hypothesized distribution based on 1000 replicates of sample size
+    $n = 100$. Naive (left): KS test with KS statistic calculated based on fitted
+    parameters. Parametric bootstrap (center): KS test with parametric
+    bootstrap. Nonparametric bootstrap (right): KS test with nonparametric
+    bootstrap using the bias correction from \citet{babu2004goodness}.
+    \eds{perhaps use density hist vs
 	freq. hist (here and elsewhere)?}}
@@
 
-The KS test also displays issues in the case of dependent data. As mentioned, an
-assumption of the test is that the data is independent. Real data, however,
-is often temporally or spatially dependent and the results of a goodness-of-fit
-test would be valuable. When the KS test is performed on dependent data it
-performs poorly. In this situation, the null hypothesis is $H_0$: the random
-sample $X_1, \ldots, X_n$ come from a continuous distribution $F$ where $F$ has
-completely specified parameters. The test statistic is the same as
-Equation~\eqref{eq:ks_standard}. However, since the data is dependent, the null
-hypothesis is wrong and must be corrected.
-\eds{null hypothesis or null distribution? or both?}
-This is demonstrated with a
-simulation in Figure~\ref{fig:hist_correlation}. Data is generated from a
-first-order autoregressive model (AR(1)) with a standard normal distribution.
-P-values are gathered from $1000$ replicate tests for different levels of the
-AR coefficient $\psi$, varying from $(-3,3)$.
-\eds{how are these p-values calculated?}
-In the presence of serially
-dependent data, the distribution of p-values no longer follows $U(0, 1)$ as
-would be expected of a valid test. The results echo those of \citet{Durilleul}
-that the KS statistic is too liberal in the presence of positive
-autocorrelation, and that the behavior is asymmetrical for negative
- autocorrelation.
+When the observed data $X_1, \ldots, X_n$ are not independent but serially
+dependent, the null distribution of the KS statistic $D_n$
+in~\eqref{eq:ks_standard} changes. For a
+stationary series, it may still be of interest to test whether the data come
+from a completely specified distribution~$F$. When the serial dependence is
+positive, the effective sample size is less than~$n$. The testing statistic
+would be stochastically greater than that obtained from independent data, making
+it more likely to reject the null hypothesis than it should. So the test is
+liberal. The reasoning is similar when the serial dependence is negative,
+in which case, the test is conservative.
+
+The invalidity of the statndard statistic for serially dependent data can be
+illustrated by a simple simulation study. Consider a first-order autoregressive
+or AR(1) model with marginal standard normal distribution. For each AR
+coefficient $\psi \in \{-0.3, 0.2, 0.1, 0, 0.1, 0.2, 0.3\}$, we generated 1000
+series of length 100. For each series, we applied the KS statistic
+in~\eqref{eq:ks_standard} to test $H_0$ that the $X_i$'s follow $N(0, 1)$
+marginally. The histograms of the p-values from $1000$ replicates for all the
+$\psi$ values are displayed in Figure~\ref{fig:hist_correlation}. When
+$\phi \ne 0$, the histograms do not look like to be generated from a standard
+uniform distribution. Positive $\psi$ values led to liberal p-values while
+negative $\psi$ values led to conservative p-values. The larger the magnitude of
+$\psi$, the bigger the deviation from the desired level.
 
@@
   \includegraphics[width=\textwidth]{hist_correlation}
-  \caption{Each histogram is a plot of the p-values of standard KS tests
-  performed on dependent data simulated from an AR(1) process of the standard
-  normal distribution. The titles represent the various levels of the AR
-  coefficient $\psi$ tested. The sample size is $n = 100$ and $1000$ replicate
-  tests were performed for each AR coefficient.}
+  \caption{Histograms of p-values for the KS test applied to data generated from
+    AR(1) processes with AR coefficients
+    $\psi \in \{-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3\}$
+    based on 1000 replicates of sample size $n = 100$.}
   \label{fig:hist_correlation}
@@
 
-In order to correct this, we can employ a parametric bootstrap procedure which
-assumes a working serial dependence structure through copulas. A copula is a
+A complete remedy for the KS tests with serially dependent data is
+challenging. The null distribution depends on the structure of the serial
+dependence, which can be arbitrary in practice. A parametric bootstrap procedure
+would need model specification of the dependence, whereas the primary interest
+is to test the marginal distribution of the stationary series. A block
+nonparametric bootstrap for stationary data \citep{kunsch1989jackknife} is
+attempting, but the counterpart of a bias correction as in
+\citet{babu2004goodness} is not available yet. Is there any approach that does
+not require fully specification of the dependence of the stationary process
+but still gives reasonably satisfactory correction to the size of the KS test in
+certain applications?
+
+We propose a semiparametric bootstrap procedure that assumes a working serial
+dependence structure which does not need to be correctly specified. The working
+serial dependence is introduced through copulas with the hope to approximate the
+true serial dependence as allowed by the working copulas. A copula is a
 multivariate distribution with standard uniform marginal distributions, which
 completely characterizes the dependence structure of a multivariate
-distribution \citep{Copula, Hofert}. For simplicity, we assume a normal copula
-with an AR(1) structure to characterize the serial dependence of the
-observations. The AR(1) parameter $r$ of the normal copula is set to match the
-sample serial Spearman's rho of the observed data.
-\eds{What is the difference between $\psi$ and $r$?}
-The procedure is as
-follows.
-
+distribution \citep{hofert2018elements}. It separates the dependence structure
+of a multivariate distribution from its marginal distributions. The normal copula
+is the copula determined by the multivariate normal distribution. We propose to
+use a normal working copula with an AR(1) structure to approximate the serial
+dependence of the observations. Let $\hat\rho$ be the lag-1 sample auto
+Spearman's rho of the observed data. A normal copula of dimension~$n$ can be
+constructed with an AR(1) structure and its AR coefficient~$\psi$ is chosen to
+ensure that the Spearman's rho matches $\hat\rho$. Let $\psi(\hat\rho)$ denote
+this coefficient. The bootstrap procedure is as follows.
 \begin{enumerate}
@@
   Generate $Z_1, \ldots, Z_n$ from an AR(1) process with autocorrelation
-  coefficient $r$ such that the $Z_i$'s are $N(0, 1)$ variables.
+  coefficient $\psi(\hat\rho)$ such that the $Z_i$'s are $N(0, 1)$ variables.
 \item
-  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i)]$, where $\Phi$ is the
-  distribution function of $N(0, 1)$, $i = 1, \ldots, n$, whose first-order
-  sample Spearman's rho matches that of the observed data.
+  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i)]$,  $i = 1, \ldots, n$,
+  where $\Phi$ is the distribution function of $N(0, 1)$.
 \item
@@
 \end{enumerate}
+The p-value of $D_n$ is, again, approximated by the proportion of $D_n^*$'s that
+are greater than or equal to~$D_n$.
 
+This process is semiparametric because the marginal distribution is
+parametrically specified while the dependence structure of the stationary series
+is only approximated. The closer the approximation is to the truth, the better
+performance of the size of the KS test  If the true dependence is indeed a
+normal copula with an AR(1) structure, this method is exact. When the true
+dependence is not AR(1), it may still give a reasonable approximation that can
+be useful for practical purposes. More complicated working models other
+than the AR(1) process could be used, but we focus here on the AR(1) model.
+
+Continuing with the simulation study, 
 Throughout the simulation we assume a working AR(1) dependence structure
-regardless of the true dependence. If the true dependence is indeed a normal
-copula with an AR(1) structure, this method is exact. When the true dependence
-is not AR(1), it may still give a reasonable approximation that can be useful
-for practical purposes. This is demonstrated with different dependence
+regardless of the true dependence. This is demonstrated with different dependence
 structures in Figure~\ref{fig:hist_ma1_arma_ar2_D}.
@@
 as obtained by the \texttt{iRho} function in the \textsf{copula} package
-\citep{Copula}. We propose the following bootstrap procedure to assess the
+\citep{Rpkg:copula}. We propose the following bootstrap procedure to assess the
 significance of the observed KS statistic.
@@
 the size of the test. A bias correction is required if the non-parametric form
-is used \citep{Babu}. In the case of \eds{serially} dependent data, a procedure
+is used \citep{babu2004goodness}. In the case of \eds{serially} dependent data, a procedure
 using bootstrap

### 2022-12-05 Code/autoarma.R
auto.arima with no intercept in fitting

@@ -1,0 +1,46 @@
+ks.arma <- function(x, pdist, qdist, B = 1000, working=c("auto", "2,2")) {
+    z <- qnorm(pdist(x))
+    n <- length(x)
+    if (working == "auto") {
+        fit <- forecast::auto.arima(z, ic = "aic", max.d = 0, max.D = 0, allowmean = FALSE)
+        ## stepwise=FALSE, approximation=FALSE)
+        ## working model: p.max = q.max = 5
+    } else {
+        pq <- as.numeric(unlist(strsplit(working, ",")))
+        fit <- arima(z, order = c(pq[1], 0, pq[2]), include.mean = FALSE) ## working arma(2, 2)
+    }
+    model <- list(ar = fit$model$phi, ma = fit$model$theta)
+
+    ## theoretical variance of arma; note the negative sign of theta; McLeod (1975)
+    sigma <- sqrt(ltsa::tacvfARMA(phi = model$ar, theta = - model$ma, maxLag = 0))
+    stat <- ks.test(x, pdist)$statistic
+    stat.b <- rep(0, B)
+    for (i in 1:B) {
+        z.b <- arima.sim(model, n = n)
+        ##   arma(1, 1) only: sd = sqrt (1 - ophi^2) / (1 + 2 * phi * theta + theta^2))
+        x.b <- qdist(pnorm(z.b, mean = 0, sd = sigma))
+        stat.b[i] <- ks.test(x.b, pdist)$statistic
+    }
+    p.value <- mean(stat.b >= stat)
+    p.value
+}
+
+## simulation
+## marginal gamma(3, 1)
+
+qdist <- function(u) qgamma(u, shape = 3, scale = 1)
+pdist <- function(u) pgamma(u, shape = 3, scale = 1)
+
+genData <- function(n, phi, theta, qdist) {
+    x <- arima.sim(model = list(ar = phi, ma = theta), n = n)
+    ## xbig <- arima.sim(model = list(ar = phi, ma = theta), n = 100000)
+    ## sigma <- sd(xbig)
+    sigma <- sqrt(ltsa::tacvfARMA(phi = phi, theta = - theta, maxLag = 0))
+    qdist(pnorm(x, sd = sigma))
+}
+
+do1rep <- function(phi, theta, n, pdist, qdist, working) {
+    model  <- list(ar = phi, ma = theta)
+    x <- genData(n, phi, theta, qdist)
+    ks.arma(x, pdist, qdist, working = working)
+}

### 2022-12-05 Code/autosim.R

@@ -1,0 +1,17 @@
+source("autoarma.R")
+
+## arma(1, 1) with phi = .3 and theta = .2
+sim.3.2 <- replicate(1000, do1rep(.3, .2, 200, pdist, qdist, "1,1"))
+sim.3.2a <- replicate(1000, do1rep(.3, .2, 200, pdist, qdist, "auto"))
+
+## ar(1) with phi = .5
+sim.5 <- replicate(500, do1rep(.5, double(0), 200, pdist, qdist, "1,0"))
+sim.5a <- replicate(500, do1rep(.5, double(0), 200, pdist, qdist, "auto"))
+
+
+## ar(1) with phi = -.3
+sim.n3 <- replicate(1000, do1rep(-.3, double(0), 200, pdist, qdist, "1,0"))
+sim.n3a <- replicate(1000, do1rep(.3, double(0), 200, pdist, qdist, "auto"))
+
+
+save(sim.3.2, sim.3.2a sim.5, sim.5a, sim.n3, sim.n3a, file = "autosim.rda")

### 2022-12-05 Code/autosim.R
number of replicates 1000 not 500

@@ -1,12 +1,15 @@
 source("autoarma.R")
 
+set.seed(20221205)
+
 ## arma(1, 1) with phi = .3 and theta = .2
 sim.3.2 <- replicate(1000, do1rep(.3, .2, 200, pdist, qdist, "1,1"))
 sim.3.2a <- replicate(1000, do1rep(.3, .2, 200, pdist, qdist, "auto"))
 
+
 ## ar(1) with phi = .5
-sim.5 <- replicate(500, do1rep(.5, double(0), 200, pdist, qdist, "1,0"))
-sim.5a <- replicate(500, do1rep(.5, double(0), 200, pdist, qdist, "auto"))
+sim.5 <- replicate(1000, do1rep(.5, double(0), 200, pdist, qdist, "1,0"))
+sim.5a <- replicate(1000, do1rep(.5, double(0), 200, pdist, qdist, "auto"))
 
 
 ## ar(1) with phi = -.3

### 2023-01-05 Code/Simulation.Rmd
Autoarma histogram framework with ggplot

---
title: "R Notebook"
output: html_notebook
---

```{r packages}
# Load packages
library(tidyverse)
library(copula)
library(evd)
library(ismev)
library(tseries)
library(forecast)
source('tspb.R')
```

```{r hist_correlation}
# Test to show that autocorrelation changes the power of the test
test_correlation <- function(n_tests, ars) {

  # Create a master data_frame for p-values
  columns <- c("p_value", "ar")
  ar_results <- data.frame(matrix(ncol = 2, nrow = 0))
  colnames(ar_results) <- columns

  # For AR coefficients from -0.5 to 0.5
  for(i in 1:length(ars)) {

    for(j in 1:n_tests) {

      # Generate random correlated data, perform a KS-test, and store the p-value
      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 100)
      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = round(ars[i], 1))
    }
  }

  return(ar_results)
}

 # Set AR coefficients and generate results
ars <- seq(-0.3, 0.3, by = 0.1)
ar_results <- test_correlation(1000, ars)

# Generate histograms plot
hist_correlation <- ggplot(ar_results) + 
                    geom_histogram(aes(x = p_value, fill = ar), boundary = 0, binwidth = 1/20) + 
                    facet_grid(~ar) +
                    theme(legend.position = "none") +
                    scale_x_continuous(name = "p-value", breaks=c(0, 1))

# Save the histogram figure
ggsave(filename = "hist_correlation.pdf", plot = hist_correlation, path = "../Manuscript", height = 2.1, width = 6)
```

```{r Parametric}
# Test parametric bootstrap as a solution to fitting parameters
test_parametric <- function(x, B = 1000) {

  # Summarize parameters
  mu <- mean(x)
  sigma <- sd(x)

  # Store KS statistic from using fitted parameters
  stat <- ks.test(x, "pnorm", mu, sigma)$statistic

  # Parametric bootstrap to approximate the null distribution
  n <- length(x)
  stat.b <- double(B)
  for (i in 1:B) {
    x.b <- rnorm(n, mu, sigma)
    mu.b <- mean(x.b)
    sigma.b <- sd(x.b)
    stat.b[i] <- ks.test(x.b, "pnorm", mu.b, sigma.b)$statistic
  }

  # Return empirical p-value
  p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)

  counter <<- counter + 1
  cat(counter, "")
  list(p.value = p.value)
}

# Test non-parametric bootstrap as a solution to fitted parameters
test_babu <- function(x, B = 1000) {
  p.value <- ks.np.babu(x, B = 1000)$p.value
  counter <<- counter + 1
  cat(counter, "")
  list(p.value = p.value)
}

# Naive KS-test to show consequence of fitted parameters
test_naive <- function(x) {
  p.value <- ks.test(x, "pnorm", mean = mean(x), sd = sd(x))$p.value
  list(p.value = p.value)
}

# Generate results
n_tests <- 1000
n <- 100
counter <- 0
pvals_parametric <- replicate(n_tests, test_parametric(rnorm(n), B = 1000)$p.value)
counter <- 0
pvals_babu <- replicate(n_tests, test_babu(rnorm(n), B = 1000)$p.value)
pvals_naive <- replicate(n_tests, test_naive(rnorm(n))$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Parametric", n_tests), rep("Babu", n_tests), rep("Naive", n_tests))
p_values <- c(pvals_parametric, pvals_babu, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Parametric", "Babu"))

# Generate histograms plot
hist_fitted <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

# Save the histogram figure
ggsave(filename = "hist_fitted.pdf", plot = hist_fitted, path = "../Manuscript", height = 2.1, width = 6)
```

```{r babu}
ecdf.leftcont <- function (x) {
    x <- sort(x)
    n <- length(x)
    if (n < 1) 
        stop("'x' must have 1 or more non-missing values")
    vals <- unique(x)
    ## making it left continuous!
    rval <- approxfun(vals, cumsum(tabulate(match(x, vals)))/n - 1/n, 
        method = "constant", yleft = 0, yright = 1, f = 1, ties = "ordered")
    class(rval) <- c("ecdf", "stepfun", class(rval))
    assign("nobs", n, envir = environment(rval))
    attr(rval, "call") <- sys.call()
    rval
}

ks.np.babu <- function(x, B = 1000) {
    ## for normal distribution only
    n <- length(x)
    Fn <- ecdf(x)
    Gn <- ecdf.leftcont(x)
    mu <- mean(x); ss <- sd(x)
    Ftheta <- pnorm(x, mu, ss)
    Bn1 <- Fn(x) - Ftheta
    Bn2 <- Gn(x) - Ftheta
    d1 <- abs(Bn1)
    d2 <- abs(Bn2)
    stat <- max(d1, d2)
    stat.b <- double(B)
    for (i in 1:B) {
        x.b <- sample(x, size = n, replace = TRUE)
        Fn.b <- ecdf(x.b)
        Gn.b <- ecdf.leftcont(x.b)
        mu.b <- mean(x.b); ss.b <- sd(x.b)
        ## evaluate at x (not x.b)
        Ftheta.b <- pnorm(x, mu.b, ss.b)
        d1.b <- abs(Fn.b(x) - Ftheta.b - Bn1)
        d2.b <- abs(Gn.b(x) - Ftheta.b - Bn2)
        stat.b[i] <- max(d1.b, d2.b)
    }
    p.value <-  (sum(stat.b >= stat) + 0.5) / (B + 1)
    list(p.value = p.value,
         statistic = stat, stat.b = stat.b)
}
```

```{r gen_data}
## generating observations from a specified distribution with serial dependence
genData <- function(n, qdist, ..., copula, rho) {
    ## n: sample size
    ## qdist: quantile function of the desired marginal distribution
    ## copula: copula for serial distribution
    ## rho: spearman's rho
    theta <- iRho(copula(), rho)
    cop <- copula(theta)
    u <- runif(n)
    for (j in 2:n) {
        u[j] <- cCopula(c(u[j-1], u[j]), cop, indices = 2, inverse = TRUE)
    }
    qdist(u, ...)
}
```

```{r AR(1) D}
test_copula_D <- function(x, pdist, qdist, ..., B, wcopula = normalCopula) {

    # Get observed statistic
    n <- length(x)

    stat  <- ks.test(x, pdist, ...)$statistic

    # Get lag-1 sample auto-spearman rho
    rho  <-  cor(x[-1], x[-n], method = "spearman")
    r <- iRho(wcopula(), rho)
    wcop <- wcopula(r)

    # Perform parametric bootstrap to get an empirical distribution of stat
    stat.b <- double(n)

    for (i in 1:B) {
        # 1. The marginal distribution is the fitted dist
        # 2. There is temporal dependence
        u <- runif(n) 
        for (j in 2:n) {
            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
        }

        # Transform bootstrap sample and fit the parameters
        x.b <- qdist(u, ...)

        # Gather bootstrap sample's test statistic
        stat.b[i] <- ks.test(x.b, pdist, ...)$statistic
    }

    # Return empirical p-value
    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)

    counter <<- counter + 1
    cat(counter, "")

    return(p.value)
}

# Standard KS test
test_standard_ks <- function(x, pdist, ...) {
  p.value <- ks.test(x, pdist, ...)$p.value
  list(p.value = p.value)
}

ptm <- proc.time()

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1000
B <- 100
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(genData(n = 100, qdist = qnorm, mean = 0, sd = 1, copula = claytonCopula, rho = 0.5), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean,
                                              sd = sd,
                                              B = B, 
                                              wcopula = normalCopula))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(genData(n = 100, qdist = qnorm, mean = 0, sd = 1, copula = claytonCopula, rho = 0.5), 
                                                pdist = pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_ar1_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ar1_D

print(proc.time() - ptm)

# Save the histogram figure
ggsave(filename = "hist_ar1_D.pdf", plot = hist_ar1_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r MA(1) D}
ptm <- proc.time()

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
ma <- 0.5
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean,
                                              sd = sd,
                                              B = B,
                                              wcopula = normalCopula))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n),
                                                pdist = pnorm,
                                                mean = mean,
                                                sd = sd)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_ma1_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ma1_D

print(proc.time() - ptm)

# Save the histogram figure
ggsave(filename = "hist_ma1_D.pdf", plot = hist_ma1_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r ARMA(1,1) D}
ptm <- proc.time()

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
ar <- 0.5
ma <- 0.3
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                            pdist = pnorm, 
                                            qdist = qnorm,
                                            mean = mean,
                                            sd = sd,
                                            B = B,
                                            wcopula = normalCopula))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n),
                                                pdist = pnorm,
                                                mean = mean,
                                                sd = sd)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_arma_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_arma_D

print(proc.time() - ptm)

# Save the histogram figure
ggsave(filename = "hist_arma_D.pdf", plot = hist_arma_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r AR(2) D}
ptm <- proc.time()

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
b1 <- 0.5
b2 <- 0.3
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                            pdist = pnorm, 
                                            qdist = qnorm,
                                            mean = mean,
                                            sd = sd,
                                            B = B,
                                            wcopula = normalCopula))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n),
                                                pdist = pnorm,
                                                mean = mean,
                                                sd = sd)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_ar2_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ar2_D

print(proc.time() - ptm)

# Save the histogram figure
ggsave(filename = "hist_ar2_D.pdf", plot = hist_ar2_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r Gamma D}
ptm <- proc.time()

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
shape <- 3
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                             pdist = pgamma,
                                             qdist = qgamma,
                                             shape = shape,
                                             scale = scale,
                                             B = B,
                                             wcopula = normalCopula))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                   pdist = pgamma,
                                                   shape = shape, 
                                                   scale = scale)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_gamma_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_gamma_D

print(proc.time() - ptm)

# Save the histogram figure
ggsave(filename = "hist_gamma_D.pdf", plot = hist_gamma_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r GEV D}
ptm <- proc.time()

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
loc <- 0
shape <- 0.2
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
                                           pdist = pgev,
                                           qdist = qgev,
                                           loc = loc, 
                                           shape = shape,
                                           scale = scale,
                                           B = B,
                                           wcopula = normalCopula))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                 pdist = pgev,
                                                 loc = loc, 
                                                 shape = shape,
                                                 scale = scale)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_gev_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_gev_D

print(proc.time() - ptm)

# Save the histogram figure
ggsave(filename = "hist_gev_D.pdf", plot = hist_gev_D, path = "../Manuscript", height = 2.1, width = 6)
```

```{r AR(1) FD}
test_copula_FD <- function(x, dist, B) {

    # Get observed statistic
    n <- length(x)
    mu <- mean(x)
    sigma <- sd(x)
    stat  <- ks.test(x, dist, mean = mu, sd = sigma)$statistic

    # Get lag-1 sample auto-spearman rho
    rho  <-  cor(x[-1], x[-n], method = "spearman")
    r <- iRho(normalCopula(), rho)
    np <- normalCopula(r)

    # Perform parametric bootstrap to get an empirical distribution of stat
    stat.b <- double(n)

    for (i in 1:B) {
        # 1. The marginal distribution is the fitted dist
        # 2. There is temporal dependence
        u <- runif(n) 
        for (j in 2:n) {
            u[j]  <- cCopula(c(u[j-1], u[j]), np, indices = 2, inverse = TRUE)
        }

        # Transform bootstrap sample and fit the parameters
        x.b <- qnorm(u, mean = mu, sd = sigma)
        mu.b <- mean(x.b)
        sigma.b <- sd(x.b)

        # Gather bootstrap sample's test statistic
        stat.b[i] <- ks.test(x.b, dist, mean = mu.b, sd = sigma.b)$statistic
    }

    # Return empirical p-value
    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)

    counter <<- counter + 1
    cat(counter, "")

    return(p.value)
}

# Super naive KS-test with fitted parameters
test_standard_ks_F <- function(x) {
  p.value <- ks.test(x, "pnorm", mean = mean(x), sd = sd(x))$p.value
  list(p.value = p.value)
}

ptm <- proc.time()

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1000
B <- 1000

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_FD(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks_F(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_ar1_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ar1_FD

print(proc.time() - ptm)

# Save the histogram figure
ggsave(filename = "hist_ar1_FD.pdf", plot = hist_ar1_FD, path = "../Manuscript", height = 2.1, width = 6)
```

```{r MA(1) FD}
## Test MA(1) model
ptm <- proc.time()

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
ma <- 0.5

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), "pnorm", B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks_F(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_ma1_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

print(proc.time() - ptm)

hist_ma1_FD

# Save the histogram figure
ggsave(filename = "hist_ma1_FD.pdf", plot = hist_ma1_FD, path = "../Manuscript", height = 2.1, width = 6)
```

```{r ARMA(1,1) FD}
## Test ARMA(1,1) model
ptm <- proc.time()

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
ar <- 0.5
ma <- 0.3

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n),
                                            "pnorm", B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ar = ar, 
                                                              ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n))$p.value)

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks_F(arima.sim(list(ar = ar, 
                                                              ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n))$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_arma_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

print(proc.time() - ptm)

hist_arma_FD

# Save the histogram figure
ggsave(filename = "hist_arma_FD.pdf", plot = hist_arma_FD, path = "../Manuscript", height = 2.1, width = 6)
```

```{r AR(2) FD}
## Test AR(2) model
ptm <- proc.time()

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
b1 <- 0.5
b2 <- 0.3

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                            "pnorm", 
                                            B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(order = c(2, 0, 0), 
                                                                   ar = c(b1, b2)), 
                                                              rand.gen=rnorm, 
                                                              sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)), 
                                                              n = n))$p.value)

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(order = c(2, 0, 0), 
                                                               ar = c(b1, b2)), 
                                                          rand.gen=rnorm, 
                                                          sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)), 
                                                          n = n))$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_ar2_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

print(proc.time() - ptm)

hist_ar2_FD

# Save the histogram figure
ggsave(filename = "hist_ar2_FD.pdf", plot = hist_ar2_FD, path = "../Manuscript", height = 2.1, width = 6)
```

```{r Gamma FD}
# Testing bootstrap with copulas for gamma distribution
test_gamma_FD <- function(x, dist, B = 100, wcopula = normalCopula) {

    # Get observed stat
    n <- length(x)
    m <- mean(x)
    v <- var(x)
    scale <- v/m
    shape <- m*m/v

    stat  <- ks.test(x, dist, shape = shape, scale = scale)$statistic

    # Get lag-1 sample auto-spearman rho
    rho  <-  cor(x[-1], x[-n], method = "spearman")
    r <- iRho(wcopula(), rho)
    wcop <- wcopula(r)

    # Parametric bootstrap to get an empirical distribution of stat
    stat.b <- double(n)

    for (i in 1:B) {
        # 1. The marginal distribution is the fitted dist
        # 2. There is temporal dependence
        u <- runif(n)
        for (j in 2:n) {
            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
        }

        # Transform the bootstrap sample and fit the parameters
        x.b <- qgamma(u, shape = shape, scale = scale)

        m.b <- mean(x.b)
        v.b <- var(x.b)
        scale.b <- v.b/m.b
        shape.b <- m.b*m.b/v.b

        # Calculate new test statistic
        stat.b[i] <- ks.test(x.b, dist, shape = shape.b, scale = scale.b)$statistic
    }

    # Return empirical p-value    
    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)

    counter <<- counter + 1
    cat(counter, "")

    return(p.value)
}

# Parametric bootstrap to solve fitted parameters for gamma distribution
test_parametric_gamma <- function(x, B = 1000) {

  # Summarize parameters
  m <- mean(x)
  v <- var(x)
  scale <- v/m
  shape <- m*m/v

  # Store KS statistic from using fitted parameters
  stat <- ks.test(x, "pgamma", shape = shape, scale = scale)$statistic

  # Parametric bootstrap to approximate the null distribution
  n <- length(x)
  stat.b <- double(B)
  for (i in 1:B) {
    x.b <- rgamma(n, shape = shape, scale = scale)

    m.b <- mean(x.b)
    v.b <- var(x.b)

    scale.b <- v.b/m.b
    shape.b <- m.b*m.b/v.b

    stat.b[i] <- ks.test(x.b, "pgamma", shape = shape.b, scale = scale.b)$statistic
  }

  # Return empirical p-value
  p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)

  counter <<- counter + 1
  cat(counter, "")
  list(p.value = p.value)
}

# Naive function that incorrectly uses fitted parameters for gamma distribution
test_super_naive_gamma <- function(x) {

  m <- mean(x)
  v <- var(x)
  scale <- v/m
  shape <- m*m/v

  p.value <- ks.test(x, "pgamma", shape = shape, scale = scale)$p.value
  list(p.value = p.value)
}

ptm <- proc.time()

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
shape <- 3
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_gamma_FD(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), "pgamma", B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- replicate(nrep, test_parametric_gamma(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value)

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_gamma_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

print(proc.time() - ptm)

hist_gamma_FD

# Save the histogram figure
ggsave(filename = "hist_gamma_FD.pdf", plot = hist_gamma_FD, path = "../Manuscript", height = 2.1, width = 6)
```

```{r GEV FD}
# Testing bootstrap with copulas for GEV distribution
test_gev_FD <- function(x, B = 100, wcopula = normalCopula) {

    n <- length(x)

    # Get observed stat
    fit <- gev.fit(x, show = FALSE)
    loc <- fit$mle[1]
    scale <- fit$mle[2]
    shape <- fit$mle[3]

    stat  <- ks.test(x, 'pgev', loc = loc, scale = scale, shape = shape)$statistic

    # Get lag-1 sample auto-spearman rho
    rho  <-  cor(x[-1], x[-n], method = "spearman")
    r <- iRho(wcopula(), rho)
    wcop <- wcopula(r)

    # Parametric bootstrap to get an empirical distribution of stat
    stat.b <- double(n)

    for (i in 1:B) {
        # 1. The marginal distribution is the fitted dist
        # 2. There is temporal dependence
        u <- runif(n)
        for (j in 2:n) {
            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
        }

        # Transform the bootstrap sample and fit the parameters
        x.b <- qgev(u, loc = loc, scale = scale, shape = shape)

        fit.b <- gev.fit(x.b, show = FALSE)
        loc.b <- fit.b$mle[1]
        scale.b <- fit.b$mle[2]
        shape.b <- fit.b$mle[3]

        # Calculate bootstrap test statistic
        stat.b[i] <- ks.test(x.b, 'pgev', loc = loc.b, scale = scale.b, shape = shape.b)$statistic
    }

    # Return empirical p-value    
    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)

    counter <<- counter + 1
    cat(counter, "")

    return(p.value)
}

# Parametric bootstrap to solve fitted parameters for GEV distribution
test_parametric_gev <- function(x, B = 1000) {

  # Summarize parameters
  fit <- gev.fit(x, show = FALSE)
  loc <- fit$mle[1]
  scale <- fit$mle[2]
  shape <- fit$mle[3]

  # Store KS statistic from using fitted parameters
  stat <- ks.test(x, "pgev", loc = loc, scale = scale, shape = shape)$statistic

  # Parametric bootstrap to approximate the null distribution
  n <- length(x)
  stat.b <- double(B)
  for (i in 1:B) {
    x.b <- rgev(n, loc = loc, scale = scale, shape = shape)

    fit.b <- gev.fit(x.b, show = FALSE)
    loc.b <- fit.b$mle[1]
    scale.b <- fit.b$mle[2]
    shape.b <- fit.b$mle[3]

    stat.b[i] <- ks.test(x.b, "pgev", loc.b, shape = shape.b, scale = scale.b)$statistic
  }

  # Return empirical p-value
  p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)

  counter <<- counter + 1
  cat(counter, "")
  list(p.value = p.value)
}

# Naive function that incorrectly uses fitted parameters for GEV distribution
test_super_naive_gev <- function(x) {

  fit <- gev.fit(x, show = FALSE)
  loc <- fit$mle[1]
  scale <- fit$mle[2]
  shape <- fit$mle[3]

  p.value <- ks.test(x, "pgev", loc = loc, scale = scale, shape = shape)$p.value
  list(p.value = p.value)
}

ptm <- proc.time()

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
loc <- 0
shape <- 0.2
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_gev_FD(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- suppressWarnings(replicate(nrep, test_parametric_gamma(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value))

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_gev_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

print(proc.time() - ptm)

hist_gev_FD

# Save the histogram figure
ggsave(filename = "hist_gev_FD.pdf", plot = hist_gev_FD, path = "../Manuscript", height = 2.1, width = 6)
```

```{r hist_ma1_arma_ar2_D}
load('results_ma1_D.RData')
model <- rep("MA(1)", 2000)
ma1 <- data_frame(results, model)

load('results_arma_D.RData')
model <- rep("ARMA(1, 1)", 2000)
arma <- data_frame(results, model)

load('results_ar2_D.RData')
model <- rep("AR(2)", 2000)
ar2 <- data_frame(results, model)

data <- rbind(ma1, arma, ar2)

data$model <- factor(data$model, levels = c("MA(1)", "ARMA(1, 1)", "AR(2)"))
data$histogram <- factor(data$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_ma1_arma_ar2_D <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(histogram~model, scales = "free_y")
hist_ma1_arma_ar2_D

ggsave(filename = "hist_ma1_arma_ar2_D.pdf", plot = hist_ma1_arma_ar2_D, path = "../Manuscript", height = 4.2, width = 6)
```

```{r hist_gamma_gev_D}
load('results_gamma_D.RData')
model <- rep("Gamma", 2000)
gamma <- data_frame(results, model)

load('results_gev_D.RData')
model <- rep("GEV", 2000)
gev <- data_frame(results, model)

data <- rbind(gamma, gev)

data$model <- factor(data$model, levels = c("Gamma", "GEV"))
data$histogram <- factor(data$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_gamma_gev_D <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(histogram~model, scales = "free_y")
hist_gamma_gev_D

ggsave(filename = "hist_gamma_gev_D.pdf", plot = hist_gamma_gev_D, path = "../Manuscript", height = 4.2, width = 6)
```

```{r hist_ma1_arma_ar2_FD}
load('results_ma1_FD.RData')
model <- rep("MA(1)", 3000)
ma1 <- data_frame(results, model)

load('results_arma_FD.RData')
model <- rep("ARMA(1, 1)", 3000)
arma <- data_frame(results, model)

load('results_ar2_FD.RData')
model <- rep("AR(2)", 3000)
ar2 <- data_frame(results, model)

data <- rbind(ma1, arma, ar2)

data$model <- factor(data$model, levels = c("MA(1)", "ARMA(1, 1)", "AR(2)"))
data$histogram <- factor(data$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_ma1_arma_ar2_FD <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_grid(histogram~model, scales = "free_y")
hist_ma1_arma_ar2_FD

ggsave(filename = "hist_ma1_arma_ar2_FD.pdf", plot = hist_ma1_arma_ar2_FD, path = "../Manuscript", height = 4.2, width = 6)
```

```{r hist_gamma_gev_FD}
load('results_gamma_FD.RData')
model <- rep("Gamma", 3000)
gamma <- data_frame(results, model)

load('results_gev_FD.RData')
model <- rep("GEV", 3000)
gev <- data_frame(results, model)

data <- rbind(gamma, gev)

data$model <- factor(data$model, levels = c("Gamma", "GEV"))
data$histogram <- factor(data$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_gamma_gev_FD <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(histogram~model, scales = "free_y", ncol = 2)
hist_gamma_gev_FD

ggsave(filename = "hist_gamma_gev_FD.pdf", plot = hist_gamma_gev_FD, path = "../Manuscript", height = 4.2, width = 6)
```

```{r AR(1) D2}
test_copula_D2 <- function(x, pdist, qdist, ..., B) {

    ## Get observed statistic
    n <- length(x) 
    stat  <- ks.test(x, pdist, ...)$statistic

    ## transform the data to standard normal scale and fit arma(1,1)
    zx <- qnorm(rank(x) / (n + 1))

    fit <- tseries::arma(zx, include.intercept = FALSE)
    ar <- fit$coef[1]
    ma <- fit$coef[2]

    ## Perform parametric bootstrap to get an empirical distribution of stat
    stat.b <- double(n)

    for (i in 1:B) {
        ## 1. The marginal distribution is the fitted dist
        ## 2. There is arma(1,1) dependence on the normal scale
        zx.b <- arima.sim(list(ar = ar, ma = ma), 
                          rand.gen=rnorm,
                          sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)),
                          n = n) # simulate from fit
        u <- pnorm(zx.b)
        # Transform bootstrap sample and fit the parameters
        x.b <- qdist(u, ...)

        # Gather bootstrap sample's test statistic
        stat.b[i] <- ks.test(x.b, pdist, ...)$statistic
    }

    # Return empirical p-value
    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)

    counter <<- counter + 1
    cat(counter, "")

    return(p.value)
}

# Set variables
n <- 100
ar <- 0.5
ma <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                                pdist = pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

#save(results, file = "results_ar1_D2.RData")

# Generate histograms plot
hist_ar1_D2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ar1_D2
```

```{r MA(1) D2}
# Set variables
n <- 100
ar <- 0.5
ma <- 0.5
counter <- 0
nrep <- 1000
B <- 100
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                                pdist = pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

#save(results, file = "results_ma1_D2.RData")

# Generate histograms plot
hist_ma1_D2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ma1_D2
```

```{r ARMA(1,1) D2}
# Set variables
n <- 100
ar <- 0.5
ma <- 0.5
counter <- 0
nrep <- 1000
B <- 100
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                                pdist = pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

#save(results, file = "results_arma_D2.RData")

# Generate histograms plot
hist_arma_D2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_arma_D2
```

```{r AR(2) D2}
# Set variables
n <- 100
b1 <- 0.5
b2 <- 0.3
counter <- 0
nrep <- 1000
B <- 100
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                                pdist = pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

#save(results, file = "results_ar2_D2.RData")

# Generate histograms plot
hist_ar2_D2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ar2_D2
```

```{r hist_ar1_ma1_arma_ar2_D2}
load('results_ar1_D2.RData')
model <- rep("AR(1)", 2000)
ar1 <- data_frame(results, model)

load('results_ma1_D2.RData')
model <- rep("MA(1)", 2000)
ma1 <- data_frame(results, model)

load('results_arma_D2.RData')
model <- rep("ARMA(1, 1)", 2000)
arma <- data_frame(results, model)

load('results_ar2_D2.RData')
model <- rep("AR(2)", 2000)
ar2 <- data_frame(results, model)

data <- rbind(ar1, ma1, arma, ar2)

data$model <- factor(data$model, levels = c("AR(1)", "MA(1)", "ARMA(1, 1)", "AR(2)"))
data$histogram <- factor(data$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_ar1_ma1_arma_ar2_D2 <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(histogram~model, scales = "free_y", ncol = 4)
hist_ar1_ma1_arma_ar2_D2

ggsave(filename = "hist_ar1_ma1_arma_ar2_D2.pdf", plot = hist_ar1_ma1_arma_ar2_D2, path = "../Manuscript", height = 4.2, width = 6)
```

```{r Gamma D2}
# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
shape <- 3
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                             pdist = pgamma, 
                                             qdist = qgamma,
                                             shape = shape,
                                             scale = scale,
                                             B = B))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                pdist = pgamma,
                                                shape = shape,
                                                scale = scale)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

save(results, file = "results_gamma_D2.RData")

# Generate histograms plot
hist_gamma_D2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_gamma_D2
```

```{r GEV D2}
# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
loc <- 0
shape <- 0.2
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
                                               pdist = pgev,
                                               qdist = qgev,
                                               loc = loc, 
                                               shape = shape,
                                               scale = scale,
                                               B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                 pdist = pgev,
                                                 loc = loc, 
                                                 shape = shape,
                                                 scale = scale)$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
p_values <- c(pvals_copula, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

save(results, file = "results_gev_D2.RData")

# Generate histograms plot
hist_gev_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_gev_D
```

```{r hist_gamma_gev_D2}
load('results_gamma_D2.RData')
model <- rep("Gamma", 2000)
gamma <- data_frame(results, model)

load('results_gev_D2.RData')
model <- rep("GEV", 2000)
gev <- data_frame(results, model)

data <- rbind(gamma, gev)

data$model <- factor(data$model, levels = c("Gamma", "GEV"))
data$histogram <- factor(data$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_gamma_gev_D2 <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(histogram~model, scales = "free_y")
hist_gamma_gev_D2

ggsave(filename = "hist_gamma_gev_D2.pdf", plot = hist_gamma_gev_D2, path = "../Manuscript", height = 4.2, width = 6)
```

```{r Autoarma}
source("autoarma.R")

# Test non-parametric bootstrap as a solution to fitted parameters
test_autoarma <- function(x, pdist, qdist, B, working) {
  p.value <- ks.arma(x = x, pdist = pdist, qdist = qdist, B = 1000, working = working)
  counter <<- counter + 1
  cat(counter, "")
  list(p.value = p.value)
}

# Naive function that incorrectly uses fitted parameters for gamma distribution
test_super_naive_autoarma <- function(x) {

  m <- mean(x)
  v <- var(x)
  scale <- v/m
  shape <- m*m/v

  p.value <- ks.test(x, "pgamma", shape = shape, scale = scale)$p.value
  list(p.value = p.value)
}

# Generate results
n_tests = 1000
n = 200
phi <- .3
theta <- .2
qdist <- function(u) qgamma(u, shape = 3, scale = 1)
pdist <- function(u) pgamma(u, shape = 3, scale = 1)
working <- "auto"
counter <- 0
pvals_autoarma <- replicate(n_tests, test_autoarma(x = genData(n, phi, theta, qdist), pdist = pdist, qdist = qdist, B = 1000, working = working)$p.value)
counter <- 0
pvals_naive <- replicate(n_tests, test_super_naive_autoarma(genData(n, phi, theta, qdist))$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Autoarma", n_tests), rep("Naive", n_tests))
p_values <- c(pvals_autoarma, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Naive", "Autoarma"))

# Generate histograms plot
hist_autoarma <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_autoarma

# Save the histogram figure
ggsave(filename = "hist_autoarma.pdf", plot = hist_autoarma, path = "../Manuscript", height = 2.1, width = 6)
```

### 2023-01-05 Code/Simulation.Rmd
Corrected naive case

@@
 
-# Test non-parametric bootstrap as a solution to fitted parameters
+# Test autoarma as a solution to correlated data
 test_autoarma <- function(x, pdist, qdist, B, working) {
@@
 
-# Naive function that incorrectly uses fitted parameters for gamma distribution
-test_super_naive_autoarma <- function(x) {
-
-  m <- mean(x)
-  v <- var(x)
-  scale <- v/m
-  shape <- m*m/v
-
-  p.value <- ks.test(x, "pgamma", shape = shape, scale = scale)$p.value
-  list(p.value = p.value)
-}
-
 # Generate results
-n_tests = 1000
-n = 200
+nrep <- 1000
+n <- 200
 phi <- .3
 theta <- .2
-qdist <- function(u) qgamma(u, shape = 3, scale = 1)
-pdist <- function(u) pgamma(u, shape = 3, scale = 1)
+shape <- 3
+scale <- 1
+qdist <- function(u) qgamma(u, shape = shape, scale = scale)
+pdist <- function(u) pgamma(u, shape = shape, scale = scale)
 working <- "auto"
 counter <- 0
-pvals_autoarma <- replicate(n_tests, test_autoarma(x = genData(n, phi, theta, qdist), pdist = pdist, qdist = qdist, B = 1000, working = working)$p.value)
-counter <- 0
-pvals_naive <- replicate(n_tests, test_super_naive_autoarma(genData(n, phi, theta, qdist))$p.value)
+pvals_autoarma <- replicate(nrep, test_autoarma(x = genData(n, phi, theta, qdist), pdist = pdist, qdist = qdist, B = 1000, working = working)$p.value)
+counter <- 0
+pvals_naive <- replicate(nrep, test_standard_ks(genData(n, phi, theta, qdist),
+                                                   pdist = pgamma,
+                                                   shape = shape, 
+                                                   scale = scale)$p.value)
 

### 2023-01-05 Code/Simulation.Rmd
Small typo

@@
 counter <- 0
-pvals_autoarma <- replicate(nrep, test_autoarma(x = genData(n, phi, theta, qdist), pdist = pdist, qdist = qdist, B = 1000, working = working)$p.value)
+pvals_autoarma <- replicate(nrep, test_autoarma(x = genData(n, phi, theta, qdist), 
+                                                   pdist = pdist, 
+                                                   qdist = qdist, 
+                                                   B = 1000, 
+                                                   working = working)$p.value)
 counter <- 0
@@
 # Create a master data_frame with all the results
-histogram <- c(rep("Autoarma", n_tests), rep("Naive", n_tests))
+histogram <- c(rep("Autoarma", nrep), rep("Naive", nrep))
 p_values <- c(pvals_autoarma, pvals_naive)

### 2023-01-05 Code/Simulation.Rmd
Testing auto arima for fitted + dependence

@@
 
-```{r Autoarma}
+```{r Autoarma D}
 source("autoarma.R")
@@
 ```
+
+```{r Autoarma FD}
+test_autoarma_FD <- function(x, pdist, qdist, B = 1000, working=c("auto", "2,2")) {
+    z <- qnorm(pdist(x))
+
+    n <- length(x)
+    m <- mean(x)
+    v <- var(x)
+    scale <- v/m
+    shape <- m*m/v
+
+    stat  <- ks.test(x, "pgamma", shape = shape, scale = scale)$statistic
+
+    if (working == "auto") {
+        fit <- forecast::auto.arima(z, ic = "aic", max.d = 0, max.D = 0, allowmean = FALSE)
+        ## stepwise=FALSE, approximation=FALSE)
+        ## working model: p.max = q.max = 5
+    } else {
+        pq <- as.numeric(unlist(strsplit(working, ",")))
+        fit <- arima(z, order = c(pq[1], 0, pq[2]), include.mean = FALSE) ## working arma(2, 2)
+    }
+    model <- list(ar = fit$model$phi, ma = fit$model$theta)
+
+    ## theoretical variance of arma; note the negative sign of theta; McLeod (1975)
+    sigma <- sqrt(ltsa::tacvfARMA(phi = model$ar, theta = - model$ma, maxLag = 0))
+
+    stat.b <- rep(0, B)
+    for (i in 1:B) {
+        z.b <- arima.sim(model, n = n)
+        ##   arma(1, 1) only: sd = sqrt (1 - ophi^2) / (1 + 2 * phi * theta + theta^2))
+        x.b <- qgamma(pnorm(z.b, mean = 0, sd = sigma), shape = shape, scale = scale)
+
+        m.b <- mean(x.b)
+        v.b <- var(x.b)
+        scale.b <- v.b/m.b
+        shape.b <- m.b*m.b/v.b
+
+        # Calculate new test statistic
+        stat.b[i] <- ks.test(x.b, "pgamma", shape = shape.b, scale = scale.b)$statistic
+    }
+    p.value <- mean(stat.b >= stat)
+
+    counter <<- counter + 1
+    cat(counter, "")
+    list(p.value = p.value)
+}
+
+# Generate results
+nrep <- 1000
+n <- 200
+phi <- .3
+theta <- .2
+shape <- 3
+scale <- 1
+qdist <- function(u) qgamma(u, shape = shape, scale = scale)
+pdist <- function(u) pgamma(u, shape = shape, scale = scale)
+working <- "auto"
+counter <- 0
+
+pvals_autoarma <- replicate(nrep, test_autoarma_FD(x = genData(n, phi, theta, qdist), 
+                                                   pdist = pdist, 
+                                                   qdist = qdist, 
+                                                   B = 1000, 
+                                                   working = working)$p.value)
+counter <- 0
+
+# P-vals from using parametric bootstrap
+pvals_parametric <- replicate(nrep, test_parametric_gamma(genData(n, phi, theta, qdist))$p.value)
+
+pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, phi, theta, qdist))$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Autoarma", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
+p_values <- c(pvals_autoarma, pvals_parametric, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Autoarma"))
+
+# Generate histograms plot
+hist_autoarma_FD <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_autoarma_FD
+
+# Save the histogram figure
+ggsave(filename = "hist_autoarma_FD.pdf", plot = hist_autoarma_FD, path = "../Manuscript", height = 2.1, width = 6)
+```

### 2023-01-09 Code/autoarma.R
Autoarma D and FD for Gamma and AR(2). Restructured code to have all functions together. Slight changes to autoarma.R

@@ -31,7 +31,7 @@ ks.arma <- function(x, pdist, qdist, B = 1000, working=c("auto", "2,2")) {
 qdist <- function(u) qgamma(u, shape = 3, scale = 1)
 pdist <- function(u) pgamma(u, shape = 3, scale = 1)
 
-genData <- function(n, phi, theta, qdist) {
+genData2 <- function(n, phi, theta, qdist) {
     x <- arima.sim(model = list(ar = phi, ma = theta), n = n)
     ## xbig <- arima.sim(model = list(ar = phi, ma = theta), n = 100000)
     ## sigma <- sd(xbig)

### 2023-01-10 manuscript/manuscript.tex
correction to KS stat scale
new method in section 3

@@
   \[
-    D^* = \sup_x | F_n^* (x)- F_{\hat\theta_n}^*(x) - B_n(x) |.
+    D^* = \sup_x | \sqrt{n}\left(F_n^* (x)- F_{\hat\theta_n}^*(x)\right) - B_n(x) |.
   \]
@@
 
-When the observed data $X_1, \ldots, X_n$ are not independent but serially
-dependent, the null distribution of the KS statistic $D_n$
-in~\eqref{eq:ks_standard} changes. For a
-stationary series, it may still be of interest to test whether the data come
-from a completely specified distribution~$F$. When the serial dependence is
+Here we consider the situation where the observed data $X_1, \ldots, X_n$ are
+not independent but serially dependent, and the hypothesized distribution $F$
+contains no unknown parameters. The null distribution of the KS statistic $D_n$
+in~\eqref{eq:ks_standard} changes with the serially dependence.
+When the serial dependence is
 positive, the effective sample size is less than~$n$. The testing statistic
@@
 dependence, which can be arbitrary in practice. A parametric bootstrap procedure
-would need model specification of the dependence, whereas the primary interest
+would need specify a model for the dependence, whereas the primary interest
 is to test the marginal distribution of the stationary series. A block
@@
 is the copula determined by the multivariate normal distribution. We propose to
-use a normal working copula with an AR(1) structure to approximate the serial
-dependence of the observations. Let $\hat\rho$ be the lag-1 sample auto
-Spearman's rho of the observed data. A normal copula of dimension~$n$ can be
-constructed with an AR(1) structure and its AR coefficient~$\psi$ is chosen to
-ensure that the Spearman's rho matches $\hat\rho$. Let $\psi(\hat\rho)$ denote
-this coefficient. The bootstrap procedure is as follows.
+use a normal working copula to approximate the serial
+dependence of the observations.
+
+The parameters of the working normal copula are
+estimated from fitting an auto-regressive moving average (ARMA) model to the
+observed data transformed to the standard normal scale. In particular, let
+$Z_i = \Phi\{ F(X_i)\}$, $i = 1, \ldots, n$, where $\Phi$ is the distribution
+function of the standard normal. Then we fit an ARMA$(p, q)$ model to
+$Z_1, \ldots, Z_n$ with AR order $p$ and MA order $q$ selected by the Akaike
+Information Criterion (AIC). This can be done with, for example, function
+\texttt{auto.arima()} from  R package \texttt{forecast}
+\citep{hyndman2008automatic}. Since it is known that the mean of $Z_i$'s are
+zero, it is necessary to set the intercept of the ARMA model as zero in the
+fitting process. The selected ARMA$(p, q)$ model with fitted
+parameters will be used as the working model to generate bootstrap sample with
+serial dependence mimicking that in the observed data. The unconditional
+variance $\sigma^2$ of the ARMA model can be obtained with function
+\texttt{tacvfARMA()} from R package \texttt{ltsa} \citep{mcleod2007algorithms}.
+
+The semiparametric bootstrap procedure is as follows.
 \begin{enumerate}
 \item
-  Generate $Z_1, \ldots, Z_n$ from an AR(1) process with autocorrelation
-  coefficient $\psi(\hat\rho)$ such that the $Z_i$'s are $N(0, 1)$ variables.
+  Generate $Z_1^*, \ldots, Z_n^*$ from the fitted ARMA$(p, q)$ process with
+  innovation variance $1 / \sigma^2$ such that the $Z_i$'s are marginally
+  standard normal variables.
 \item
-  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i)]$,  $i = 1, \ldots, n$,
-  where $\Phi$ is the distribution function of $N(0, 1)$.
+  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i^*)]$,  $i = 1, \ldots, n$.
 \item
@@
 is only approximated. The closer the approximation is to the truth, the better
-performance of the size of the KS test  If the true dependence is indeed a
-normal copula with an AR(1) structure, this method is exact. When the true
-dependence is not AR(1), it may still give a reasonable approximation that can
-be useful for practical purposes. More complicated working models other
-than the AR(1) process could be used, but we focus here on the AR(1) model.
+performance of the size of the KS test, The dependence structure determined by
+the working ARMA process approximates a wide class of dependence structures.
+If the true dependence indeed has an ARMA structure, this method is exact. When
+the true dependence is not covered the ARMA model, the working model may still
+give a reasonable approximation that can
+be useful for practical purposes.
 
@@
 \end{figure}
+
+\jy{to be rewritten when the figures are generated.}
+\jy{I suggest that we keep using gamma as the marginal distribution throughout.}
 

### 2023-01-10 manuscript/manuscript.tex
bootstrap steps for section 4

@@
 
-The invalidity of the statndard statistic for serially dependent data can be
+The invalidity of the standard statistic for serially dependent data can be
 illustrated by a simple simulation study. Consider a first-order autoregressive
@@
 observed data transformed to the standard normal scale. In particular, let
-$Z_i = \Phi\{ F(X_i)\}$, $i = 1, \ldots, n$, where $\Phi$ is the distribution
+$Z_i = \Phi^{-1}\{ F(X_i)\}$, $i = 1, \ldots, n$, where $\Phi$ is the distribution
 function of the standard normal. Then we fit an ARMA$(p, q)$ model to
@@
 
-The procedure demonstrated in Section~\ref{sec:dependence} works when the data
-is dependent and the hypothesized distribution is completely specified. However,
-this is not practical. In practice we do not know the parameters of the
-hypothesized distribution. Therefore, it is valuable to have a procedure that
-corrects for both fitted parameters and serially dependent data. The remedy
-using copulas can be modified to be effective in the case where both assumptions
-must be violated. The null hypothesis is equivalent to Section~\ref{sec:fitted}
-and the test statistic is equal to Equation~\eqref{eq:ks_fitted}. The bootstrap
-procedure in Section~\ref{sec:fitted} is no longer valid because the serial
-dependence is not accounted for. Let $r$ be the AR(1) coefficient of the normal
-copula that matches the sample first-order Spearman's rho of the observed data
-as obtained by the \texttt{iRho} function in the \textsf{copula} package
-\citep{Rpkg:copula}. We propose the following bootstrap procedure to assess the
+For testing distributions with unspecified parameters with serially dependent
+data, we can modify the procedure in the last section. In preparation, let
+$\hat\theta_n$ be the marginally fitted parameters, and let
+$Z_i = \Phi^{-1} \{F_{\hat\theta_n}(X_i)\}$, $i = 1, \ldots, n$.
+For $Z_i$'s that are marginally standard normal variables, we fit an
+ARMA$(p,q)$ model with AR order $p$ and MA order $q$ selected by AIC as in the
+last section. Let $\sigma^2$ be the unconditional variance of the fitted ARMA
+process. We propose the following bootstrap procedure to assess the
 significance of the observed KS statistic.
@@
 \item
-  Generate $Z_1, \ldots, Z_n$ from an AR(1) process with autocorrelation
-  coefficient $r$ such that the $Z_i$'s are $N(0, 1)$ variables.
+  Generate $Z_1^*, \ldots, Z_n^*$ from the fitted ARMA$(p, q)$ process
+  with innovation variance $1 / \sigma^2$ such that the $Z_i$'s are $N(0, 1)$ variables.
 \item

### 2023-01-12 manuscript/manuscript.tex
edits and comments through section 3

@@
 distributions containing estimated parameters. For example, it has been
-``discovered'' multiple times that the test is too conservative when
+``discovered'' multiple times that the test is too conservative when the 
 hypothesized distribution has parameters that need to be estimated.
@@
 samples, the tests can be performed with a table \citep{smirnov1948table}.
-Critical values for small samples ($n \le 35$) has also been given
+Critical values for small samples ($n \le 35$) have also been given
 \citep{massey1951kolmogorov}. The KS test is available in popular
@@
 distribution of the KS statistic for discontinuous distributions has been
-efficiently addressed by \citet{dimitrova2020computing} with an
+efficiently addressed by \citet{dimitrova2020computing} with a
 companion R package \textsf{KSgeneral}. Although a common misuse of KS test, the
-issue with discontinuous or data is not our focus.
+issue with discontinuous data is not our focus.
 
@@
 such ways. In fact, using fitted parameters in place of the true parameters in
-KS test is long known to yield extremely conservative results
+KS test has been long known to yield extremely conservative results
 \citep[e.g.,][]{lilliefors1967kolmogorov}. This problem can be solved by
 parametric bootstrap \citep{efron1985bootstrap, hall1991two}, where
-bootstrap samples of the testing statistics are constructed from samples
+bootstrap samples of the test statistics are constructed from samples
 generated from the fitted hypothesized distribution. A nonparametric bootstrap
-solution is not trivial because the a nonparametric bootstrap sample of the
-observed data have ties, which would not happen for continuous distributions.
-\citet{babu2004goodness} derived the bias of standard nonparametric bootstrap and
+solution is not trivial because a nonparametric bootstrap sample of the
+observed data has ties, which would not happen for continuous distributions.
+\citet{babu2004goodness} derived the bias of the standard nonparametric 
+bootstrap and
 showed how to correct it. They further noted that both parametric and
-non-parametric procedures lead to correct asymptotic levels.
+nonparametric procedures lead to correct asymptotic levels.
 
@@
 \citet{durilleul1992lack} demonstrates that a naive application of
-the KS statistic is too liberal for medium-to-high positive serieal dependence,
+the KS statistic is too liberal for medium-to-high positive serial dependence,
 and that for negative dependence, the behavior is asymmetrical. For remedies,
-\citet{weiss1978modification} provides a procedure that is applicable specifically for data
+\citet{weiss1978modification} provides a procedure that is applicable 
+specifically for data
 modeled by the second-order auto-regressive (AR) process where the AR parameters
-are known. \citet{lanzante2021testing} tests various strategies for dealing with temporal
+are known. \citet{lanzante2021testing} tests various strategies for dealing with
+temporal
 dependence and concludes that a test based on Monte-Carlo simulations performed
@@
 remedy is detailed and performed alongside the misuse to show its positive
-effects. In order to set up the demonstrations, simulated data is used
+effects. In order to set up the demonstrations, simulated data are used
 throughout. The remedies are also performed on various families of
@@
 issue. Section~\ref{sec:dependence} investigates the scenario where the data of
-the empirical distribution is serially dependent. A bootstrap procedure
+the empirical distribution are serially dependent. A bootstrap procedure
 employing copulas to account for dependence is proposed as a working solution.
@@
   H_0: \text{the random sample $X_1, \ldots, X_n$
-    comes from a distribution $F_\theta$ with some $\theta$.}
+    comes from a distribution $F_\theta$ for some $\theta$.}
 \]
@@
 distribution with sample size $n = 100$. The sample mean and sample standard
-deviation were used as $\hat\theta_n$. The p-value of the testing
+deviation were used as $\hat\theta_n$. The p-value of the test
 statistic~$D_n$ in~\eqref{eq:ks_fitted} was obtained by naively calling the
@@
 $N(\bar X, s^2)$ where $\bar X$ is the sample mean and $s^2$ is the sample
-variance. This experiment was repeated for 1000 times and the histogram of the
+variance. This experiment was repeated 1000 times and the histogram of the
 1000 p-values are displayed in Figure~\ref{fig:hist_fitted}. If the test were
@@
 To fix the problem, parametric bootstrap can be used to approximate the null
-distribution of the testing statistic~$D_n$:
+distribution of the test statistic~$D_n$:
 \begin{enumerate}
@@
 \item
-  Fit $F_\theta$ to the sample and obtain estimate $\hat\theta_n^*$ of $\theta$.
+  Fit $F_\theta$ to $X_1^*,...,X_n^*$ \eds{verify edit} and obtain estimate 
+	$\hat\theta_n^*$ of $\theta$.
 \item
@@
   \]
+	\eds{please explicitly define $F_{\hat\theta_n}^*(x)$ here.  Or should it be
+	$F_{{\hat{\theta}_n}^*}(x)$ instead? (Note placement of *)}
 \item
   Repeat the previous steps a large number~$B$ times and use the empirical
-  distribution of $D^*$ to approximate the null distribution of the observed
+  distribution of $D_n^*$ to approximate the null distribution of the observed
   statistic.
 \end{enumerate}
-The p-value of $D_n$ is approximated by the proportion of $D_n^*$'s that are
+The p-value of $D_n$ is approximated by the proportion of the $D_n^*$ 
+statistics that are
 greater than or equal to~$D_n$.
@@
 Nonparametric bootstrap can also be used to approximate the null distribution
-of the testing statistic with the bias correction from \citet{babu2004goodness}:
+of the test statistic with the bias correction from \citet{babu2004goodness}:
 \begin{enumerate}
@@
 \item
-  Fit $F_\theta$ to the sample and obtain estimate $\hat\theta_n^*$ of $\theta$.
+  Fit $F_\theta$ to $X_1^*,...,X_n^*$ \eds{verify edit} and obtain estimate 
+	$\hat\theta_n^*$ of $\theta$.
 \item
-  Obtain the empirical distribution function of the random sample $F_n^*$
+  Obtain the empirical distribution function $F_n^*$ of
+  $X_1^*, \ldots,  X_n^*$. \eds{verify edit}
 \item
@@
   \]
+	\eds{do we want an n subscript on $D^*$?  It is not consistently used below.}
   where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
-  bias term \citep{babu2004goodness}
+  bias term \citep{babu2004goodness}.
+	\eds{same question about $F_{\hat\theta_n}^*(x)$ as above}
 \item
@@
   distribution of $D^*$ to approximate the null distribution of the observed
-  statistic.
+  statistic. \eds{do we want an n subscript on $D^*$}
 \end{enumerate}
-The p-value of $D_n$ is, again, approximated by the proportion of $D_n^*$'s that
-are greater than or equal to~$D_n$.
+The p-value of $D_n$ is, again, approximated by the proportion of the $D_n^*$
+statistics that
+are greater than or equal to~$D_n$. \eds{do we want an n subscript on $D^*$}
 
@@
 p-values from the parametric and nonparametric bootstrap procedures,
-respectively. This time, both samples of the p-values appear to come from the
+respectively. This time, both samples of p-values appear to come from
 standard uniform distributions.
@@
 contains no unknown parameters. The null distribution of the KS statistic $D_n$
-in~\eqref{eq:ks_standard} changes with the serially dependence.
+in~\eqref{eq:ks_standard} changes with serial dependence.
 When the serial dependence is
-positive, the effective sample size is less than~$n$. The testing statistic
-would be stochastically greater than that obtained from independent data, making
-it more likely to reject the null hypothesis than it should. So the test is
-liberal. The reasoning is similar when the serial dependence is negative,
-in which case, the test is conservative.
+positive, the effective sample size is less than~$n$. The test statistic
+would be stochastically greater than that obtained from independent data, 
+resulting in a test that is too liberal (i.e., the null hypothesis is rejected
+more often than it should). The reasoning is similar when the serial dependence 
+is negative, in which case, the test is conservative.
 
@@
 $\psi$ values are displayed in Figure~\ref{fig:hist_correlation}. When
-$\phi \ne 0$, the histograms do not look like to be generated from a standard
+$\phi \ne 0$, the histograms do not look likely to be generated from a standard
 uniform distribution. Positive $\psi$ values led to liberal p-values while
-negative $\psi$ values led to conservative p-values. The larger the magnitude of
+negative $\psi$ values led to conservative p-values. 
+\eds{can p-values be liberal or conservative?  Not sure, but I think I have only
+ heard of tests being described in this way} 
+The larger the magnitude of
 $\psi$, the bigger the deviation from the desired level.
@@
 
-A complete remedy for the KS tests with serially dependent data is
+A complete remedy for KS tests with serially dependent data is
 challenging. The null distribution depends on the structure of the serial
 dependence, which can be arbitrary in practice. A parametric bootstrap procedure
-would need specify a model for the dependence, whereas the primary interest
+would need to specify a model for the dependence, whereas the primary interest
 is to test the marginal distribution of the stationary series. A block
 nonparametric bootstrap for stationary data \citep{kunsch1989jackknife} is
-attempting, but the counterpart of a bias correction as in
+tempting, but the counterpart of a bias correction as in
 \citet{babu2004goodness} is not available yet. Is there any approach that does
-not require fully specification of the dependence of the stationary process
+not require full specification of the dependence of the stationary process,
 but still gives reasonably satisfactory correction to the size of the KS test in
@@
 \texttt{auto.arima()} from  R package \texttt{forecast}
-\citep{hyndman2008automatic}. Since it is known that the mean of $Z_i$'s are
+\citep{hyndman2008automatic}. Since it is known that the mean of $Z_i$'s is
 zero, it is necessary to set the intercept of the ARMA model as zero in the
 fitting process. The selected ARMA$(p, q)$ model with fitted
-parameters will be used as the working model to generate bootstrap sample with
+parameters will be used as the working model to generate bootstrap samples with
 serial dependence mimicking that in the observed data. The unconditional
@@
   Generate $Z_1^*, \ldots, Z_n^*$ from the fitted ARMA$(p, q)$ process with
-  innovation variance $1 / \sigma^2$ such that the $Z_i$'s are marginally
+  innovation \eds{? inverse?} variance $1 / \sigma^2$ such that the $Z_i$'s are
+	marginally
   standard normal variables.
@@
   \]
+	\eds{n subscript for $D^*$? Not consistently used.}
 \item
@@
 \end{enumerate}
-The p-value of $D_n$ is, again, approximated by the proportion of $D_n^*$'s that
-are greater than or equal to~$D_n$.
+The p-value of $D_n$ is, again, approximated by the proportion of the $D_n^*$
+statistics that are greater than or equal to~$D_n$. \eds{n subscript for $D^*$?}
 
@@
 is only approximated. The closer the approximation is to the truth, the better
-performance of the size of the KS test, The dependence structure determined by
+performance of the size of the KS test. The dependence structure determined by
 the working ARMA process approximates a wide class of dependence structures.
 If the true dependence indeed has an ARMA structure, this method is exact. When
-the true dependence is not covered the ARMA model, the working model may still
-give a reasonable approximation that can
+the true dependence is not covered by the ARMA model, the working model may 
+still give a reasonable approximation that can
 be useful for practical purposes.
@@
   standard KS test. The Copula plot (right) is the histogram of p-values from
-  implementing parametric bootstrap with copulas for dependence. In each case,
+  implementing the parametric \eds{semiparametric?} bootstrap with copulas for
+	dependence. In each case,
   $1000$ replicate tests were performed with the data generated from an AR(1)

### 2023-01-13 manuscript/manuscript.tex
addressed comments from elizabeth

@@
 nonparametric bootstrap;
-parametric bootstrap.
+parametric bootstrap;
+working dependence.
 \end{abstract}
@@
 \item
-  Fit $F_\theta$ to $X_1^*,...,X_n^*$ \eds{verify edit} and obtain estimate 
+  Fit $F_\theta$ to $X_1^*,...,X_n^*$ and obtain estimate 
 	$\hat\theta_n^*$ of $\theta$.
@@
   \[
-    D_n^* = \sqrt{n} \sup_x | F_n^* (x)- F_{\hat\theta_n}^*(x) |.
+    D_n^* = \sqrt{n} \sup_x | F_n^* (x)- F_{\hat\theta_n^*}(x) |.
   \]
-	\eds{please explicitly define $F_{\hat\theta_n}^*(x)$ here.  Or should it be
-	$F_{{\hat{\theta}_n}^*}(x)$ instead? (Note placement of *)}
 \item
@@
   \[
-    D^* = \sup_x | \sqrt{n}\left(F_n^* (x)- F_{\hat\theta_n}^*(x)\right) - B_n(x) |.
+    D_n^* = \sup_x | \sqrt{n}\left(F_n^* (x)- F_{\hat\theta_n^*}(x)\right) - B_n(x) |.
   \]
-	\eds{do we want an n subscript on $D^*$?  It is not consistently used below.}
   where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
   bias term \citep{babu2004goodness}.
-	\eds{same question about $F_{\hat\theta_n}^*(x)$ as above}
 \item
   Repeat the previous steps a large number $B$ times and use the empirical
-  distribution of $D^*$ to approximate the null distribution of the observed
-  statistic. \eds{do we want an n subscript on $D^*$}
+  distribution of $D_n^*$ to approximate the null distribution of the observed
+  statistic. 
 \end{enumerate}
 The p-value of $D_n$ is, again, approximated by the proportion of the $D_n^*$
-statistics that
-are greater than or equal to~$D_n$. \eds{do we want an n subscript on $D^*$}
+statistics that are greater than or equal to~$D_n$.
 
@@
 $\phi \ne 0$, the histograms do not look likely to be generated from a standard
-uniform distribution. Positive $\psi$ values led to liberal p-values while
-negative $\psi$ values led to conservative p-values. 
-\eds{can p-values be liberal or conservative?  Not sure, but I think I have only
- heard of tests being described in this way} 
-The larger the magnitude of
+uniform distribution. Positive $\psi$ values led to p-values with a distribution
+function higher than the standard uniform distribution function and, hence,
+conservative tests. Negative $\psi$ values led to p-values with a distribution
+function lower than the standard uniform distribution and, hence, liberal
+tests. The larger the magnitude of
 $\psi$, the bigger the deviation from the desired level.
@@
 zero, it is necessary to set the intercept of the ARMA model as zero in the
-fitting process. The selected ARMA$(p, q)$ model with fitted
+fitting process. This restriction turned out to be critical in our
+investigation; having the intercept estimated does not lead to desired p-value
+distributions in the following bootstrap process.
+The selected ARMA$(p, q)$ model with fitted
 parameters will be used as the working model to generate bootstrap samples with
@@
   innovation \eds{? inverse?} variance $1 / \sigma^2$ such that the $Z_i$'s are
-	marginally
+	marginally \jy{yes, it means the innovation series of an ARMA process.}
   standard normal variables.
@@
   \[
-    D^* = \sup_x \lvert F_n^* (x)- F(x) \rvert.
+    D_n^* = \sup_x \lvert F_n^* (x)- F(x) \rvert.
   \]
-	\eds{n subscript for $D^*$? Not consistently used.}
 \item
@@
 The p-value of $D_n$ is, again, approximated by the proportion of the $D_n^*$
-statistics that are greater than or equal to~$D_n$. \eds{n subscript for $D^*$?}
+statistics that are greater than or equal to~$D_n$.
 
@@
 parametrically specified while the dependence structure of the stationary series
-is only approximated. The closer the approximation is to the truth, the better
-performance of the size of the KS test. The dependence structure determined by
-the working ARMA process approximates a wide class of dependence structures.
+is only approximated by that of an ARMA process with normal distributions.
+The closer the approximation is to the truth, the better
+performance of the size of the KS test. The normal copula of the working ARMA
+process provides a wide class of dependence structures.
 If the true dependence indeed has an ARMA structure, this method is exact. When

### 2023-01-14 manuscript/manuscript.tex
simulation setting suggestions

@@
 
+\jy{Simulation study: let's use two distributions:
+  $N(8, 8)$ and $\Gamma(8, 1)$. These two distributions have the same means and
+  variances. So we could use them to study powers of the tests too.}
+
 In the same simulation study, p-values were obtained for the 1000 replicates
@@
 is negative, in which case, the test is conservative.
+
+\jy{For the same two marginal distributions $N(8, 8)$ and $\Gamma(8, 1)$, let's
+  generate data from dependence structures of AR(1) with two coefficients
+  $\psi \in \{ -0. 5, 0.5\}$.}
 
@@
 
+\jy{Here we work on the same marginal distributions $N(8, 8)$ and $\Gamma(8, 1)$
+  with different dependence structures:
+  ARMA(1, 1); MA(2); AR(2)
+  }
 Continuing with the simulation study, 
@@
 
+\jy{need a paragraph to describe the misuse and explain the results. Repeat the
+  study at the begining of the last section.}
+
 For testing distributions with unspecified parameters with serially dependent
@@
 \item
-  Fit $F_\theta$ to the sample $X_1^*, \ldots, X_n^*$ and obtain estimator
-  $\hat\theta_n^*$
+  Fit $F_\theta$ to the bootstrap sample $X_1^*, \ldots, X_n^*$ and obtain estimator
+  $\hat\theta_n^*$ of $\theta$.
 \item
@@
 \end{enumerate}
+
+\jy{For the simulation study, repeat the study at the end of the last section.}
 

### 2023-03-14 Code/ksfitted.R
concise function ks.test.fitted()

@@ -1,0 +1,80 @@
+##' Distribution Functions with Given Parameters
+##'
+##' Generate a (d, p, q, or r) function of a distribution
+##'
+##' This function creates a function for a distribution with given parameters
+##' and a desired usage (d, p, q, or r).
+##'
+##' @param dist A string specificing the distribution, assuming function names
+##' prefixed with (d, p, q, or r) are available.
+##' @param param A named vector specifying the parameters of the distribution
+##' @param fn A character of `d`, `p`, `q`, or `r` for density, distribution,
+##' quantile, and random number generation.
+##' @return A function with a single argument while other parameters specified
+##' through the input `param`.
+##' 
+fitteddist <- function(dist, param, fn) {
+    nm <- names(param); l <- length(param)
+    fun <- get(paste0(fn, dist))
+    f <- formals(fun)
+    args <- names(f)
+    m <- match(nm, args)
+    formals(fun) <- c(f[c(1, m)], f[-c(1, m)])
+    myfun <- function(z) {}
+    body(myfun) <- parse(
+        text = paste("fun(z,", paste0("param[", 1L:l, "]", collapse = ", "), ")"))
+    myfun
+}
+
+
+##' Kolmogorov-Smirnov Tests with Fitted Parameters and Serial Dependence
+##'
+##' Performs a one-sample K-S test with fitted parameters and serial dependence
+##'
+##' This function allows fitted parameters through maximim likelihood when
+##' performing K-S test for commonly used distributions via parametric
+##' bootstrap. Serial dependence in allowed and preserved in bootstrap by a
+##' auto-selected working ARMA model for the residuals on the normal scale.
+##' 
+##' @param x a numeric vector of data values.
+##' @param dist a string of the name of the hypothesized distribution
+##' @param B number of bootstrap replicates
+##' @param fit if TRUE, test performed at the fitted parameter
+##' @param serial if TRUE, account for serial dependence via an auto-selected
+##' working ARMA model
+##' @param param a named vector for the hypothesized distribution. If fit ==
+##' TRUE, it will be used as the starting value for fitting
+ks.test.fitted <- function(x, dist, B = 1000, fit = TRUE, serial = FALSE,
+                         param = c()) {
[…]

### 2023-03-14 Code/try.R

@@ -1,0 +1,50 @@
+source("tacvfARMA.R")
+source("ksfitted.R")
+
+### fitted distribution
+n <- 200
+param <- c(shape = 2, scale = 3)
+dist <- "gamma"
+start <- c(shape = 1, scale = 1)
+
+nrep <- 2
+
+gm.f <- replicate(nrep, ks.test.fitted(rgamma(n, shape = 2, scale = 3), "gamma", param = start, fit = TRUE, serial = FALSE)$p.value)
+
+nm.f <- replicate(nrep, ks.test.fitted(rnorm(n, mean = 1, sd = 2), "norm", param = c(mean = 0, sd = 1), fit = TRUE, serial = FALSE)$p.value)
+
+### serial dependence with known distribution
+
+genData <- function(n, phi, theta, qdist) {
+    x <- arima.sim(model = list(ar = phi, ma = theta), n = n)
+    ## xbig <- arima.sim(model = list(ar = phi, ma = theta), n = 100000)
+    ## sigma <- sd(xbig)
+    sigma <- sqrt(tacvfARMA.my(phi = phi, theta = - theta, maxLag = 0))
+    qdist(pnorm(x, sd = sigma))
+}
+
+gmqdist <- function(x) qgamma(x, shape = 3, scale = 2)
+gm.s <- replicate(nrep, ks.test.fitted(genData(n, .3, numeric(0), gmqdist), "gamma", param = c(shape = 3, scale = 2), fit = FALSE, serial = TRUE)$p.value)
+## if serial dependence is ignored
+gm._ <- replicate(nrep, ks.test.fitted(genData(n, .3, numeric(0), gmqdist), "gamma", param = c(shape = 3, scale = 2), fit = FALSE, serial = FALSE)$p.value)
+
+
+nmqdist <- function(x) qnorm(x, mean = 1, sd = 2)
+nm.s <- replicate(nrep, ks.test.fitted(genData(n, .3, numeric(0), nmqdist), "norm", param = c(mean = 1, sd = 2), fit = FALSE, serial = TRUE)$p.value)
+nm._ <- replicate(nrep, ks.test.fitted(genData(n, .3, numeric(0), nmqdist), "norm", param = c(mean = 1, sd = 2), fit = FALSE, serial = FALSE)$p.value)
+
+### serial dependence with fitted distribution
+
[…]

### 2023-03-14 Code/try.R
minor fix

@@ -45,6 +45,6 @@ nm.s.f <- replicate(nrep, ks.test.fitted(genData(n, .3, numeric(0), nmqdist), "n
 nm._.f <- replicate(nrep, ks.test.fitted(genData(n, .3, numeric(0), nmqdist), "norm", param = c(mean = 1, sd = 2), fit = TRUE, serial = FALSE)$p.value)
 
 save(gm.f, nm.f
-     gm.s, gm._, nm.s, nm._
+     gm.s, gm._, nm.s, nm._,
      gm.s.f, gm._.f, nm.s.f, nm._.f,
      file = "sim.rda")

### 2023-03-14 Code/try.R
minor fix

@@ -44,7 +44,7 @@ nm.s.f <- replicate(nrep, ks.test.fitted(genData(n, .3, numeric(0), nmqdist), "n
 ## if serial dependence is ignored
 nm._.f <- replicate(nrep, ks.test.fitted(genData(n, .3, numeric(0), nmqdist), "norm", param = c(mean = 1, sd = 2), fit = TRUE, serial = FALSE)$p.value)
 
-save(gm.f, nm.f
+save(gm.f, nm.f,
      gm.s, gm._, nm.s, nm._,
      gm.s.f, gm._.f, nm.s.f, nm._.f,
      file = "sim.rda")

### 2023-03-14 manuscript/manuscript.tex
bootstrap for fitted distribution with serial dependence

@@
 \citep{massey1951kolmogorov}. The KS test is available in popular
-statistical software packages, such as function \texttt{ks.test} in R package
+statistical software packages, such as function \texttt{ks.test()} in R package
 \textsf{stats} \citep{R, marsaglia2003evaluating}.
@@
 throughout. The remedies are also performed on various families of
-distributions.
+distributions. An R implementation of the proposed methods will be available
+after the paper is published.
 
@@
 The p-value of $D_n$ is, again, approximated by the proportion of the $D_n^*$
-statistics that are greater than or equal to~$D_n$.
+statistics that are greater than or equal to~$D_n$. Note that the step~1 and
+step~4 are different from the parametric bootstrap version.
 
@@
 not independent but serially dependent, and the hypothesized distribution $F$
-contains no unknown parameters. The null distribution of the KS statistic $D_n$
-in~\eqref{eq:ks_standard} changes with serial dependence.
+contains no unknown parameters. That is,
+\[
+H_0: \text{$X_i$'s have marginal distribution $F$.}
+\]
+The KS statistic $D_n$ in~\eqref{eq:ks_standard}
+is still a good measure of deviation from the null hypothesis. Nonetheless, the
+null distribution of $F_n$ changes when there is serial dependence.
 When the serial dependence is
@@
 serial dependence mimicking that in the observed data. The unconditional
-variance $\sigma^2$ of the ARMA model can be obtained with function
+variance $\sigma^2$ of the ARMA model with unit innovation variance can be
+obtained with function
 \texttt{tacvfARMA()} from R package \texttt{ltsa} \citep{mcleod2007algorithms}.
@@
 \jy{to be rewritten when the figures are generated.}
-\jy{I suggest that we keep using gamma as the marginal distribution throughout.}
+\jy{I suggest that we keep using gamma as the marginal distribution
+  throughout. Elizabeth, let's finalize the settings next time we meet. I've
+  implemented a concise version of the test.}
 
@@
 
-\jy{need a paragraph to describe the misuse and explain the results. Repeat the
-  study at the begining of the last section.}
+When the observed sample $X_1, \ldots, X_n$ is no longer a random sample but
+a serially dependent stationary series, we may still be interested in testing
+whether marginally each $X_i$ follows hypothesized distribution with unknown
+parameters. That is, the null hypothesis is
+\[
+H_0: \text{$X_i$'s have marginal distribution $F_\theta$ for some $\theta$}.
+\]
+The testing statistic $D_n$ in Equation~\eqref{eq:ks_fitted} still measures the
+deviation from $H_0$, but its null distribution depends on the serial
+dependence. The bootstrap procedure in the last section can be adapted to handle
+this situation.
 
-For testing distributions with unspecified parameters with serially dependent
-data, we can modify the procedure in the last section. In preparation, let
-$\hat\theta_n$ be the marginally fitted parameters, and let
-$Z_i = \Phi^{-1} \{F_{\hat\theta_n}(X_i)\}$, $i = 1, \ldots, n$.
-For $Z_i$'s that are marginally standard normal variables, we fit an
-ARMA$(p,q)$ model with AR order $p$ and MA order $q$ selected by AIC as in the
-last section. Let $\sigma^2$ be the unconditional variance of the fitted ARMA
-process. We propose the following bootstrap procedure to assess the
-significance of the observed KS statistic.
+Specifically, let $\hat\theta_n$ be the marginally fitted parameters, and
+$Z_i = \Phi^{-1} \{F_{\hat\theta_n}(X_i)\}$, $i = 1, \ldots, n$ be a
+transformation of the observed data onto the standard normal scale using the
+fitted parameters $\hat\theta_n$. We then fit an ARMA model with orders
+selected by the AIC using function \texttt{auto.arima()} from R package
+\texttt{forecase}. This ARMA model will be used as the working model to
+introduce serial dependence in the bootstrap samples. Similarly, we obtain the
+unconditional variance $\sigma^2$ of the ARMA process with unit innovation
+variance. Our semiparametric bootstrap procedure is as follows
 
@@
 \item
-  Generate $Z_1^*, \ldots, Z_n^*$ from the fitted ARMA$(p, q)$ process
-  with innovation variance $1 / \sigma^2$ such that the $Z_i$'s are $N(0, 1)$ variables.
+  Generate $Z_1^*, \ldots, Z_n^*$ from the working ARMA$(p, q)$ model with
+  innovation variance $1 / \sigma^2$ such that the $Z_i$'s are marginally
+  standard normal variables.
 \item
-  Form a bootstrap sample $X_i^* = F^{-1}_{\hat\theta_n} [\Phi(Z_i)]$,
-  $i = 1, \ldots, n$, whose first-order sample Spearman's rho matches that of
-  the observed data.
+  Form a bootstrap sample
+  $X_i^* = F_{\hat\theta_n}^{-1} [\Phi(Z_i^*)]$, $i = 1, \ldots, n$.
 \item
-  Fit $F_\theta$ to the bootstrap sample $X_1^*, \ldots, X_n^*$ and obtain estimator
-  $\hat\theta_n^*$ of $\theta$.
+  Fir $F_\theta$ to $X_1^*, \ldots, X_n^*$ to obtain estimate $\hat\theta_n^*$
+  of $\theta$.
 \item
@@
   \[
-    D^* = \sup_x \lvert F_n^* (x)- F_{\hat\theta_n^*}(x) \rvert.
+    D_n^* = \sup_x \lvert F_n^* (x) - F_{\hat\theta_n}^* (x) \rvert.
   \]
@@
 \end{enumerate}
+The p-value of $D_n$ is approximated by the proportion of the $D_n^*$
+statistics that are greater than or equal to~$D_n$. Compared to the algorithm in
+the last section, here we use $F_{\hat\theta_n}$ and $F_{\hat\theta_n}^*$ in
+place of the known~$F$.
 

### 2023-03-23 Code/ksfitted.R
clearer organiztion in ksfitted

@@ -48,13 +48,12 @@ ks.test.fitted <- function(x, dist, B = 1000, fit = TRUE, serial = FALSE,
                          param = c()) {
     ## if estimation is needed, fit marginal distribution
     ddist <- get(paste0("d", dist))
-    if (fit) param  <- MASS::fitdistr(x, ddist, start = split(param, names(param)))$estimate
+    if (fit)
+        param  <- MASS::fitdistr(x, ddist, start = split(param, names(param)))$estimate
     pdist <- fitteddist(dist, param, "p")
     rdist <- fitteddist(dist, param, "r")
-    ## get observed ks-stat
-    stat <- ks.test(x, pdist)$statistic
-    stat.b <- double(B)
-    n <- length(x)
+    qdist <- fitteddist(dist, param, "q")
+    working <- list(ar = numeric(0), ma = numeric(0))
     ## working, sigma, qdist are only used when serial == TRUE
     if (serial) {
         z <- qnorm(pdist(x))
@@ -64,6 +63,10 @@ ks.test.fitted <- function(x, dist, B = 1000, fit = TRUE, serial = FALSE,
         sigma <- sqrt(tacvfARMA.my(phi = working$ar, theta = - working$ma, maxLag = 0))     
         qdist <- fitteddist(dist, param, "q")
     }
+    ## get observed ks-stat
+    stat <- ks.test(x, pdist)$statistic
+    stat.b <- double(B)
+    n <- length(x)
     ## bootstrapping
     for (i in 1:B) {
         if (serial)

### 2023-03-23 manuscript/manuscript.tex
one example reference of misuse
edits on description of working arma

@@
 the best. When additionally the hypothesized distribution contains unknown
-parameters, the standard KS test becomes even further inapplicable.
+parameters, the standard KS test becomes even further
+inapplicable. Practitioners, however, may have used the test without knowing its
+limitations \citep[e.g.,][]{tuncer2019online}.
 
@@
 remedy is detailed and performed alongside the misuse to show its positive
-effects. In order to set up the demonstrations, simulated data are used
+effects. Specifically, unspecified parameters are handled by parametric
+bootstrap; serial dependence is handled by introducing a working autoregressive
+moving average (ARMA) model that preserves the serial dependence for a wide
+range of dependence structures.
+In order to set up the demonstrations, simulated data are used
 throughout. The remedies are also performed on various families of
@@
 issue. Section~\ref{sec:dependence} investigates the scenario where the data of
-the empirical distribution are serially dependent. A bootstrap procedure
-employing copulas to account for dependence is proposed as a working solution.
-Section~\ref{sec:fittedwithdependence}
-explores the case where a combination of the first two scenarios occurs. The
-copula procedure can be adjusted for the use of fitted parameters as a remedy.
+the empirical distribution are serially dependent. An bootstrap procedure
+employing a working ARMA model to account for dependence is proposed as a
+working solution. Section~\ref{sec:fittedwithdependence}
+explores the case where a combination of the first two scenarios occurs.
 Section~\ref{sec:conclusion} concludes with a discussion.
@@
   Obtain the empirical distribution function $F_n^*$ of
-  $X_1^*, \ldots,  X_n^*$. \eds{verify edit}
+  $X_1^*, \ldots,  X_n^*$. \eds{verify edit} \jy{Good.}
 \item
@@
 dependence structure which does not need to be correctly specified. The working
-serial dependence is introduced through copulas with the hope to approximate the
-true serial dependence as allowed by the working copulas. A copula is a
-multivariate distribution with standard uniform marginal distributions, which
-completely characterizes the dependence structure of a multivariate
-distribution \citep{hofert2018elements}. It separates the dependence structure
-of a multivariate distribution from its marginal distributions. The normal copula
-is the copula determined by the multivariate normal distribution. We propose to
-use a normal working copula to approximate the serial
-dependence of the observations.
+serial dependence is introduced through a working ARMA process with the hope to
+approximate the true serial dependence as allowed by the working
+model. Essentially, this working model covers the most commonly seen dependence
+structure characterized by a normal copula \citep{hofert2018elements}, which
+separates the dependence structure
+of a multivariate distribution from its marginal distributions. 
+The parameters of the working normal copula are
+estimated from fitting an ARMA model to the
+observed data transformed to the standard normal scale.
 
-The parameters of the working normal copula are
-estimated from fitting an auto-regressive moving average (ARMA) model to the
-observed data transformed to the standard normal scale. In particular, let
+In particular, let
 $Z_i = \Phi^{-1}\{ F(X_i)\}$, $i = 1, \ldots, n$, where $\Phi$ is the distribution
@@
 \item
-  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i^*)]$,  $i = 1, \ldots, n$.
+  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i^*)]$,  $i = 1, \ldots, n$,
+  where $F^{-1}$ is the quantile function of $F$.
 \item
@@
 selected by the AIC using function \texttt{auto.arima()} from R package
-\texttt{forecase}. This ARMA model will be used as the working model to
-introduce serial dependence in the bootstrap samples. Similarly, we obtain the
+\texttt{forecast}. This ARMA model will be used as the working model to
+introduce serial dependence in the bootstrap samples. Again, we obtain the
 unconditional variance $\sigma^2$ of the ARMA process with unit innovation
-variance. Our semiparametric bootstrap procedure is as follows
+variance. Our semiparametric bootstrap procedure is as follows.
 
@@
   Form a bootstrap sample
-  $X_i^* = F_{\hat\theta_n}^{-1} [\Phi(Z_i^*)]$, $i = 1, \ldots, n$.
+  $X_i^* = F_{\hat\theta_n}^{-1} [\Phi(Z_i^*)]$, $i = 1, \ldots, n$, where
+  $F_{\hat\theta_n}^{-1}$ is the quantile function of $F_{\hat\theta_n}$.
 \item

### 2023-03-23 Code/try.R
minor syntax fix

@@ -7,7 +7,7 @@ param <- c(shape = 2, scale = 3)
 dist <- "gamma"
 start <- c(shape = 1, scale = 1)
 
-nrep <- 2
+nrep <- 1000
 
 gm.f <- replicate(nrep, ks.test.fitted(rgamma(n, shape = 2, scale = 3), "gamma", param = start, fit = TRUE, serial = FALSE)$p.value)
 

### 2023-04-08 Code/ksfitted.R
simulation code streamlined

@@ -13,7 +13,7 @@
 ##' @return A function with a single argument while other parameters specified
 ##' through the input `param`.
 ##' 
-fitteddist <- function(dist, param, fn) {
+getfndist <- function(dist, param, fn) {
     nm <- names(param); l <- length(param)
     fun <- get(paste0(fn, dist))
     f <- formals(fun)
@@ -50,9 +50,9 @@ ks.test.fitted <- function(x, dist, B = 1000, fit = TRUE, serial = FALSE,
     ddist <- get(paste0("d", dist))
     if (fit)
         param  <- MASS::fitdistr(x, ddist, start = split(param, names(param)))$estimate
-    pdist <- fitteddist(dist, param, "p")
-    rdist <- fitteddist(dist, param, "r")
-    qdist <- fitteddist(dist, param, "q")
+    pdist <- getfndist(dist, param, "p")
+    rdist <- getfndist(dist, param, "r")
+    qdist <- getfndist(dist, param, "q")
     working <- list(ar = numeric(0), ma = numeric(0))
     ## working, sigma, qdist are only used when serial == TRUE
     if (serial) {
@@ -61,10 +61,11 @@ ks.test.fitted <- function(x, dist, B = 1000, fit = TRUE, serial = FALSE,
         ## working arma model to preserve serial dependence
         working <- list(ar = fit.arma$model$phi, ma = fit.arma$model$theta)
         sigma <- sqrt(tacvfARMA.my(phi = working$ar, theta = - working$ma, maxLag = 0))     
-        qdist <- fitteddist(dist, param, "q")
+        qdist <- getfndist(dist, param, "q")
     }
     ## get observed ks-stat
-    stat <- ks.test(x, pdist)$statistic
+    ks <- ks.test(x, pdist)
+    stat <- ks$statistic
     stat.b <- double(B)
     n <- length(x)
     ## bootstrapping
@@ -74,10 +75,10 @@ ks.test.fitted <- function(x, dist, B = 1000, fit = TRUE, serial = FALSE,
         else x.b <- rdist(n)
         if (fit) {
             fitted.b <- MASS::fitdistr(x.b, ddist, start = split(param, names(param)))
-            pdist.b <- fitteddist(dist, fitted.b$estimate, "p")
+            pdist.b <- getfndist(dist, fitted.b$estimate, "p")
             stat.b[i] <- ks.test(x.b, pdist.b)$statistic
[…]

### 2023-04-08 Code/sim.R

@@ -1,0 +1,120 @@
+## library(ggplot2)
+library(qqplotr)
+
+source("tacvfARMA.R")
+source("ksfitted.R")
+
+n <- 200
+nrep <- 10
+
+### Section 2: fitted distribution
+
+do1rep <- function(n, dist, param) {
+    rdist <- getfndist(dist, param, "r")
+    x <- rdist(n)
+    ks <- ks.test.fitted(x, dist, param = param, fit = TRUE, serial = FALSE)
+    c(ks$p.naive, ks$p.value)
+}
+
+## normal
+n.par <- c(mean = 8, sd = sqrt(8))
+n.f <- t(replicate(nrep, do1rep(n, "norm", n.par)))
+                                        # n.f <- runif(2000)
+
+## gamma
+shape <- 8; rate <- 1
+g.par <- c(shape = 8, rate = 1)
+g.f <- t(replicate(nrep, do1rep(n, "gamma", g.par)))
+# g.f <- runif(2000)
+
+f.data <- data.frame(p = c(n.f, g.f),
+                     dist = gl(2, nrep * 2, nrep * 4, c("normal", "gamma")),
+                     meth = gl(2, nrep, nrep * 4, c("naive", "bootstrap")))
+
+save(f.data, file = "f.rda")
+
+### Section 3: serial dependence (but known distribution)
+
+genData <- function(n, phi, theta, qdist) {
+    x <- arima.sim(model = list(ar = phi, ma = theta), n = n)
+    ## xbig <- arima.sim(model = list(ar = phi, ma = theta), n = 100000)
+    ## sigma <- sd(xbig)
+    sigma <- sqrt(tacvfARMA.my(phi = phi, theta = - theta, maxLag = 0))
+    qdist(pnorm(x, sd = sigma))
+}
+
+do1rep <- function(n, rho, dist, param) {
+    rdist <- getfndist(dist, param, "r")
+    qdist <- getfndist(dist, param, "q")
+    pdist <- getfndist(dist, param, "p")
+    x <- genData(n, rho, numeric(0), qdist)
+    ks.test(x, pdist)$p.value
+}
+
+n.s.3 <- replicate(nrep, do1rep(n, 0.3, "norm", n.par))
+n.s.1 <- replicate(nrep, do1rep(n, 0.1, "norm", n.par))
[…]

### 2023-04-08 Code/plot.R
initial code for plots

@@ -1,0 +1,50 @@
+library(qqplotr)
+
+load("sim.rda")
+
+## Section 2: Fitted parameters
+gg.f <- ggplot(data = f.data, mapping = aes(sample = p)) +
+    stat_pp_band(distribution = "unif") +
+    stat_pp_line() +
+    stat_pp_point(distribution = "unif", cex = .3) +
+    facet_grid(vars(dist), vars(meth)) +
+    labs(x = "Probability Points", y = "Cumulative Probability") +
+    coord_fixed() # theme(aspect.ratio=1)
+
+ggsave(filename = "pp_fit.pdf", plot = gg.f, path = "../Manuscript", height = 4, width = 4)
+
+
+## Section 3: Demonstrate the consequence of serial dependence
+gg.s <- ggplot(data = s.data, mapping = aes(sample = p)) +
+    stat_pp_band(distribution = "unif") +
+    stat_pp_line() +
+    stat_pp_point(distribution = "unif", cex = .3) +
+    facet_grid(vars(dist), vars(rho)) +
+    labs(x = "Probability Points", y = "Cumulative Probability") +
+    coord_fixed() # theme(aspect.ratio=1)
+
+ggsave(filename = "pp_s.pdf", plot = gg.s, path = "../Manuscript", height = 3, width = 6)
+
+## corrected for serial dependence
+gg.ss <- ggplot(data = subset(ss.data, meth == "bootstrap"),
+             mapping = aes(sample = p)) +
+    stat_pp_band(distribution = "unif") +
+    stat_pp_line() +
+    stat_pp_point(distribution = "unif", cex = .3) +
+    facet_grid(vars(dist), vars(dep)) +
+    labs(x = "Probability Points", y = "Cumulative Probability") +
+    coord_fixed() # theme(aspect.ratio=1)
+
+ggsave(filename = "pp_ss.pdf", plot = gg.ss, path = "../Manuscript", height = 3, width = 6)
+
+## Section 4: fitted parameter and serial dependence
+gg.ssf <- ggplot(data = subset(ss.data, meth == "bootstrap"),
+                 mapping = aes(sample = p)) +
+    stat_pp_band(distribution = "unif") +
+    stat_pp_line() +
+    stat_pp_point(distribution = "unif", cex = .3) +
+    facet_grid(vars(dist), vars(dep)) +
+    labs(x = "Probability Points", y = "Cumulative Probability") +
[…]

### 2023-04-08 manuscript/manuscript.tex
cleaned up desired plots

@@
 issue. Section~\ref{sec:dependence} investigates the scenario where the data of
-the empirical distribution are serially dependent. An bootstrap procedure
+the empirical distribution are serially dependent. A bootstrap procedure
 employing a working ARMA model to account for dependence is proposed as a
@@
 variance. This experiment was repeated 1000 times and the histogram of the
-1000 p-values are displayed in Figure~\ref{fig:hist_fitted}. If the test were
+1000 p-values are displayed in Figure~\ref{fig:pp_f}. If the test were
 valid, the p-values would be uniformly distributed in the unit
@@
 Nonparametric bootstrap can also be used to approximate the null distribution
-of the test statistic with the bias correction from \citet{babu2004goodness}:
-\begin{enumerate}
-\item
-  Draw a random sample $X_1^*,...,X_n^*$ from the empirical distribution $F_n$
-  with replacement
-\item
-  Fit $F_\theta$ to $X_1^*,...,X_n^*$ and obtain estimate 
-	$\hat\theta_n^*$ of $\theta$.
-\item
-  Obtain the empirical distribution function $F_n^*$ of
-  $X_1^*, \ldots,  X_n^*$. \eds{verify edit} \jy{Good.}
-\item
-  Calculate bootstrap KS statistic
-  \[
-    D_n^* = \sup_x | \sqrt{n}\left(F_n^* (x)- F_{\hat\theta_n^*}(x)\right) - B_n(x) |.
-  \]
-  where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
-  bias term \citep{babu2004goodness}.
-\item
-  Repeat the previous steps a large number $B$ times and use the empirical
-  distribution of $D_n^*$ to approximate the null distribution of the observed
-  statistic. 
-\end{enumerate}
-The p-value of $D_n$ is, again, approximated by the proportion of the $D_n^*$
-statistics that are greater than or equal to~$D_n$. Note that the step~1 and
-step~4 are different from the parametric bootstrap version.
+of the test statistic except that a bias correction is needed
+\citet{babu2004goodness}. Details of the nonparametric bootstrap procedure is
+in the Appendix. The results from nonparametric bootstrap are similar to those
+from the parametric bootstrap and, hence, are omitted.
 
@@
   \includegraphics[width=\textwidth]{hist_fitted}
-  \caption{Histograms of p-values for the KS test with unspecified parameters in
-    the hypothesized distribution based on 1000 replicates of sample size
-    $n = 100$. Naive (left): KS test with KS statistic calculated based on fitted
-    parameters. Parametric bootstrap (center): KS test with parametric
-    bootstrap. Nonparametric bootstrap (right): KS test with nonparametric
-    bootstrap using the bias correction from \citet{babu2004goodness}.
-    \eds{perhaps use density hist vs
-	freq. hist (here and elsewhere)?}}
-  \label{fig:hist_fitted}
+  \caption{PP-plot for the p-values obtained from KS tests with unspecified
+    parameters with sample size $n = 200$ based on 1000 replicats. The data
+    generating models were $N(8, 8)$ and $\Gamma(8, 1)$.
+  }
+  \label{fig:pp_f}
 \end{figure}
-
-\jy{Anthony, could you label the panels as ``Parametric bootstrap'' and
-  ``Nonparametric bootstrap'' for the center and right panels?}
-
-\jy{Simulation study: let's use two distributions:
-  $N(8, 8)$ and $\Gamma(8, 1)$. These two distributions have the same means and
-  variances. So we could use them to study powers of the tests too.}
 
@@
 with both the parametric and nonparametric bootstrap procedures. The center and
-right panels of Figure~\ref{fig:hist_fitted} display the histograms of the 1000
+right panels of Figure~\ref{fig:pp_f} display the histograms of the 1000
 p-values from the parametric and nonparametric bootstrap procedures,
@@
 
-\jy{For the same two marginal distributions $N(8, 8)$ and $\Gamma(8, 1)$, let's
-  generate data from dependence structures of AR(1) with two coefficients
-  $\psi \in \{ -0. 5, 0.5\}$.}
-
 The invalidity of the standard statistic for serially dependent data can be
@@
   \includegraphics[width=\textwidth]{hist_correlation}
-  \caption{Histograms of p-values for the KS test applied to data generated from
-    AR(1) processes with AR coefficients
-    $\psi \in \{-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3\}$
-    based on 1000 replicates of sample size $n = 100$.}
-  \label{fig:hist_correlation}
+  \caption{PP-plots for the p-values obtained from KS test with serial
+    dependence discarded and sample size $n = 200$ based on 1000
+    replicates. The data have marginal distributions $N(8, 8)$ and
+    $\Gamma(8, 1)$, with an AR(1) dependence structure on the standard normal
+    scale. The AR coefficients were $\psi \in \{-0.3, -0.1,  0.1,  0.3\}$.
+  }
+  \label{fig:pp_s}
 \end{figure}
@@
 
-\jy{Here we work on the same marginal distributions $N(8, 8)$ and $\Gamma(8, 1)$
-  with different dependence structures:
-  ARMA(1, 1); MA(2); AR(2)
-  }
-Continuing with the simulation study, 
-Throughout the simulation we assume a working AR(1) dependence structure
-regardless of the true dependence. This is demonstrated with different dependence
-structures in Figure~\ref{fig:hist_ma1_arma_ar2_D}.
+\jy{describe the simulation setting here.}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{hist_ar1_D}
-  \caption{The Naive plot (left) is the histogram of p-values from the
-  standard KS test. The Copula plot (right) is the histogram of p-values from
-  implementing the parametric \eds{semiparametric?} bootstrap with copulas for
-	dependence. In each case,
-  $1000$ replicate tests were performed with the data generated from an AR(1)
-  process of the standard normal distribution with $\psi = .5$. The sample size
-  is $n = 100$ and $B = 1000$ bootstrap samples are obtained for each test.}
-  \label{fig:hist_ar1_D}
+  \includegraphics[width=\textwidth]{hist_correlation}
+  \caption{PP-plots for the p-values obtained from KS test with serial
+    dependence accounted for through a working ARMA model and $n = 200$ based on
+    1000 replicates. The data have marginal distributions $N(8, 8)$ and
+    $\Gamma(8, 1)$. The dependence structure on the standard normal scale was
+    characterized by ARMA(1, 1) model, AR(2) model, and MA(1) model.
+  }
+  \label{fig:pp_ss}
 \end{figure}
-
-Figure~\ref{fig:hist_ar1_D} displays the results of the copula remedy for
-dependent data. The data is generated from the standard normal distribution with
-an AR(1) dependence structure where $\psi = .5$. The copula used is to model
-dependence is the normal copula. The distribution of p-values is again expected
-to be $U(0, 1)$ for a valid test. The Naive plot is clearly not uniform and
-reinforces the results shown in Figure~\ref{fig:hist_correlation}. The Copula
-plot, which implements the aforementioned procedure to correct for dependence
-in the data, appears to be uniform and restores the size of the KS test.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{hist_ma1_arma_ar2_D}
-  \caption{The Naive plots are the histograms of p-values from the standard KS
-  test. The Copula plots are the histograms of p-values from parametric
-  bootstrap with copulas for dependence. The data is generated from an MA(1)
-  process (left) with $\theta = .5$, ARMA(1, 1) process (middle) with $\psi =
-  .5$ and $\theta = .3$, and AR(2) process (right) with $\psi = (.5, .3)$ of the
-  standard normal distribution. In each case, $1000$ replicate tests were
-  performed with sample size $n = 100$ and $B = 1000$ bootstrap samples.}
-  \label{fig:hist_ma1_arma_ar2_D}
-\end{figure}
-
-\jy{to be rewritten when the figures are generated.}
-\jy{I suggest that we keep using gamma as the marginal distribution
-  throughout. Elizabeth, let's finalize the settings next time we meet. I've
-  implemented a concise version of the test.}
-
-The procedure detailed in this section can also provide a reasonable
-approximation in cases where the true dependence structure is not far from
-AR(1). Figure~\ref{fig:hist_ma1_arma_ar2_D} shows the distribution of p-values
-for dependence structures MA(1), ARMA(1, 1), and AR(2). As expected,
-naively performing the KS test without correcting for dependence provides plots
-of p-values that deviate from the uniform distribution. In the case of MA(1)
-and ARMA(1, 1), the true dependence structure is close enough to our
-assumption of AR(1) that the bootstrap procedure provides a reasonable
-approximation. However, the AR(2) copula plot shows the limitation of this
-technique as no AR(1) process can approximate an AR(2) process unless the
-second-order coefficient is close to zero.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{hist_gamma_gev_D}
-  \caption{The Naive plots are the histograms of p-values from the standard KS
-  test. The Copula plots are the histograms of p-values from parametric
-  bootstrap with copulas for dependence. The data is generated from $Gamma(3,
-  1)$ (left) and $GEV(0, .2, 1)$ (right) with a correlation coefficient of $r =
-  0.5$. In each case, $1000$ replicate tests were performed with sample size $n
-  = 100$ and $B = 1000$ bootstrap samples.}
-  \label{fig:hist_gamma_gev_D}
-\end{figure}
-
-To further demonstrate the effectiveness of the procedure, we perform similar
-simulations on other families of distributions.
-Figure~\ref{fig:hist_gamma_gev_D} displays the results of tests using dependent
-data generated from the gamma and the generalized extreme value distributions.
-The procedure corrects the distribution of p-values for both distributions and
-is shown to be applicable regardless of the family of distribution tested.
 
@@
 
-\jy{For the simulation study, repeat the study at the end of the last section.}
-
 \begin{figure}[tbp]
   \centering
-  \includegraphics[width=\textwidth]{hist_ar1_FD}
-  \caption{The Super Naive plot (left) is the histogram of p-values from the
-  standard KS test with fitted parameters. The Naive Parametric plot (middle) is
-  the histogram of p-values from implementing parametric bootstrap. The Copula
-  plot is the histogram of p-values from implementing parametric bootstrap with
-  copulas for dependence and correcting for fitted parameters. In each case,
-  $1000$ replicate tests were performed with the data generated from an AR(1)
-  process of the standard normal distribution with $\psi = .5$. The sample size
-  is $n = 100$ and $B = 1000$ bootstrap samples are obtained for each test.}
-  \label{fig:hist_ar1_FD}
-\end{figure}
-
-Figure~\ref{fig:hist_ar1_FD} shows the results of our simulation on data
-simulated from an AR(1) process. As should be expected, naively fitting
-parameters while providing no adjustment for dependent data invalidates the KS
-test. As well, only using the parametric bootstrap remedy for fitted parameters
-from Section~\ref{sec:fitted} seems to provide weaker results than the
-copula remedy presented above. The results show that copula remedy generates
-uniform p-values and restores the size of the KS test.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{hist_ma1_arma_ar2_FD}
-  \caption{The Super Naive plots (left) are the histograms of p-values from the
-  standard KS test with fitted parameters. The Naive Parametric plots (middle)
-  are the histograms of p-values from implementing parametric bootstrap. The
-  Copula plots (bottom) are the histograms of p-values from implementing
-  parametric bootstrap with copulas for dependence and correcting for fitted
-  parameters. The data is generated from an MA(1) process (left) with
-  $\theta = .5$, ARMA(1, 1) process (middle) with $\psi = .5$ and $\theta = .3$,
-  and AR(2) process (right) with $\psi = (.5, .3)$ of the standard normal
-  distribution. In each case, $1000$ replicate tests were performed with sample
-  size $n = 100$ and $B = 1000$ bootstrap samples.}
-  \label{fig:hist_ma1_arma_ar2_FD}
+  \includegraphics[width=\textwidth]{hist_correlation}
+  \caption{PP-plots for the p-values obtained from KS test with unspecified
+    parameters and serial
+    dependence accounted for through a working ARMA model and $n = 200$ based on
+    1000 replicates. The data have marginal distributions $N(8, 8)$ and
+    $\Gamma(8, 1)$. The dependence structure on the standard normal scale was
+    characterized by ARMA(1, 1) model, AR(2) model, and MA(1) model.
+  }
+  \label{fig:pp_ss}
 \end{figure}
@@
 procedure.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{hist_gamma_gev_FD}
-  \caption{The Super Naive plots (left) are the histograms of p-values from the
-  standard KS test with fitted parameters. The Naive Parametric plots (middle)
-  are the histograms of p-values from implementing parametric bootstrap. The
-  Copula plots are the histograms of p-values from implementing parametric
-  bootstrap with copulas for dependence and correcting for fitted parameters.
-  The data is generated from $Gamma(3, 1)$ (left) and $GEV(0, .2, 1)$ (right)
-  with a correlation coefficient of $r = 0.5$. In each case, $1000$ replicate
-  tests were performed with sample size $n = 100$ and $B = 1000$ bootstrap
-  samples.}
-  \label{fig:hist_gamma_gev_FD}
-\end{figure}
-
-It is also possible to apply our procedure to other families of distributions.
-The data in Figure~\ref{fig:hist_gamma_gev_FD} is generated from the gamma and
-generalized extreme value distributions. The results are favorable and show that
-the procedure outlined as a remedy for fitted parameters and spatially dependent
-can be adapted for various families of distributions.
 
@@
 
+\appendix
+
+\section{Nonparametric Bootstrap for KS Test with Fitted Parameters}
+
+Using the same notations in the text, the procedure is summarized as follows
+\citep{babu2004goodness}.
+\begin{enumerate}
+\item
+  Draw a random sample $X_1^*,...,X_n^*$ from the empirical distribution $F_n$
+  with replacement
+\item
+  Fit $F_\theta$ to $X_1^*,...,X_n^*$ and obtain estimate 
+	$\hat\theta_n^*$ of $\theta$.
+\item
+  Obtain the empirical distribution function $F_n^*$ of
+  $X_1^*, \ldots,  X_n^*$. 
+\item
+  Calculate bootstrap KS statistic
+  \[
+    D_n^* = \sup_x | \sqrt{n}\left(F_n^* (x)- F_{\hat\theta_n^*}(x)\right) - B_n(x) |.
+  \]
+  where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
+  bias term \citep{babu2004goodness}.
+\item
+  Repeat the previous steps a large number $B$ times and use the empirical
+  distribution of $D_n^*$ to approximate the null distribution of the observed
+  statistic. 
+\end{enumerate}
+The p-value of $D_n$ is, again, approximated by the proportion of the $D_n^*$
+statistics that are greater than or equal to~$D_n$. Note that the step~1 and
+step~4 are different from the parametric bootstrap version.
+
 \bibliographystyle{asa}

### 2023-04-10 Code/plot.R
tuned ar2 and ma parameters for higher acf

@@ -38,7 +38,9 @@ gg.ss <- ggplot(data = subset(ss.data, meth == "bootstrap"),
 ggsave(filename = "pp_ss.pdf", plot = gg.ss, path = "../Manuscript", height = 3, width = 6)
 
 ## Section 4: fitted parameter and serial dependence
-gg.ssf <- ggplot(data = subset(ss.data, meth == "bootstrap"),
+
+ssf.data$meth <- gl(3, nrep, nrep * 18, c("naive0", "naive", "bootstrap"))
+gg.ssf <- ggplot(data = subset(ssf.data, meth == "bootstrap"),
                  mapping = aes(sample = p)) +
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
@@ -48,3 +50,23 @@ gg.ssf <- ggplot(data = subset(ss.data, meth == "bootstrap"),
     coord_fixed() # theme(aspect.ratio=1)
 
 ggsave(filename = "pp_ssf.pdf", plot = gg.ssf, path = "../Manuscript", height = 3, width = 6)
+
+gg.s_f <- ggplot(data = subset(ssf.data, meth == "naive"),
+                 mapping = aes(sample = p)) +
+    stat_pp_band(distribution = "unif") +
+    stat_pp_line() +
+    stat_pp_point(distribution = "unif", cex = .3) +
+    facet_grid(vars(dist), vars(dep)) +
+    labs(x = "Probability Points", y = "Cumulative Probability") +
+    coord_fixed() # theme(aspect.ratio=1)
+
+gg.s__ <- ggplot(data = subset(ssf.data, meth == "naive0"),
+                 mapping = aes(sample = p)) +
+    stat_pp_band(distribution = "unif") +
+    stat_pp_line() +
+    stat_pp_point(distribution = "unif", cex = .3) +
+    facet_grid(vars(dist), vars(dep)) +
+    labs(x = "Probability Points", y = "Cumulative Probability") +
+    coord_fixed() # theme(aspect.ratio=1)
+
+ggsave(filename = "pp_s_.pdf", plot = gg.s__, path = "../Manuscript", height = 3, width = 6)

### 2023-04-10 Code/sim.R

@@ -80,12 +80,12 @@ do1rep <- function(n, phi, theta, dist, param) {
 }
 
 n.arma <- t(replicate(nrep, do1rep(n, .5, .3, "norm", n.par)))
-n.ar   <- t(replicate(nrep, do1rep(n, c(-.5, .3), numeric(0), "norm", n.par)))
-n.ma   <- t(replicate(nrep, do1rep(n, numeric(0), .5, "norm", n.par)))
+n.ar   <- t(replicate(nrep, do1rep(n, c(.6, .2), numeric(0), "norm", n.par)))
+n.ma   <- t(replicate(nrep, do1rep(n, numeric(0), .8, "norm", n.par)))
 
 g.arma <- t(replicate(nrep, do1rep(n, .5, .3, "gamma", g.par)))
-g.ar   <- t(replicate(nrep, do1rep(n, c(-.5, .3), numeric(0), "gamma", g.par)))
-g.ma   <- t(replicate(nrep, do1rep(n, numeric(0), .5, "gamma", g.par)))
+g.ar   <- t(replicate(nrep, do1rep(n, c(.6, .2), numeric(0), "gamma", g.par)))
+g.ma   <- t(replicate(nrep, do1rep(n, numeric(0), .8, "gamma", g.par)))
 
 ss.data <- data.frame(p = c(n.arma, n.ar, n.ma, g.arma, g.ar, g.ma),
                       dist = gl(2, nrep * 6, nrep * 12, c("normal", "gamma")),
@@ -99,22 +99,22 @@ do1rep <- function(n, phi, theta, dist, param) {
     rdist <- getfndist(dist, param, "r")
     qdist <- getfndist(dist, param, "q")
     x <- genData(n, phi, theta, qdist)
-    ks.f <- ks.test.fitted(x, dist, fit = TRUE, serial = TRUE, param = param)
-    ks.fs <- ks.test.fitted(x, dist, fit = TRUE, serial = FALSE, param = param)
+    ks.f <- ks.test.fitted(x, dist, fit = TRUE, serial = FALSE, param = param)
+    ks.fs <- ks.test.fitted(x, dist, fit = TRUE, serial = TRUE, param = param)
     c(ks.f$p.naive, ks.f$p.value, ks.fs$p.value)
 }
 
 n.arma <- t(replicate(nrep, do1rep(n, .5, .3, "norm", n.par)))
[…]

### 2023-04-10 Code/sim.R
nrep = 1000

@@ -5,7 +5,7 @@ source("tacvfARMA.R")
 source("ksfitted.R")
 
 n <- 200
-nrep <- 10
+nrep <- 1000
 
 ### Section 2: fitted distribution
 

### 2023-04-11 manuscript/manuscript.tex
added pp-plots to manuscript

@@
   \centering
-  \includegraphics[width=\textwidth]{hist_fitted}
+  \includegraphics[width=.5\textwidth]{pp_f.pdf}
   \caption{PP-plot for the p-values obtained from KS tests with unspecified
@@
 marginally. The histograms of the p-values from $1000$ replicates for all the
-$\psi$ values are displayed in Figure~\ref{fig:hist_correlation}. When
+$\psi$ values are displayed in Figure~\ref{fig:pp_s}. When
 $\phi \ne 0$, the histograms do not look likely to be generated from a standard
@@
   \centering
-  \includegraphics[width=\textwidth]{hist_correlation}
+  \includegraphics[width=\textwidth]{pp_s.pdf}
   \caption{PP-plots for the p-values obtained from KS test with serial
@@
   \centering
-  \includegraphics[width=\textwidth]{hist_correlation}
+  \includegraphics[width=.75\textwidth]{pp_ss.pdf}
   \caption{PP-plots for the p-values obtained from KS test with serial
@@
   \centering
-  \includegraphics[width=\textwidth]{hist_correlation}
-  \caption{PP-plots for the p-values obtained from KS test with unspecified
-    parameters and serial
-    dependence accounted for through a working ARMA model and $n = 200$ based on
+  \includegraphics[width=.75\textwidth]{pp_s_f.pdf}
+  \includegraphics[width=.75\textwidth]{pp_ssf.pdf}
+  \caption{PP-plots for the p-values obtained from KS test without and with
+    serial dependence accounted for and unspecified parameters and sample size
+    $n = 200$ based on
     1000 replicates. The data have marginal distributions $N(8, 8)$ and
@@
   }
-  \label{fig:pp_ss}
+  \label{fig:pp_ssf}
 \end{figure}
@@
 correction still provides a reasonable approximation that can be useful for
-practical purposes. Figure~\ref{fig:hist_ma1_arma_ar2_FD} shows the results of the
+practical purposes. Figure~\ref{fig:ssd} shows the results of the
 procedure performed on data generated with dependence structures of  MA(1),

### 2023-04-11 Code/plot.R

@@ -4,6 +4,7 @@ load("sim.rda")
 
 ## Section 2: Fitted parameters
 gg.f <- ggplot(data = f.data, mapping = aes(sample = p)) +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0)) + 
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
     stat_pp_point(distribution = "unif", cex = .3) +
@@ -16,6 +17,7 @@ ggsave(filename = "pp_fit.pdf", plot = gg.f, path = "../Manuscript", height = 4,
 
 ## Section 3: Demonstrate the consequence of serial dependence
 gg.s <- ggplot(data = s.data, mapping = aes(sample = p)) +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
     stat_pp_point(distribution = "unif", cex = .3) +
@@ -23,11 +25,12 @@ gg.s <- ggplot(data = s.data, mapping = aes(sample = p)) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed() # theme(aspect.ratio=1)
 
-ggsave(filename = "pp_s.pdf", plot = gg.s, path = "../Manuscript", height = 3, width = 6)
+ggsave(filename = "pp_s.pdf", plot = gg.s, path = "../Manuscript", height = 3.5, width = 6)
 
 ## corrected for serial dependence
 gg.ss <- ggplot(data = subset(ss.data, meth == "bootstrap"),
              mapping = aes(sample = p)) +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
     stat_pp_point(distribution = "unif", cex = .3) +
@@ -35,13 +38,13 @@ gg.ss <- ggplot(data = subset(ss.data, meth == "bootstrap"),
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed() # theme(aspect.ratio=1)
 
-ggsave(filename = "pp_ss.pdf", plot = gg.ss, path = "../Manuscript", height = 3, width = 6)
+ggsave(filename = "pp_ss.pdf", plot = gg.ss, path = "../Manuscript", height = 3, width = 4.5)
 
 ## Section 4: fitted parameter and serial dependence
 
[…]

### 2023-04-11 Code/plot.R
sparser ticks in pp-plots

@@ -4,7 +4,8 @@ load("sim.rda")
 
 ## Section 2: Fitted parameters
 gg.f <- ggplot(data = f.data, mapping = aes(sample = p)) +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0)) + 
+    scale_x_continuous(breaks=c(0, 1)) +
+    scale_y_continuous(breaks=c(0, 1)) + 
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
     stat_pp_point(distribution = "unif", cex = .3) +
@@ -12,12 +13,13 @@ gg.f <- ggplot(data = f.data, mapping = aes(sample = p)) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed() # theme(aspect.ratio=1)
 
-ggsave(filename = "pp_fit.pdf", plot = gg.f, path = "../Manuscript", height = 4, width = 4)
+ggsave(filename = "pp_f.pdf", plot = gg.f, path = "../Manuscript", height = 4, width = 4)
 
 
 ## Section 3: Demonstrate the consequence of serial dependence
 gg.s <- ggplot(data = s.data, mapping = aes(sample = p)) +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
+    scale_x_continuous(breaks=c(0, 1)) +
+    scale_y_continuous(breaks=c(0, 1)) + 
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
     stat_pp_point(distribution = "unif", cex = .3) +
@@ -30,7 +32,8 @@ ggsave(filename = "pp_s.pdf", plot = gg.s, path = "../Manuscript", height = 3.5,
 ## corrected for serial dependence
 gg.ss <- ggplot(data = subset(ss.data, meth == "bootstrap"),
              mapping = aes(sample = p)) +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
+    scale_x_continuous(breaks=c(0, 1)) +
+    scale_y_continuous(breaks=c(0, 1)) + 
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
     stat_pp_point(distribution = "unif", cex = .3) +
@@ -44,7 +47,8 @@ ggsave(filename = "pp_ss.pdf", plot = gg.ss, path = "../Manuscript", height = 3,
 
[…]

### 2023-04-12 Code/sim.R
removed redundant lines

@@ -37,8 +37,6 @@ save(f.data, file = "f.rda")
 
 genData <- function(n, phi, theta, qdist) {
     x <- arima.sim(model = list(ar = phi, ma = theta), n = n)
-    ## xbig <- arima.sim(model = list(ar = phi, ma = theta), n = 100000)
-    ## sigma <- sd(xbig)
     sigma <- sqrt(tacvfARMA.my(phi = phi, theta = - theta, maxLag = 0))
     qdist(pnorm(x, sd = sigma))
 }
@@ -72,7 +70,6 @@ s.data <- data.frame(p = c(n.s.n3, n.s.n1, n.s.1, n.s.3,
 ### Section 3: after fixing the serial dependence with auto.arima
 
 do1rep <- function(n, phi, theta, dist, param) {
-    rdist <- getfndist(dist, param, "r")
     qdist <- getfndist(dist, param, "q")
     x <- genData(n, phi, theta, qdist)
     ks <- ks.test.fitted(x, dist, fit = FALSE, serial = TRUE, param = param)
@@ -96,7 +93,6 @@ ss.data <- data.frame(p = c(n.arma, n.ar, n.ma, g.arma, g.ar, g.ma),
 
 
 do1rep <- function(n, phi, theta, dist, param) {
-    rdist <- getfndist(dist, param, "r")
     qdist <- getfndist(dist, param, "q")
     x <- genData(n, phi, theta, qdist)
     ks.f <- ks.test.fitted(x, dist, fit = TRUE, serial = FALSE, param = param)

### 2023-04-12 Code/power.R
added power study code

@@ -1,0 +1,49 @@
+source("tacvfARMA.R")
+source("ksfitted.R")
+library("truncdist")
+
+n <- 100
+nrep <- 1000
+
+n.par <- c(mean = 8, sd = sqrt(8))
+g.par <- c(shape = 8, rate = 1)
+
+genData <- function(n, phi, theta, qdist) {
+    x <- arima.sim(model = list(ar = phi, ma = theta), n = n)
+    sigma <- sqrt(tacvfARMA.my(phi = phi, theta = - theta, maxLag = 0))
+    qdist(pnorm(x, sd = sigma))
+}
+
+do1rep <- function(n, phi, theta, qdist, hypod, start) {
+    x <- genData(n, phi, theta, qdist)
+    ks.f <- ks.test.fitted(x, hypod, fit = TRUE, serial = FALSE, param = start)
+    ks.fs <- ks.test.fitted(x, hypod, fit = TRUE, serial = TRUE, param = start)
+    c(ks.f$p.value, ks.fs$p.value)
+}
+
+## true distribution is truncated normal(8, 8)
+qdist <- function(p) qtrunc(p, "norm", a = 0, mean = 8, sd = sqrt(8))
+
+hg.n3 <- t(replicate(nrep, do1rep(n, -0.3, numeric(0), qdist, "gamma", g.par)))
+hg.0 <- t(replicate(nrep, do1rep(n, numeric(0), numeric(0), qdist, "gamma", g.par)))
+hg.3 <- t(replicate(nrep, do1rep(n, 0.3, numeric(0), qdist, "gamma", g.par)))
+                    
+        
+hg.data <- data.frame(p = c(hg.n3, hg.0, hg.3),
+                      meth = gl(2, nrep, nrep * 6, c("not serial", "serial")),
+                      dep = gl(3, nrep * 2, nrep * 6, c(-0.3, 0, 0.3)))
+
+
+## true distribution is gamma(8, 1)
+qdist <- function(p) qgamma(p, shape = 8, rate = 1)
+
+hn.n3 <- t(replicate(nrep, do1rep(n, -0.3, numeric(0), qdist, "norm", n.par)))
+hn.0 <- t(replicate(nrep, do1rep(n, numeric(0), numeric(0), qdist, "norm", n.par)))
+hn.3 <- t(replicate(nrep, do1rep(n, 0.3, numeric(0), qdist, "norm", n.par)))
+                    
+        
[…]

### 2023-04-16 Code/power.R
added try-error control to power study

@@ -16,9 +16,10 @@ genData <- function(n, phi, theta, qdist) {
 
 do1rep <- function(n, phi, theta, qdist, hypod, start) {
     x <- genData(n, phi, theta, qdist)
-    ks.f <- ks.test.fitted(x, hypod, fit = TRUE, serial = FALSE, param = start)
-    ks.fs <- ks.test.fitted(x, hypod, fit = TRUE, serial = TRUE, param = start)
-    c(ks.f$p.value, ks.fs$p.value)
+    ks.f <- try(ks.test.fitted(x, hypod, fit = TRUE, serial = FALSE, param = start))
+    ks.fs <- try(ks.test.fitted(x, hypod, fit = TRUE, serial = TRUE, param = start))
+    c(ifelse(inherits(ks.f, "try-error"), NA, ks.f$p.value),
+      ifelse(inherits(ks.fs, "try-error"), NA, ks.fs$p.value))
 }
 
 ## true distribution is truncated normal(8, 8)

### 2023-04-18 manuscript/manuscript.tex
added a power study

@@
 
+\begin{table}[ht]
+  \label{tab:power}
+  \caption{Power of rejecting the null hypothesis of normal and gamma
+    distribution at significance level 0.05 when the true distribution was
+    $\Gamma(8, 1)$ and $N(8, 8)$, respectively. }
+\centering
+\begin{tabular}{llrrrr}
+  \toprule
+  &  & \multicolumn{2}{c}{$H_0:$ normal} &
+  \multicolumn{2}{c}{$H_0$: gamma}\\
+  \cmidrule(lr){3-4}\cmidrule(lr){5-6}
+  Dependence & Method & $n = 100$ & $n = 200$ & $n = 100$ & $n = 200$\\
+  \midrule
+ARMA & naive & 0.40 & 0.66 & 0.52 & 0.78 \\ 
+   & copula & 0.33 & 0.56 & 0.44 & 0.72 \\ 
+  AR & naive & 0.41 & 0.66 & 0.46 & 0.70 \\ 
+   & copula & 0.26 & 0.45 & 0.31 & 0.54 \\ 
+  MA & naive & 0.37 & 0.73 & 0.51 & 0.82 \\ 
+   & copula & 0.34 & 0.69 & 0.49 & 0.80 \\ 
+   \bottomrule
+\end{tabular}
+\end{table}
+
+Finally, we report a small study of the power of the one-sample KS test with
+unspecified parameters and serially dependent data. Using the three dependence
+models characterized by ARMA(1, 1), AR(2), and MA(1), we generated serially
+dependent data with marginal distributions $N(8, 8)$ left truncated by zero and
+$\Gamma(8, 1)$. Then, for data from $\Gamma(8, 1)$, we tested $H_0$ that the
+data has marginally a normal distribution; for data from $N(8, 8)$ left
+truncated by zero, we tested $H_0$ that the data has marginally a gamma
+distribution;  In both cases, no parameters were specified. Two sample sizes
+were considered, $n \in \{100, 200\}$. Table~\ref{tab:power} summarizes the
+power of rejecting the null hypothesis at significance level~0.05. The tests
+based on a working copula have substantial power in rejecting the null
+hypothesis and the power increases as sample size increases. The power from the
+naive tests where the serial dependence is discarded, although the unspecified
+parameters are accounted for, appear to have higher power than the proposed
+tests, but this is not reliable since they do not hold their sizes as
+demonstrated in the Figures.
+
 \section{Conclusion}

### 2023-04-18 Code/power.R

@@ -32,7 +32,7 @@ hg.ma <- t(replicate(nrep, do1rep(n, numeric(0), 0.8, qdist, "gamma", g.par)))
         
 hg.data <- data.frame(p = c(hg.arma, hg.ar, hg.ma),
                       meth = gl(2, nrep, nrep * 6, c("not serial", "serial")),
-                      dep = gl(3, nrep * 2, nrep * 6, c(-0.3, 0, 0.3)))
+                      dep = gl(3, nrep * 2, nrep * 6, c("ARMA", "AR", "MA")))
 
 
 ## true distribution is gamma(8, 1)

### 2023-04-20 manuscript/manuscript.tex
mid-way through Sec 3

@@
 be testing a different~$H_0$ that the random sample comes from the specific
-member distribution~$F_{\hat\theta}$ instead of the family~$F_\theta$.
+member distribution~$F_{\hat\theta_n}$ instead of the family~$F_\theta$.
 
@@
 in~\eqref{eq:ks_fitted} can be illustrated through a simple simulation study. A
-random sample $X_1, \ldots, X_n$ was generated from the standard normal
-distribution with sample size $n = 100$. The sample mean and sample standard
+random sample $X_1, \ldots, X_n$ was generated from a normal
+distribution with both mean and variance parameters set equal to 8 ($N(8,8)$), 
+and sample size $n = 200$. The sample mean and sample standard
 deviation were used as $\hat\theta_n$. The p-value of the test
@@
 $N(\bar X, s^2)$ where $\bar X$ is the sample mean and $s^2$ is the sample
-variance. This experiment was repeated 1000 times and the histogram of the
-1000 p-values are displayed in Figure~\ref{fig:pp_f}. If the test were
+variance. This experiment was repeated 1000 times and the 
+probability-probability plot (PP-plot) of the 1000 p-values are displayed in the 
+top left plot of Figure~\ref{fig:pp_f}. If the test were
 valid, the p-values would be uniformly distributed in the unit
-interval. Clearly, the pattern of the 1000 p-values are very different from what
+interval and the points in the PP plot would fall along the diagonal line. 
+Clearly, the distribution of the 1000 p-values are very different from what
 one would expect to see from 1000 draws from the standard uniform
 distribution.
+
+We similarly considered random samples $X_1, \ldots, X_n$ 
+generated from a gamma distribution with shape and scale parameters 8 and 1, 
+respectively ($\Gamma(8,1)$), and sample size $n=200$. These parameter values 
+were selected so that mean and variance of the normal and gamma distributions 
+in the simulations are the same. Likewise, the p-value of the test 
+statistic~$D_n$ in~\eqref{eq:ks_fitted} was obtained by naively calling the
+\texttt{ks.test()} function in~R with the fitted gamma distribution as the
+hypothesized distribution using the shape and scale \eds{maximum likelihood 
+estimates}. The PP plot of the p-values from 1000 replications of this 
+experiment are displayed in the bottom left plot of Figure~\ref{fig:pp_f}. The
+p-values are again non-uniformly distributed due to the use of the 
+estimated parameters when specifying the null distribution.
 
@@
 
+In the same simulation study, p-values were obtained for the 1000 replicates
+from the parametric bootstrap procedures. The top and bottom right plots of 
+Figure~\ref{fig:pp_f} display the PP-plots of the 1000
+p-values from the normal and gamma data generation scenarios,
+respectively. This time, all points fall along the diagonal lines implying that
+the p-values are coming from standard uniform distributions.
+
 Nonparametric bootstrap can also be used to approximate the null distribution
-of the test statistic except that a bias correction is needed
-\citet{babu2004goodness}. Details of the nonparametric bootstrap procedure is
+of the test statistic in~\eqref{eq:ks_fitted} except that a bias correction is 
+needed
+\citep{babu2004goodness}. Details of the nonparametric bootstrap procedure are
 in the Appendix. The results from nonparametric bootstrap are similar to those
@@
   \includegraphics[width=.5\textwidth]{pp_f.pdf}
-  \caption{PP-plot for the p-values obtained from KS tests with unspecified
-    parameters with sample size $n = 200$ based on 1000 replicats. The data
+  \caption{PP-plots for the p-values obtained from KS tests with unspecified
+    parameters with sample size $n = 200$ based on 1000 replicates. The data
     generating models were $N(8, 8)$ and $\Gamma(8, 1)$.
@@
 \end{figure}
-
-In the same simulation study, p-values were obtained for the 1000 replicates
-with both the parametric and nonparametric bootstrap procedures. The center and
-right panels of Figure~\ref{fig:pp_f} display the histograms of the 1000
-p-values from the parametric and nonparametric bootstrap procedures,
-respectively. This time, both samples of p-values appear to come from
-standard uniform distributions.
 
@@
 illustrated by a simple simulation study. Consider a first-order autoregressive
-or AR(1) model with marginal standard normal distribution. For each AR
-coefficient $\psi \in \{-0.3, 0.2, 0.1, 0, 0.1, 0.2, 0.3\}$, we generated 1000
+or AR(1) model with marginal normal (or gamma) distribution. For each AR
+coefficient $\psi \in \{-0.3, 0.1, 0.1, 0.3\}$, we generated 1000
 series of length 100. For each series, we applied the KS statistic
-in~\eqref{eq:ks_standard} to test $H_0$ that the $X_i$'s follow $N(0, 1)$
-marginally. The histograms of the p-values from $1000$ replicates for all the
-$\psi$ values are displayed in Figure~\ref{fig:pp_s}. When
-$\phi \ne 0$, the histograms do not look likely to be generated from a standard
-uniform distribution. Positive $\psi$ values led to p-values with a distribution
-function higher than the standard uniform distribution function and, hence,
-conservative tests. Negative $\psi$ values led to p-values with a distribution
-function lower than the standard uniform distribution and, hence, liberal
-tests. The larger the magnitude of
+in~\eqref{eq:ks_standard} to test $H_0$ that the $X_i$'s follow $N(8, 8)$ (or 
+$\Gamma(8,1)$ marginally. The PP-plots of the p-values from $1000$ replicates 
+for all the $\psi$ values are displayed in Figure~\ref{fig:pp_s}. When
+$\phi$ diverges from 0, the p-values do not look likely to be generated from a 
+standard uniform distributions. Positive $\psi$ values led to p-values with a 
+distribution function higher than the standard uniform distribution function and, 
+hence, conservative tests. Negative $\psi$ values led to p-values with a 
+distributionfunction lower than the standard uniform distribution and, hence, 
+liberal tests. \eds{check previous statement, not consistent with beginning of 
+this section} The larger the magnitude of
 $\psi$, the bigger the deviation from the desired level.
+\eds{check that $\psi=.1$ plots are really from .1 and not 0}
 

### 2023-04-20 Code/plot.R
even smaller cex (0.1) for plots

@@ -8,7 +8,7 @@ gg.f <- ggplot(data = f.data, mapping = aes(sample = p)) +
     scale_y_continuous(breaks=c(0, 1)) + 
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
-    stat_pp_point(distribution = "unif", cex = .3) +
+    stat_pp_point(distribution = "unif", cex = .1) +
     facet_grid(vars(dist), vars(meth)) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed() # theme(aspect.ratio=1)
@@ -22,7 +22,7 @@ gg.s <- ggplot(data = s.data, mapping = aes(sample = p)) +
     scale_y_continuous(breaks=c(0, 1)) + 
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
-    stat_pp_point(distribution = "unif", cex = .3) +
+    stat_pp_point(distribution = "unif", cex = .1) +
     facet_grid(vars(dist), vars(rho)) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed() # theme(aspect.ratio=1)
@@ -36,7 +36,7 @@ gg.ss <- ggplot(data = subset(ss.data, meth == "bootstrap"),
     scale_y_continuous(breaks=c(0, 1)) + 
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
-    stat_pp_point(distribution = "unif", cex = .3) +
+    stat_pp_point(distribution = "unif", cex = .1) +
     facet_grid(vars(dist), vars(dep)) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed() # theme(aspect.ratio=1)
@@ -51,7 +51,7 @@ gg.ssf <- ggplot(data = subset(ssf.data, meth == "bootstrap"),
     scale_y_continuous(breaks=c(0, 1)) + 
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
-    stat_pp_point(distribution = "unif", cex = .3) +
+    stat_pp_point(distribution = "unif", cex = .1) +
     facet_grid(vars(dist), vars(dep)) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed() # theme(aspect.ratio=1)
@@ -64,7 +64,7 @@ gg.s_f <- ggplot(data = subset(ssf.data, meth == "naive"),
[…]

### 2023-04-20 manuscript/manuscript.tex
Finished my pass. Few comments remain

@@
 distribution with both mean and variance parameters set equal to 8 ($N(8,8)$), 
-and sample size $n = 200$. The sample mean and sample standard
-deviation were used as $\hat\theta_n$. The p-value of the test
-statistic~$D_n$ in~\eqref{eq:ks_fitted} was obtained by naively calling the
-\texttt{ks.test()} function in~R with the fitted normal distribution as the
+and sample size $n = 200$. The maximum likelihood estimates of the mean and 
+variance were used as $\hat\theta_n$. The p-value of the test
+statistic~$D_n$ in Equation~\eqref{eq:ks_fitted} was obtained by naively calling 
+the \texttt{ks.test()} function in~R with the fitted normal distribution as the
 hypothesized distribution. That is, the hypothesized distribution was
 $N(\bar X, s^2)$ where $\bar X$ is the sample mean and $s^2$ is the sample
-variance. This experiment was repeated 1000 times and the 
-probability-probability plot (PP-plot) of the 1000 p-values are displayed in the 
-top left plot of Figure~\ref{fig:pp_f}. If the test were
+variance (with $n$ in the denominator). This experiment was repeated 1000 times
+and the probability-probability plot (PP-plot) of the 1000 p-values are 
+displayed in the top left plot of Figure~\ref{fig:pp_f}. If the test were
 valid, the p-values would be uniformly distributed in the unit
@@
 \texttt{ks.test()} function in~R with the fitted gamma distribution as the
-hypothesized distribution using the shape and scale \eds{maximum likelihood 
-estimates}. The PP plot of the p-values from 1000 replications of this 
+hypothesized distribution using the shape and scale maximum likelihood 
+estimates. The PP plot of the p-values from 1000 replications of this 
 experiment are displayed in the bottom left plot of Figure~\ref{fig:pp_f}. The
@@
 \]
-The KS statistic $D_n$ in~\eqref{eq:ks_standard}
+The KS statistic $D_n$ in Equation~\eqref{eq:ks_standard}
 is still a good measure of deviation from the null hypothesis. Nonetheless, the
@@
 or AR(1) model with marginal normal (or gamma) distribution. For each AR
-coefficient $\psi \in \{-0.3, 0.1, 0.1, 0.3\}$, we generated 1000
-series of length 100. For each series, we applied the KS statistic
+coefficient $\psi \in \{-0.3, -0.1, 0.1, 0.3\}$, we generated 1000
+series of length 200. For each series, we applied the KS statistic
 in~\eqref{eq:ks_standard} to test $H_0$ that the $X_i$'s follow $N(8, 8)$ (or 
-$\Gamma(8,1)$ marginally. The PP-plots of the p-values from $1000$ replicates 
-for all the $\psi$ values are displayed in Figure~\ref{fig:pp_s}. When
-$\phi$ diverges from 0, the p-values do not look likely to be generated from a 
+$\Gamma(8,1)$) marginally. The PP-plots of the p-values from $1000$ replicates 
+for all the $\psi$ values are displayed in Figure~\ref{fig:pp_s}. As 
+$\phi$ diverges from 0, the p-values look less likely to be generated from a 
 standard uniform distributions. Positive $\psi$ values led to p-values with a 
@@
 hence, conservative tests. Negative $\psi$ values led to p-values with a 
-distributionfunction lower than the standard uniform distribution and, hence, 
-liberal tests. \eds{check previous statement, not consistent with beginning of 
-this section} The larger the magnitude of
-$\psi$, the bigger the deviation from the desired level.
-\eds{check that $\psi=.1$ plots are really from .1 and not 0}
+distribution function lower than the standard uniform distribution and, hence, 
+liberal tests. \eds{the previous two sentences are not consistent with what is 
+written at the beginning of this section. If I am interpreting the plots 
+correctly, then positive $\psi$ leads to p-values that are too low which would
+correspond to liberal tests (consistent with what was written at the beginning 
+of this section).}
 
@@
   \caption{PP-plots for the p-values obtained from KS test with serial
-    dependence discarded and sample size $n = 200$ based on 1000
+    dependence ignored and sample size $n = 200$ based on 1000
     replicates. The data have marginal distributions $N(8, 8)$ and
@@
   Generate $Z_1^*, \ldots, Z_n^*$ from the fitted ARMA$(p, q)$ process with
-  innovation \eds{? inverse?} variance $1 / \sigma^2$ such that the $Z_i$'s are
-	marginally \jy{yes, it means the innovation series of an ARMA process.}
-  standard normal variables.
+  innovation variance $1 / \sigma^2$ such that the $Z_i$'s are
+	marginally standard normal variables.
 \item
@@
 
-\jy{describe the simulation setting here.}
+The semiparametric bootstrap procedure was evaluated in simulation. We 
+considered three true dependence structures on the standard normal scale 
+(ARMA(1, 1), AR(2), and MA(1)) and two marginal distributions 
+($N(8,8)$ and $\Gamma(8,1)$).
+For each dependence structure and marginal distribution combination, we generated 1000 series of length 200.
+For each series, we applied the semiparametric bootstrap procedure with serial
+dependence accounted for through a working ARMA model to test $H_0$ that the 
+$X_i$'s marginally follow their true marginal distribution ($N(8, 8)$ or 
+$\Gamma(8,1)$). Figure~\ref{fig:pp_ss} displays the PP-plots of the 1000 
+p-values for each dependence structure and marginal distribution combination.
+All plots within the figure show the points falling along the diagonal lines, 
+implying that the p-values are coming from standard uniform distributions and 
+that the semiparametric bootstrap procedure is an effective remedy in all cases
+considered.
 
@@
 \item
-  Fir $F_\theta$ to $X_1^*, \ldots, X_n^*$ to obtain estimate $\hat\theta_n^*$
+  Fit $F_\theta$ to $X_1^*, \ldots, X_n^*$ to obtain estimate $\hat\theta_n^*$
   of $\theta$.
@@
   \includegraphics[width=.75\textwidth]{pp_ssf.pdf}
-  \caption{PP-plots for the p-values obtained from KS test without and with
+  \caption{PP-plots for the p-values obtained from KS test without (top) and 
+	  with (bottom)
     serial dependence accounted for and unspecified parameters and sample size
@@
 correction still provides a reasonable approximation that can be useful for
-practical purposes. Figure~\ref{fig:ssd} shows the results of the
-procedure performed on data generated with dependence structures of  MA(1),
-ARMA(1, 1), and AR(2). Naively fitting parameters and not adjusting for
-dependence clearly deviates from a uniform distribution of p-values. Parametric
-bootstrap provides some correction but does not account for dependence, so
-therefore the results of the copula remedy are more accurate and favorable.
+practical purposes. Figure~\ref{fig:pp_ssf} shows the results of the
+procedure performed on data generated with dependence structures of ARMA(1, 1),
+AR(2), and MA(1). Naively fitting parameters and not adjusting for dependence  clearly deviates from a uniform distribution of p-values. 
+Parametric bootstrap provides some correction but does not account for 
+dependence, 
+\eds{just want to verify: you are using parametric bootstrap from Section 2 for
+the top portion of Figure~\ref{fig:pp_ssf}? (Not the totally naive procedure 
+that ignores both issues)} 
+so therefore the results of the copula remedy are more accurate and favorable.
 In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough
@@
 appears to be just far enough from our assumption, showing a limitation of the
-procedure.
+procedure. \eds{I don't think AR(2) looks that bad?}
 
@@
 hypothesis and the power increases as sample size increases. The power from the
-naive tests where the serial dependence is discarded, although the unspecified
-parameters are accounted for, appear to have higher power than the proposed
-tests, but this is not reliable since they do not hold their sizes as
-demonstrated in the Figures.
+naive tests where the serial dependence is ignored, although the unspecified
+parameters are accounted for \eds{i.e., procedure from Section 2?  It may be 
+less confusing if we had a name for the procedure discussed in each section 
+rather than using ``naive'' to describe both levels of ignorance?}, appear to 
+have higher power than the proposed tests, but this is not reliable since they 
+do not hold their sizes as demonstrated in the Figures.
 
@@
 the size of the test. A bias correction is required if the non-parametric form
-is used \citep{babu2004goodness}. In the case of \eds{serially} dependent data, a procedure
-using bootstrap
-with copulas to model dependency shows positive results. When both assumptions
-are violated, i.e., where the data has \eds{serial} dependence and parameters
-must
-be fitted, an adjusted copula procedure also shows positive results. The tests
-appear effective for a variety of families of distributions. The copula remedy
-is not a complete solution and has limitations. Regardless of the true
-dependence, we assume an AR(1) dependence structure. Therefore, if the AR(1)
-dependence structure is a close approximation of the truth, the approach can work.
-However, in cases such as AR(2), if the approximation is too far from the true
-dependence structure the approach does not completely remedy the issue. As well,
-tests were only performed with the normal copula. It is possible that other
-copulas could provide stronger results based on the true dependence of the data.
+is used \citep{babu2004goodness}. In the case of serially dependent data, 
+a procedure using bootstrap with copulas to model dependency shows positive
+results. When both assumptions are violated, i.e., where the data has serial 
+dependence and parameters must be fitted, an adjusted copula procedure also 
+shows positive results. The tests appear effective for a variety of families of 
+distributions. The copula remedy is not a complete solution and has limitations. 
+Regardless of the true dependence, we assume an ARMA(p,q) dependence structure 
+in the procedure in Section~\ref{sec:dependence} and an AR(1) dependence 
+structure in the procedure in Section~\ref{sec:fittedwithdependence}. 
+%Therefore, if the AR(1) dependence structure is a 
+%close approximation of the truth, the approach can work.
+%However, in cases such as AR(2) \eds{I still do not think AR(2) looks bad!}, if 
+%the approximation is too far from the true
+%dependence structure the approach does not completely remedy the issue.
+Therefore, if the assumed dependence structure is a close approximation of the
+truth, the approach can work. However, if the approximation is too far from the 
+true dependence structure the approach does not completely remedy the issue. 
+As well, tests were only performed with the normal copula. It is possible that 
+other copulas could provide stronger results based on the true dependence of the 
+data.
 

### 2023-04-20 manuscript/manuscript.tex
fixed AR(1) confusion in Section 4

@@
 working solution. Section~\ref{sec:fittedwithdependence}
-explores the case where a combination of the first two scenarios occurs.
+explores the case where a combination of the first two scenarios occurs. An  
+adjusted bootstrap procedure is proposed as a working solution in this case.  
 Section~\ref{sec:conclusion} concludes with a discussion.
@@
 
-Similar to Section~\ref{sec:dependence}, the copula approach is not a complete
-solution. Regardless of the true dependence in the data we assume an AR(1)
-dependence structure by taking the lag-1 sample auto-spearman rho. However, we
-can show that as long as the AR(1) assumption is a close approximation, the
-correction still provides a reasonable approximation that can be useful for
-practical purposes. Figure~\ref{fig:pp_ssf} shows the results of the
+Figure~\ref{fig:pp_ssf} shows the results of the
 procedure performed on data generated with dependence structures of ARMA(1, 1),
@@
 so therefore the results of the copula remedy are more accurate and favorable.
-In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough
-to our assumption of AR(1) that the results are reasonable. AR(2) however
-appears to be just far enough from our assumption, showing a limitation of the
-procedure. \eds{I don't think AR(2) looks that bad?}
+%In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough
+%to our assumption of AR(1) that the results are reasonable. AR(2) however
+%appears to be just far enough from our assumption, showing a limitation of the
+%procedure.
+
+Similar to Section~\ref{sec:dependence}, the copula approach is not a complete
+solution. Regardless of the true dependence in the data we assume an ARMA$(p,q)$
+dependence structure. As long as this assumption is a close approximation, the
+correction should still provide a reasonable approximation that can be useful 
+for practical purposes. 
+%Regardless of the true dependence in the data we assume an AR(1)
+%dependence structure by taking the lag-1 sample auto-spearman rho. However, we
+%can show that as long as the AR(1) assumption is a close approximation, the
+%correction still provides a reasonable approximation that can be useful for
+%practical purposes.
 
@@
 distributions. The copula remedy is not a complete solution and has limitations. 
-Regardless of the true dependence, we assume an ARMA(p,q) dependence structure 
-in the procedure in Section~\ref{sec:dependence} and an AR(1) dependence 
-structure in the procedure in Section~\ref{sec:fittedwithdependence}. 
+Regardless of the true dependence, we assume an ARMA($p,q$) dependence structure. 
 %Therefore, if the AR(1) dependence structure is a 
 %close approximation of the truth, the approach can work.
-%However, in cases such as AR(2) \eds{I still do not think AR(2) looks bad!}, if 
+%However, in cases such as AR(2), if 
 %the approximation is too far from the true

### 2023-04-26 manuscript/manuscript.tex
responded to comments

@@
 
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=.5\textwidth]{pp_f.pdf}
+  \caption{PP-plots for the p-values obtained from KS tests with unspecified
+    parameters with sample size $n = 200$ based on 1000 replicates. The data
+    generating models were $N(8, 8)$ and $\Gamma(8, 1)$.
+  }
+  \label{fig:pp_f}
+\end{figure}
+
 We similarly considered random samples $X_1, \ldots, X_n$ 
@@
 The p-value of $D_n$ is approximated by the proportion of the $D_n^*$ 
-statistics that are
-greater than or equal to~$D_n$.
+statistics that are greater than or equal to~$D_n$.
 
@@
 from the parametric bootstrap and, hence, are omitted.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=.5\textwidth]{pp_f.pdf}
-  \caption{PP-plots for the p-values obtained from KS tests with unspecified
-    parameters with sample size $n = 200$ based on 1000 replicates. The data
-    generating models were $N(8, 8)$ and $\Gamma(8, 1)$.
-  }
-  \label{fig:pp_f}
-\end{figure}
 
@@
 
+\jy{how about removing the panels for $-0.1$ and 0.1?}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{pp_s.pdf}
+  \caption{PP-plots for the p-values obtained from KS test with serial
+    dependence ignored and sample size $n = 200$ based on 1000
+    replicates. The data have marginal distributions $N(8, 8)$ and
+    $\Gamma(8, 1)$, with an AR(1) dependence structure on the standard normal
+    scale. The AR coefficients were $\psi \in \{-0.3, -0.1,  0.1,  0.3\}$.
+  }
+  \label{fig:pp_s}
+\end{figure}
+
 The invalidity of the standard statistic for serially dependent data can be
@@
 correspond to liberal tests (consistent with what was written at the beginning 
-of this section).}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{pp_s.pdf}
-  \caption{PP-plots for the p-values obtained from KS test with serial
-    dependence ignored and sample size $n = 200$ based on 1000
-    replicates. The data have marginal distributions $N(8, 8)$ and
-    $\Gamma(8, 1)$, with an AR(1) dependence structure on the standard normal
-    scale. The AR coefficients were $\psi \in \{-0.3, -0.1,  0.1,  0.3\}$.
-  }
-  \label{fig:pp_s}
-\end{figure}
+of this section).} \jy{Need to rephrase. A distribution function higher than
+  another distribution means that it has more smaller values.}
 
@@
 zero, it is necessary to set the intercept of the ARMA model as zero in the
-fitting process. This restriction turned out to be critical in our
+fitting process. This restriction turned out to be critical from our
 investigation; having the intercept estimated does not lead to desired p-value
@@
 
-The semiparametric bootstrap procedure was evaluated in simulation. We 
-considered three true dependence structures on the standard normal scale 
-(ARMA(1, 1), AR(2), and MA(1)) and two marginal distributions 
-($N(8,8)$ and $\Gamma(8,1)$).
-For each dependence structure and marginal distribution combination, we generated 1000 series of length 200.
-For each series, we applied the semiparametric bootstrap procedure with serial
-dependence accounted for through a working ARMA model to test $H_0$ that the 
-$X_i$'s marginally follow their true marginal distribution ($N(8, 8)$ or 
-$\Gamma(8,1)$). Figure~\ref{fig:pp_ss} displays the PP-plots of the 1000 
-p-values for each dependence structure and marginal distribution combination.
-All plots within the figure show the points falling along the diagonal lines, 
-implying that the p-values are coming from standard uniform distributions and 
-that the semiparametric bootstrap procedure is an effective remedy in all cases
-considered.
-
 \begin{figure}[tbp]
@@
 \end{figure}
+
+The semiparametric bootstrap procedure was evaluated in a simulation study. We
+considered two marginal distributions: $N(8,8)$ and $\Gamma(8,1)$. Three
+dependence structures were used to link variables generated from each marginal
+distribution; on the standard normal scale, they are
+ARMA(1, 1) with AR coefficient 0.5 and MA coefficient 0.3;
+AR(2) with coefficients $(0.6, 0.2)$; and
+MA(1)) with coefficient 0.8.
+For each dependence structure and marginal distribution combination, we
+generated 1000 series of length 200.  For each series, we applied the
+semiparametric bootstrap procedure with serial
+dependence accounted for through a working ARMA model to test $H_0$ that the 
+$X_i$'s marginally follow their true marginal distribution ($N(8, 8)$ or 
+$\Gamma(8,1)$). Figure~\ref{fig:pp_ss} displays the PP-plots of the 1000 
+p-values for each dependence structure and marginal distribution combination.
+All plots within the figure show the points falling along the diagonal lines, 
+implying that the p-values are coming from standard uniform distributions and 
+that the semiparametric bootstrap procedure is an effective remedy in all cases
+considered.
 
@@
 
-Figure~\ref{fig:pp_ssf} shows the results of the
-procedure performed on data generated with dependence structures of ARMA(1, 1),
-AR(2), and MA(1). Naively fitting parameters and not adjusting for dependence  clearly deviates from a uniform distribution of p-values. 
-Parametric bootstrap provides some correction but does not account for 
-dependence, 
+Figure~\ref{fig:pp_ssf} shows the PP-plots resulting p-valuess of the
+procedure performed on data generated from same simulation settings as in
+Section~\ref{sec:dependence}. For comparison, we also displayed the PP-plot of
+a naive bootstrap procedure that adjusts for the unspecified parameters as in
+Section~\ref{sec:fitted} but not for the serial dependence. The p-values from
+naively fitting parameters but not adjusting for dependence clearly deviates
+from the standard uniform distribution except in the MA(1) case.
+\jy{needs an explanation ...}
+The super naive approach that does not adjust for fitted parameters nor serial
+dependence would have double sin, so the results are not reported.
 \eds{just want to verify: you are using parametric bootstrap from Section 2 for
 the top portion of Figure~\ref{fig:pp_ssf}? (Not the totally naive procedure 
-that ignores both issues)} 
-so therefore the results of the copula remedy are more accurate and favorable.
-%In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough
-%to our assumption of AR(1) that the results are reasonable. AR(2) however
-%appears to be just far enough from our assumption, showing a limitation of the
-%procedure.
+that ignores both issues)} \jy{Yes}
+Similar to Section~\ref{sec:dependence}, the working normal copula approach
+gives p-values with the desired standard uniform distribution regardless of the
+true dependence.
 
-Similar to Section~\ref{sec:dependence}, the copula approach is not a complete
-solution. Regardless of the true dependence in the data we assume an ARMA$(p,q)$
-dependence structure. As long as this assumption is a close approximation, the
-correction should still provide a reasonable approximation that can be useful 
-for practical purposes. 
-%Regardless of the true dependence in the data we assume an AR(1)
-%dependence structure by taking the lag-1 sample auto-spearman rho. However, we
-%can show that as long as the AR(1) assumption is a close approximation, the
-%correction still provides a reasonable approximation that can be useful for
-%practical purposes.
-
-\begin{table}[ht]
+\begin{table}[tbp]
   \label{tab:power}
@@
 Regardless of the true dependence, we assume an ARMA($p,q$) dependence structure. 
-%Therefore, if the AR(1) dependence structure is a 
-%close approximation of the truth, the approach can work.
-%However, in cases such as AR(2), if 
-%the approximation is too far from the true
-%dependence structure the approach does not completely remedy the issue.
 Therefore, if the assumed dependence structure is a close approximation of the

### 2023-04-27 manuscript/manuscript.tex
responded to responses

@@
 \jy{how about removing the panels for $-0.1$ and 0.1?}
+\eds{seems like too few if those are removed. How about $\{-0.4,-0.2,0.2,0.4\}$
+or $\{-0.30,-0.15,0.15,0.30\}$? Is it easy/quick to generate the plots?}
 
@@
 standard uniform distributions. Positive $\psi$ values led to p-values with a 
-distribution function higher than the standard uniform distribution function and, 
-hence, conservative tests. Negative $\psi$ values led to p-values with a 
-distribution function lower than the standard uniform distribution and, hence, 
-liberal tests. \eds{the previous two sentences are not consistent with what is 
+distribution function higher than the standard uniform distribution function as 
+there were more smaller p-values than expected, and 
+hence, %conservative 
+liberal tests. Negative $\psi$ values led to p-values with a 
+distribution function lower than the standard uniform distribution as there 
+were more larger p-values than expected, and hence, 
+%liberal 
+conservative tests. 
+\eds{the previous two sentences are not consistent with what is 
 written at the beginning of this section. If I am interpreting the plots 
@@
   another distribution means that it has more smaller values.}
+\eds{do the edits fix the problem?}
 
@@
   \]
+	\eds{check placement of * in second F}
 \item
@@
 the last section, here we use $F_{\hat\theta_n}$ and $F_{\hat\theta_n}^*$ in
-place of the known~$F$.
+place of the known~$F$. \eds{check placement of * in second F}
 
@@
 a naive bootstrap procedure that adjusts for the unspecified parameters as in
-Section~\ref{sec:fitted} but not for the serial dependence. The p-values from
+Section~\ref{sec:fitted} but not for the serial dependence. 
+The super naive approach that does not adjust for fitted parameters nor serial
+dependence would have double sin, so the results are not reported. 
+The p-values from
 naively fitting parameters but not adjusting for dependence clearly deviates
@@
 \jy{needs an explanation ...}
-The super naive approach that does not adjust for fitted parameters nor serial
-dependence would have double sin, so the results are not reported.
-\eds{just want to verify: you are using parametric bootstrap from Section 2 for
-the top portion of Figure~\ref{fig:pp_ssf}? (Not the totally naive procedure 
-that ignores both issues)} \jy{Yes}
+\eds{if we had used a different MA parameter other than 0.8, would we see  
+similar behavior?} 
 Similar to Section~\ref{sec:dependence}, the working normal copula approach
@@
 dependent data with marginal distributions $N(8, 8)$ left truncated by zero and
-$\Gamma(8, 1)$. Then, for data from $\Gamma(8, 1)$, we tested $H_0$ that the
+$\Gamma(8, 1)$. 
+\eds{same AR and MA parameters as the previous section?}
+Then, for data from $\Gamma(8, 1)$, we tested $H_0$ that the
 data has marginally a normal distribution; for data from $N(8, 8)$ left
@@
 naive tests where the serial dependence is ignored, although the unspecified
-parameters are accounted for \eds{i.e., procedure from Section 2?  It may be 
-less confusing if we had a name for the procedure discussed in each section 
-rather than using ``naive'' to describe both levels of ignorance?}, appear to 
+parameters are accounted for (i.e., procedure from 
+Section~\ref{sec:dependence}), appear to 
 have higher power than the proposed tests, but this is not reliable since they 

### 2023-04-28 Code/sim-ma.R
ma investigation

@@ -1,0 +1,69 @@
+## library(ggplot2)
+library(qqplotr)
+
+source("tacvfARMA.R")
+source("ksfitted.R")
+
+n <- 200
+nrep <- 1000
+
+### Section 2: fitted distribution
+
+do1rep <- function(n, dist, param) {
+    rdist <- getfndist(dist, param, "r")
+    x <- rdist(n)
+    ks <- ks.test.fitted(x, dist, param = param, fit = TRUE, serial = FALSE)
+    c(ks$p.naive, ks$p.value)
+}
+
+## normal
+n.par <- c(mean = 8, sd = sqrt(8))
+# n.f <- t(replicate(nrep, do1rep(n, "norm", n.par)))
+
+
+## gamma
+g.par <- c(shape = 8, rate = 1)
+# g.f <- t(replicate(nrep, do1rep(n, "gamma", g.par)))
+
+
+## f.data <- data.frame(p = c(n.f, g.f),
+##                      dist = gl(2, nrep * 2, nrep * 4, c("normal", "gamma")),
+##                      meth = gl(2, nrep, nrep * 4, c("naive", "bootstrap")))
+
+save(f.data, file = "f.rda")
+
+### Section 3: serial dependence (but known distribution)
+
+genData <- function(n, phi, theta, qdist) {
+    x <- arima.sim(model = list(ar = phi, ma = theta), n = n)
+    sigma <- sqrt(tacvfARMA.my(phi = phi, theta = - theta, maxLag = 0))
+    qdist(pnorm(x, sd = sigma))
+}
+
+do1rep <- function(n, phi, dist, param) {
+    rdist <- getfndist(dist, param, "r")
+    qdist <- getfndist(dist, param, "q")
+    pdist <- getfndist(dist, param, "p")
+    x <- genData(n,numeric(0), phi, qdist)
+    ks.test(x, pdist)$p.value
+}
+
+n.s.8 <- replicate(nrep, do1rep(n, 0.8, "norm", n.par))
+n.s.4 <- replicate(nrep, do1rep(n, 0.4, "norm", n.par))
+n.s.n4 <- replicate(nrep, do1rep(n, -.4, "norm", n.par))
+n.s.n8 <- replicate(nrep, do1rep(n, -.8, "norm", n.par))
+
+
+g.s.8 <- replicate(nrep, do1rep(n, 0.8, "gamma", n.par))
[…]

### 2023-04-28 Code/ksfitted.R
cleaning

@@ -60,8 +60,8 @@ ks.test.fitted <- function(x, dist, B = 1000, fit = TRUE, serial = FALSE,
         fit.arma <- forecast::auto.arima(z, ic = "aic", max.d = 0, max.D = 0, allowmean = FALSE)
         ## working arma model to preserve serial dependence
         working <- list(ar = fit.arma$model$phi, ma = fit.arma$model$theta)
-        sigma <- sqrt(tacvfARMA.my(phi = working$ar, theta = - working$ma, maxLag = 0))     
-        qdist <- getfndist(dist, param, "q")
+        sigma <- sqrt(tacvfARMA.my(phi = working$ar, theta = - working$ma, maxLag = 0))
+        ## qdist <- getfndist(dist, param, "q")
     }
     ## get observed ks-stat
     ks <- ks.test(x, pdist)
@@ -70,9 +70,8 @@ ks.test.fitted <- function(x, dist, B = 1000, fit = TRUE, serial = FALSE,
     n <- length(x)
     ## bootstrapping
     for (i in 1:B) {
-        if (serial)
-            x.b <- qdist(pnorm(stats::arima.sim(working, n = n), sd = sigma))
-        else x.b <- rdist(n)
+        xb. <- ifelse(serial,  qdist(pnorm(stats::arima.sim(working, n = n), sd = sigma)),
+                      rdist(n))
         if (fit) {
             fitted.b <- MASS::fitdistr(x.b, ddist, start = split(param, names(param)))
             pdist.b <- getfndist(dist, fitted.b$estimate, "p")

### 2023-04-28 Code/sim-ma.R
fixed ma simulation

@@ -26,12 +26,6 @@ g.par <- c(shape = 8, rate = 1)
 # g.f <- t(replicate(nrep, do1rep(n, "gamma", g.par)))
 
 
-## f.data <- data.frame(p = c(n.f, g.f),
-##                      dist = gl(2, nrep * 2, nrep * 4, c("normal", "gamma")),
-##                      meth = gl(2, nrep, nrep * 4, c("naive", "bootstrap")))
-
-save(f.data, file = "f.rda")
-
 ### Section 3: serial dependence (but known distribution)
 
 genData <- function(n, phi, theta, qdist) {
@@ -44,7 +38,7 @@ do1rep <- function(n, phi, dist, param) {
     rdist <- getfndist(dist, param, "r")
     qdist <- getfndist(dist, param, "q")
     pdist <- getfndist(dist, param, "p")
-    x <- genData(n,numeric(0), phi, qdist)
+    x <- genData(n, numeric(0), phi, qdist)
     ks.test(x, pdist)$p.value
 }
 
@@ -54,10 +48,10 @@ n.s.n4 <- replicate(nrep, do1rep(n, -.4, "norm", n.par))
 n.s.n8 <- replicate(nrep, do1rep(n, -.8, "norm", n.par))
 
 
-g.s.8 <- replicate(nrep, do1rep(n, 0.8, "gamma", n.par))
-g.s.4 <- replicate(nrep, do1rep(n, 0.4, "gamma", n.par))
-g.s.n4 <- replicate(nrep, do1rep(n, -.4, "gamma", n.par))
-g.s.n8 <- replicate(nrep, do1rep(n, -.8, "gamma", n.par))
+g.s.8 <- replicate(nrep, do1rep(n, 0.8, "gamma", g.par))
+g.s.4 <- replicate(nrep, do1rep(n, 0.4, "gamma", g.par))
+g.s.n4 <- replicate(nrep, do1rep(n, -.4, "gamma", g.par))
+g.s.n8 <- replicate(nrep, do1rep(n, -.8, "gamma", g.par))
 
 
 
@@ -66,4 +60,38 @@ s.data <- data.frame(p = c(n.s.n8, n.s.n4, n.s.4, n.s.8,
                      dist = gl(2, nrep * 4, nrep * 8, c("normal", "gamma")),
                      rho = gl(4, nrep, nrep * 8, c(-0.8, -0.4, 0.4, 0.8)))
 
-save(s.data, file = "sim-ma.rda")
+
[…]

### 2023-04-28 Code/ksfitted.R
removed typo

@@ -70,7 +70,7 @@ ks.test.fitted <- function(x, dist, B = 1000, fit = TRUE, serial = FALSE,
     n <- length(x)
     ## bootstrapping
     for (i in 1:B) {
-        xb. <- ifelse(serial,  qdist(pnorm(stats::arima.sim(working, n = n), sd = sigma)),
+        xb <- ifelse(serial,  qdist(pnorm(stats::arima.sim(working, n = n), sd = sigma)),
                       rdist(n))
         if (fit) {
             fitted.b <- MASS::fitdistr(x.b, ddist, start = split(param, names(param)))

### 2023-04-28 Code/ksfitted.R
fixed a typo

@@ -70,7 +70,7 @@ ks.test.fitted <- function(x, dist, B = 1000, fit = TRUE, serial = FALSE,
     n <- length(x)
     ## bootstrapping
     for (i in 1:B) {
-        xb <- ifelse(serial,  qdist(pnorm(stats::arima.sim(working, n = n), sd = sigma)),
+        x.b <- ifelse(serial,  qdist(pnorm(stats::arima.sim(working, n = n), sd = sigma)),
                       rdist(n))
         if (fit) {
             fitted.b <- MASS::fitdistr(x.b, ddist, start = split(param, names(param)))

### 2023-04-28 Code/ksfitted.R
replaced ifelse with if else

@@ -70,8 +70,7 @@ ks.test.fitted <- function(x, dist, B = 1000, fit = TRUE, serial = FALSE,
     n <- length(x)
     ## bootstrapping
     for (i in 1:B) {
-        x.b <- ifelse(serial,  qdist(pnorm(stats::arima.sim(working, n = n), sd = sigma)),
-                      rdist(n))
+        x.b <- if(serial) qdist(pnorm(stats::arima.sim(working, n = n), sd = sigma)) else rdist(n)
         if (fit) {
             fitted.b <- MASS::fitdistr(x.b, ddist, start = split(param, names(param)))
             pdist.b <- getfndist(dist, fitted.b$estimate, "p")

### 2023-04-28 Code/sim-ma.R

@@ -83,9 +83,10 @@ ss.data <-data.frame(p = c(n.ma.8, n.ma.4, n.ma.n4, n.ma.n8))
 do1rep <- function(n, phi, theta, dist, param) {
     qdist <- getfndist(dist, param, "q")
     x <- genData(n, phi, theta, qdist)
-    ks.f <- ks.test.fitted(x, dist, fit = TRUE, serial = FALSE, param = param)
-    ks.fs <- ks.test.fitted(x, dist, fit = TRUE, serial = TRUE, param = param)
-    c(ks.f$p.naive, ks.f$p.value, ks.fs$p.value)
+    ks.f <- try(ks.test.fitted(x, dist, fit = TRUE, serial = FALSE, param = param))
+    ks.fs <- try(ks.test.fitted(x, dist, fit = TRUE, serial = TRUE, param = param))
+    c(ifelse(inherits(ks.f, "try-error"), c(NA, NA), c(ks.f$p.naive, ks.f$p.value)),
+      ifelse(inherits(ks.fs, "try-error"), NA, ks.fs$p.value))
 }
 
 n.8 <- t(replicate(nrep, do1rep(n, numeric(0), .8, "norm", n.par)))

### 2023-04-28 Code/sim-ma.R
fixed sim-ma design

@@ -5,7 +5,7 @@ source("tacvfARMA.R")
 source("ksfitted.R")
 
 n <- 200
-nrep <- 1000
+nrep <- 2
 
 ### Section 2: fitted distribution
 
@@ -76,7 +76,9 @@ n.ma.4   <- t(replicate(nrep, do1rep(n, numeric(0), .4, "norm", n.par)))
 n.ma.n4   <- t(replicate(nrep, do1rep(n, numeric(0), -.4, "norm", n.par)))
 n.ma.n8   <- t(replicate(nrep, do1rep(n, numeric(0), -.8, "norm", n.par)))
 
-ss.data <-data.frame(p = c(n.ma.8, n.ma.4, n.ma.n4, n.ma.n8))
+ss.data <-data.frame(p = c(n.ma.8, n.ma.4, n.ma.n4, n.ma.n8),
+                     method = gl(2, nrep, nrep * 8, c("naive", "serial")),
+                     theta = gl(4, nrep * 2, nrep * 4, c(.8, .4, -.4, -.8)))
 
 ## Section 4: fitted parameter and serial dependence
 
@@ -85,14 +87,18 @@ do1rep <- function(n, phi, theta, dist, param) {
     x <- genData(n, phi, theta, qdist)
     ks.f <- try(ks.test.fitted(x, dist, fit = TRUE, serial = FALSE, param = param))
     ks.fs <- try(ks.test.fitted(x, dist, fit = TRUE, serial = TRUE, param = param))
-    c(ifelse(inherits(ks.f, "try-error"), c(NA, NA), c(ks.f$p.naive, ks.f$p.value)),
+    c(if(inherits(ks.f,  "try-error")) c(NA, NA) else c(ks.f$p.naive, ks.f$p.value),
       ifelse(inherits(ks.fs, "try-error"), NA, ks.fs$p.value))
 }
 
 n.8 <- t(replicate(nrep, do1rep(n, numeric(0), .8, "norm", n.par)))
+n.4 <- t(replicate(nrep, do1rep(n, numeric(0), .4, "norm", n.par)))
+n.n4 <- t(replicate(nrep, do1rep(n, numeric(0), -.4, "norm", n.par)))
 n.n8 <- t(replicate(nrep, do1rep(n, numeric(0), -.8, "norm", n.par)))
 
 
-ssf.data <- data.frame(p = c(n.8, n.n8))
+ssf.data <- data.frame(p = c(n.8, n.4, n.n4, n.n8),
[…]

### 2023-04-28 Code/sim-ma.R
nrep to 1000

@@ -5,7 +5,7 @@ source("tacvfARMA.R")
 source("ksfitted.R")
 
 n <- 200
-nrep <- 2
+nrep <- 1000
 
 ### Section 2: fitted distribution
 

### 2023-04-30 Code/sim.R
ar1 coeff changed to (-.4, -.2, .2, .4)

@@ -49,22 +49,20 @@ do1rep <- function(n, rho, dist, param) {
     ks.test(x, pdist)$p.value
 }
 
-n.s.3 <- replicate(nrep, do1rep(n, 0.3, "norm", n.par))
-n.s.1 <- replicate(nrep, do1rep(n, 0.1, "norm", n.par))
-n.s.0 <- replicate(nrep, do1rep(n, numeric(0), "norm", n.par))
-n.s.n1 <- replicate(nrep, do1rep(n, -.1, "norm", n.par))
-n.s.n3 <- replicate(nrep, do1rep(n, -.3, "norm", n.par))
+n.s.4 <- replicate(nrep, do1rep(n, 0.4, "norm", n.par))
+n.s.2 <- replicate(nrep, do1rep(n, 0.2, "norm", n.par))
+n.s.n2 <- replicate(nrep, do1rep(n, -.2, "norm", n.par))
+n.s.n4 <- replicate(nrep, do1rep(n, -.4, "norm", n.par))
 
-g.s.3 <- replicate(nrep, do1rep(n, 0.3, "gamma", g.par))
-g.s.1 <- replicate(nrep, do1rep(n, 0.1, "gamma", g.par))
-g.s.0 <- replicate(nrep, do1rep(n, numeric(0), "gamma", g.par))
-g.s.n1 <- replicate(nrep, do1rep(n, -.1, "gamma", g.par))
-g.s.n3 <- replicate(nrep, do1rep(n, -.3, "gamma", g.par))
+g.s.4 <- replicate(nrep, do1rep(n, 0.4, "gamma", g.par))
+g.s.2 <- replicate(nrep, do1rep(n, 0.2, "gamma", g.par))
+g.s.n2 <- replicate(nrep, do1rep(n, -.2, "gamma", g.par))
+g.s.n4 <- replicate(nrep, do1rep(n, -.4, "gamma", g.par))
 
-s.data <- data.frame(p = c(n.s.n3, n.s.n1, n.s.1, n.s.3,
-                           g.s.n3, g.s.n1, g.s.1, g.s.3),
+s.data <- data.frame(p = c(n.s.n4, n.s.n2, n.s.2, n.s.4,
+                           g.s.n4, g.s.n2, g.s.2, g.s.4),
                      dist = gl(2, nrep * 4, nrep * 8, c("normal", "gamma")),
-                     rho = gl(4, nrep, nrep * 8, c(-0.3, -0.1, 0.1, 0.3)))
[…]

### 2023-04-30 Code/sim-ma.R
typo fix

@@ -78,7 +78,7 @@ n.ma.n8   <- t(replicate(nrep, do1rep(n, numeric(0), -.8, "norm", n.par)))
 
 ss.data <-data.frame(p = c(n.ma.8, n.ma.4, n.ma.n4, n.ma.n8),
                      method = gl(2, nrep, nrep * 8, c("naive", "serial")),
-                     theta = gl(4, nrep * 2, nrep * 4, c(.8, .4, -.4, -.8)))
+                     theta = gl(4, nrep * 2, nrep * 8, c(.8, .4, -.4, -.8)))
 
 ## Section 4: fitted parameter and serial dependence
 

### 2023-04-30 manuscript/manuscript.tex
minor

@@
 or $\{-0.30,-0.15,0.15,0.30\}$? Is it easy/quick to generate the plots?} 
+\jy{Will get jobs done for $\{-0.4,-0.2,0.2,0.4\}$}
 
@@
 \eds{do the edits fix the problem?}
+\jy{can we rephrase ``than excepted'' to ``than there should be'' or something
+  along the line?}
 
@@
   \eds{check placement of * in second F}
+  \jy{the start should be with hat theta from step 3}
 \item
@@
 \eds{if we had used a different MA parameter other than 0.8, would we see  
-similar behavior?} 
+similar behavior?}  \jy{yes. I have more results for other MA coefficients to
+  show when we meet.}
 Similar to Section~\ref{sec:dependence}, the working normal copula approach
@@
 unspecified parameters and serially dependent data. Using the three dependence
-models characterized by ARMA(1, 1), AR(2), and MA(1), we generated serially
+models characterized by ARMA(1, 1), AR(2), and MA(1) in the simulation settings
+in the last section, we generated serially
 dependent data with marginal distributions $N(8, 8)$ left truncated by zero and
 $\Gamma(8, 1)$. 
-\eds{same AR and MA parameters as the previous section?}
+\eds{same AR and MA parameters as the previous section?} \jy{yes; edited.}
 Then, for data from $\Gamma(8, 1)$, we tested $H_0$ that the
@@
 is used \citep{babu2004goodness}. In the case of serially dependent data, 
-a procedure using bootstrap with copulas to model dependency shows positive
+a procedure using bootstrap with the normal copula determined by an
+automatically selected ARMA model to account for dependency shows positive
 results. When both assumptions are violated, i.e., where the data has serial 

### 2023-05-04 manuscript/manuscript.tex
removed resolved comments

@@
 distribution function higher than the standard uniform distribution function as 
-there were more smaller p-values than expected, and 
+there were more smaller p-values than there should be, and 
 hence, %conservative 
@@
 distribution function lower than the standard uniform distribution as there 
-were more larger p-values than expected, and hence, 
+were more larger p-values than there should be, and hence, 
 %liberal 
 conservative tests.
-\eds{the previous two sentences are not consistent with what is 
-written at the beginning of this section. If I am interpreting the plots 
-correctly, then positive $\psi$ leads to p-values that are too low which would
-correspond to liberal tests (consistent with what was written at the beginning 
-of this section).} \jy{Need to rephrase. A distribution function higher than
-  another distribution means that it has more smaller values.}
-\eds{do the edits fix the problem?}
-\jy{can we rephrase ``than excepted'' to ``than there should be'' or something
-  along the line?}
 
@@
 $\Gamma(8, 1)$. 
-\eds{same AR and MA parameters as the previous section?} \jy{yes; edited.}
 Then, for data from $\Gamma(8, 1)$, we tested $H_0$ that the

### 2023-05-05 manuscript/manuscript.tex
remade figures, table, and discussion

@@
 
-\usepackage[pagewise]{lineno}
-%\linenumbers*[1]
+\usepackage[]{lineno}
+\linenumbers*[1]
 % %% patches to make lineno work better with amsmath
@@
 of the test statistic in~\eqref{eq:ks_fitted} except that a bias correction is 
-needed
-\citep{babu2004goodness}. Details of the nonparametric bootstrap procedure are
+needed \citep{babu2004goodness}; see details of the procedure in
 in the Appendix. The results from nonparametric bootstrap are similar to those
@@
 
-\jy{how about removing the panels for $-0.1$ and 0.1?}
-\eds{seems like too few if those are removed. How about $\{-0.4,-0.2,0.2,0.4\}$
-or $\{-0.30,-0.15,0.15,0.30\}$? Is it easy/quick to generate the plots?} 
-\jy{Will get jobs done for $\{-0.4,-0.2,0.2,0.4\}$}
-
 \begin{figure}[tbp]
@@
     $\Gamma(8, 1)$, with an AR(1) dependence structure on the standard normal
-    scale. The AR coefficients were $\psi \in \{-0.3, -0.1,  0.1,  0.3\}$.
+    scale. The AR coefficients were $\psi \in \{-0.4, -0.2,  0.2,  0.4\}$.
   }
@@
 or AR(1) model with marginal normal (or gamma) distribution. For each AR
-coefficient $\psi \in \{-0.3, -0.1, 0.1, 0.3\}$, we generated 1000
+coefficient $\psi \in \{-0.4, -0.2, 0.2, 0.4\}$, we generated 1000
 series of length 200. For each series, we applied the KS statistic
@@
 distribution function higher than the standard uniform distribution function as 
-there were more smaller p-values than there should be, and 
-hence, %conservative 
+there were more smaller p-values than there should be, and hence, 
 liberal tests. Negative $\psi$ values led to p-values with a 
 distribution function lower than the standard uniform distribution as there 
-were more larger p-values than there should be, and hence, 
-%liberal 
-conservative tests.
+were more larger p-values than there should be, and hence, conservative tests.
 
@@
 
-This process is semiparametric because the marginal distribution is
-parametrically specified while the dependence structure of the stationary series
-is only approximated by that of an ARMA process with normal distributions.
+This process is semiparametric because the dependence structure is specified by
+a normal copula determined by an ARMA process with normally distributed errors.
 The closer the approximation is to the truth, the better
@@
   \[
-    D_n^* = \sup_x \lvert F_n^* (x) - F_{\hat\theta_n}^* (x) \rvert.
+    D_n^* = \sup_x \lvert F_n^* (x) - F_{\hat\theta_n^*} (x) \rvert.
   \]
-  \eds{check placement of * in second F}
-  \jy{the start should be with hat theta from step 3}
 \item
@@
 statistics that are greater than or equal to~$D_n$. Compared to the algorithm in
-the last section, here we use $F_{\hat\theta_n}$ and $F_{\hat\theta_n}^*$ in
-place of the known~$F$. \eds{check placement of * in second F}
+the last section, here we use $F_{\hat\theta_n^*}$ in place of the known~$F$.
 
@@
 
-Figure~\ref{fig:pp_ssf} shows the PP-plots resulting p-valuess of the
+Figure~\ref{fig:pp_ssf} shows the PP-plots resulting p-values of the
 procedure performed on data generated from same simulation settings as in
@@
 naively fitting parameters but not adjusting for dependence clearly deviates
-from the standard uniform distribution except in the MA(1) case.
-\jy{needs an explanation ...}
-\eds{if we had used a different MA parameter other than 0.8, would we see  
-similar behavior?}  \jy{yes. I have more results for other MA coefficients to
-  show when we meet.}
+from the standard uniform distribution except in the MA(1) case, where the
+autocorrelation is nonzero with a short memory of only lag~1.
 Similar to Section~\ref{sec:dependence}, the working normal copula approach
@@
 \centering
-\begin{tabular}{llrrrr}
+\begin{tabular}{ll cccc}
   \toprule
@@
   \midrule
-ARMA & naive & 0.40 & 0.66 & 0.52 & 0.78 \\ 
-   & copula & 0.33 & 0.56 & 0.44 & 0.72 \\ 
-  AR & naive & 0.41 & 0.66 & 0.46 & 0.70 \\ 
-   & copula & 0.26 & 0.45 & 0.31 & 0.54 \\ 
-  MA & naive & 0.37 & 0.73 & 0.51 & 0.82 \\ 
-   & copula & 0.34 & 0.69 & 0.49 & 0.80 \\ 
+ARMA & naive & 0.404 & 0.656 & 0.515 & 0.779 \\ 
+ & copula & 0.330 & 0.556 & 0.442 & 0.722 \\ 
+AR & naive & 0.411 & 0.655 & 0.455 & 0.705 \\ 
+& copula & 0.261 & 0.448 & 0.313 & 0.544 \\ 
+MA & naive & 0.374 & 0.728 & 0.514 & 0.817 \\ 
+& copula & 0.343 & 0.693 & 0.487 & 0.797 \\ 
    \bottomrule
@@
 were considered, $n \in \{100, 200\}$. Table~\ref{tab:power} summarizes the
-power of rejecting the null hypothesis at significance level~0.05. The tests
+power of rejecting the null hypothesis at significance level~0.05 from
+1000~replicates. The tests
 based on a working copula have substantial power in rejecting the null
@@
 have higher power than the proposed tests, but this is not reliable since they 
-do not hold their sizes as demonstrated in the Figures.
+do not hold their sizes as demonstrated in the Figure~\ref{fig:pp_ssf}.
 
@@
 
-The KS test has base assumptions that the hypothesized distribution is
-completely specified and the data is independent. When these assumptions are
-violated, the test is no longer accurate and remedies must be performed. In the
-case of fitted parameters, parametric and non-parametric bootstrap can restore
-the size of the test. A bias correction is required if the non-parametric form
-is used \citep{babu2004goodness}. In the case of serially dependent data, 
-a procedure using bootstrap with the normal copula determined by an
-automatically selected ARMA model to account for dependency shows positive
-results. When both assumptions are violated, i.e., where the data has serial 
-dependence and parameters must be fitted, an adjusted copula procedure also 
-shows positive results. The tests appear effective for a variety of families of 
-distributions. The copula remedy is not a complete solution and has limitations. 
-Regardless of the true dependence, we assume an ARMA($p,q$) dependence structure. 
-Therefore, if the assumed dependence structure is a close approximation of the
-truth, the approach can work. However, if the approximation is too far from the 
-true dependence structure the approach does not completely remedy the issue. 
-As well, tests were only performed with the normal copula. It is possible that 
-other copulas could provide stronger results based on the true dependence of the 
-data.
+The three kinds of misuses of the KS test for one-sample goodness-of-fit that we
+demonstrated here are commonly seen in practice. With the aid of computing tools
+such as R, they can be easily demonstrated in classroom teaching. Practitioners
+need to be aware of the assumptions of the standard one-sample KS test that the
+hypothesized distribution is completely specified and that the data are
+independent. When these assumptions are not met, naive applications of the test
+are no longer accurate and remedies must be performed. In the
+case of fitted parameters, parametric and nonparametric bootstrap can restore
+the size of the test. The nonparametric version has long been developed too but
+is lesser known \citep{babu2004goodness}. In the case of serially dependent data,
+our semiparametric bootstrap procedure with a working dependence structure
+controlled by an automatically selected ARMA model restore the size of the test
+for a wide range of dependence structures.
+When both assumptions are violated, i.e., where the data has serial 
+dependence and the parameters must be fitted, a combination of the two
+individual remedies shows good results.
+
+The semiparametric bootstrap procedure with a working ARMA dependence structure
+is not a complete solution and has limitations. When the true serial dependence
+structure cannot be well approximated by an ARMA model with normally distributed
+error terms, the remedy may not restore the size of the test. The working
+dependence structure is essentially the normal copula uniquely determined by the
+ARMA model with normal errors. Some copulas are quite different from the normal
+copula. For example, extreme value copulas have tail dependence, which is not
+provided by normal copulas.
+Using a normal copula to approximate an extreme value copula may not capture the
+true serial dependence structure that is needed to restore the size of the
+test. A block version of the nonparametric bootstrap \citep{babu2004goodness},
+which avoids specification of a working dependence structure, would be more
+desirable.
 
@@
 
-Using the same notations in the text, the procedure is summarized as follows
+Using the same notations in the text, the nonparametric bootstrap procedure of
+\citet{babu2004goodness} is summarized as follows
 \citep{babu2004goodness}.
@@
 \end{document}
-%%% LocalWords: 
+%%% LocalWords: nonparametric semiparametric autocorrelation ARMA
 %%% Local Variables:

### 2023-05-09 manuscript/manuscript.tex
minor

@@
 efficiently addressed by \citet{dimitrova2020computing} with a
-companion R package \textsf{KSgeneral}. Although a common misuse of KS test, the
-issue with discontinuous data is not our focus.
+companion R package \textsf{KSgeneral}. Although a common misuse of the KS test, 
+the issue with discontinuous data is not our focus.
 
@@
 such ways. In fact, using fitted parameters in place of the true parameters in
-KS test has been long known to yield extremely conservative results
+the KS test has been long known to yield extremely conservative results
 \citep[e.g.,][]{lilliefors1967kolmogorov}. This problem can be solved by
@@
 valid, the p-values would be uniformly distributed in the unit
-interval and the points in the PP plot would fall along the diagonal line. 
+interval and the points in the PP-plot would fall along the diagonal line. 
 Clearly, the distribution of the 1000 p-values are very different from what
@@
 hypothesized distribution using the shape and scale maximum likelihood 
-estimates. The PP plot of the p-values from 1000 replications of this 
+estimates. The PP-plot of the p-values from 1000 replications of this 
 experiment are displayed in the bottom left plot of Figure~\ref{fig:pp_f}. The
@@
 of the test statistic in~\eqref{eq:ks_fitted} except that a bias correction is 
-needed \citep{babu2004goodness}; see details of the procedure in
+needed \citep{babu2004goodness}; see details of the procedure
 in the Appendix. The results from nonparametric bootstrap are similar to those
@@
     $\Gamma(8, 1)$, with an AR(1) dependence structure on the standard normal
-    scale. The AR coefficients were $\psi \in \{-0.4, -0.2,  0.2,  0.4\}$.
+    scale. The AR coefficients are $\psi \in \{-0.4, -0.2,  0.2,  0.4\}$.
   }
@@
 $\Gamma(8,1)$) marginally. The PP-plots of the p-values from $1000$ replicates 
-for all the $\psi$ values are displayed in Figure~\ref{fig:pp_s}. As 
-$\phi$ diverges from 0, the p-values look less likely to be generated from a 
+for each $\psi$ value are displayed in Figure~\ref{fig:pp_s}. As 
+$\psi$ diverges from 0, the p-values look less likely to be generated from a 
 standard uniform distributions. Positive $\psi$ values led to p-values with a 
@@
 AR(2) with coefficients $(0.6, 0.2)$; and
-MA(1)) with coefficient 0.8.
+MA(1) with coefficient 0.8.
 For each dependence structure and marginal distribution combination, we
@@
 	  with (bottom)
-    serial dependence accounted for and unspecified parameters and sample size
+    serial dependence accounted for and unspecified parameters; sample size
     $n = 200$ based on
@@
 truncated by zero, we tested $H_0$ that the data has marginally a gamma
-distribution;  In both cases, no parameters were specified. Two sample sizes
+distribution.  In both cases, no parameters were specified. Two sample sizes
 were considered, $n \in \{100, 200\}$. Table~\ref{tab:power} summarizes the
@@
 parameters are accounted for (i.e., procedure from 
-Section~\ref{sec:dependence}), appear to 
-have higher power than the proposed tests, but this is not reliable since they 
+Section~\ref{sec:fitted}), appear to 
+have higher power than the proposed tests, but these are not reliable since they 
 do not hold their sizes as demonstrated in the Figure~\ref{fig:pp_ssf}.
@@
 our semiparametric bootstrap procedure with a working dependence structure
-controlled by an automatically selected ARMA model restore the size of the test
+controlled by an automatically selected ARMA model restores the size of the test
 for a wide range of dependence structures.
@@
   Draw a random sample $X_1^*,...,X_n^*$ from the empirical distribution $F_n$
-  with replacement
+  with replacement.
 \item

### 2023-05-09 manuscript/manuscript.tex
touch up

@@
 the best. When additionally the hypothesized distribution contains unknown
-parameters, the standard KS test becomes even further
-inapplicable. Practitioners, however, may have used the test without knowing its
-limitations \citep[e.g.,][]{tuncer2019online}.
+parameters, the standard KS test becomes even further inapplicable.
 
@@
 
-Using the same notations in the text, the nonparametric bootstrap procedure of
-\citet{babu2004goodness} is summarized as follows
-\citep{babu2004goodness}.
+Using the same notations in the text, the nonparametric bootstrap procedure 
+is summarized as follows \citep{babu2004goodness}.
 \begin{enumerate}
@@
   where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
-  bias term \citep{babu2004goodness}.
+  bias term.
 \item

### 2023-07-30 manuscript/manuscript.tex
addressed comments from TAS and added education twist

@@
 \begin{abstract}
-The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit
-tests for comparing a sample with a hypothesized continuous distribution.
-Nevertheless, it has often been misused. The standard one-sample KS test applies
-to independent, continuous data with a hypothesized distribution that is
-completely specified. It is not uncommon, however, to see in the literature that
-it was applied to dependent, discrete, or rounded data, with hypothesized
-distributions containing estimated parameters. For example, it has been
+The Kolmogorov--Smirnov (KS) test is widely employed to assess the
+goodness-of-fit of a hypothezized continuous distribution to a sample.
+Despite its popularity, the test is frequently in the literature and
+practice. While originally intended for independent, continuous data with
+precisely specified hypothesized distributions, it is erroneously applied to
+scenarios with dependent, discrete, or rounded data, with hypothesized
+distributions requiring estimated parameters. For example, it has been
 ``discovered'' multiple times that the test is too conservative when the 
 hypothesized distribution has parameters that need to be estimated.
+-conservative outcome when estimating such parameters. 
 We demonstrate misuses of the one-sample KS test in
@@
 3) a combination of the first two scenarios.
-For each scenario, we provide remedies for practical applications.
+For each scenario, we provide remedies for practical applications using
+appropriate bootstrap approaches.
+The whole demonstration can be used as hands-on education materials on both
+goodness-of-fit tests and bootstrap.
 
@@
 the KS test when applied to discontinuous distributions. The null distribution
-of the KS statistic is no longer distribution free. Computing the
+of the KS statistic is no longer distribution-free and depends on the
+hypothesized distribution~$F$. Computing the
 exact and asymptotic distribution of $D_n$ is challenging. Fortunately, the null
@@
 modeled by the second-order auto-regressive (AR) process where the AR parameters
-are known. \citet{lanzante2021testing} tests various strategies for dealing with
-temporal
-dependence and concludes that a test based on Monte-Carlo simulations performed
-the best. When additionally the hypothesized distribution contains unknown
+are known. Serial dependence affects the validity of the two-sample KS test too.
+In a recent paper on online diagnosis of performance variation in
+high-performance computing systems, for example, the authors provided no details
+about whether they accounted for serial dependence when applying the two-sample
+KS test \citep{tuncer2019online}. After comparing various strategies for dealing
+with serial dependence, \citet{lanzante2021testing} concludes that a test based
+on Monte-Carlo simulations performed the best.
+When additionally the hypothesized distribution contains unknown
 parameters, the standard KS test becomes even further inapplicable.
@@
 The contribution of this paper is a demonstration of misuses of the one-sample
-KS test in three scenarios and their remedies in practice. The scenarios are
-where:
+KS test in three scenarios and their remedies in practice. Contrary to the
+assumptions within the statistics community that anyone familiar with the
+relevant literature would be ``misusing'' the KS test, there is still a
+considerable journey ahead in educating students and practitioners from diverse
+fields on the proper utilization of the KS test and similar tests. The scenarios
+that we consider are where:
 1) the hypothesized distribution has unspecified parameters;
@@
 have higher power than the proposed tests, but these are not reliable since they 
-do not hold their sizes as demonstrated in the Figure~\ref{fig:pp_ssf}.
+do not hold their sizes as demonstrated in Figure~\ref{fig:pp_ssf}.
 
-\section{Conclusion}
+\section{Concluding Remarks}
 \label{sec:conclusion}
@@
 dependence and the parameters must be fitted, a combination of the two
-individual remedies shows good results.
+individual remedies shows good results. The misuses of the KS tset are also seen
+in practice with other goodness-of-fit tests based on the empirical distribution
+function, such as the Anderson—Darling test or the Cramér—von Mise test, which
+are known to be superior to KS in certain respects \citep{stephens2017tests}. We
+expect that similar bootstrap remedies can be developed. Statisticians living in
+an ivory tower tend to be doubt that anyone would be misusing the KS test as we
+illustrated given that such situations are very well-known in the statistics
+literature. It is our experience, however, that much effort is needed in
+propagating many knowns in the statistics community to the real wild world
+through innovative and impactful education. Such effort may be more valuable
+than developing more advanced methods that no one would use in practice.
 
@@
 is not a complete solution and has limitations. When the true serial dependence
+can be well approximated by an ARMA model, the model selection process could be
+avoided by using a computationally easier and theoretically more attractive
+autoregressive sieve, i.e., autore-gressive models the order of which increases
+simultaneously with the sample size at a suitably slower rate than the sample
+size \citep[e.g.,][]{psaradakis2017distance, psaradakis2020normality}.
+When the true serial dependence
 structure cannot be well approximated by an ARMA model with normally distributed

### 2023-07-31 manuscript/manuscript.tex
minor edits on new content and added blind option

@@
-\documentclass[12pt, letterpaper, titlepage]{article}
+\documentclass[12pt, letterpaper]{article}
+%\documentclass[12pt, letterpaper, titlepage]{article}
 
@@
 
-\title{On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit}
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{1}
 
-\author{Anthony Zeimbekakis\\
+%\title{On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit}
+%
+%\author{Anthony Zeimbekakis\\
+%%   \href{mailto:anthony.zeimbekakis@uconn.edu}
+%% {\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
+  %Elizabeth D.  Schifano\\
+  %Jun Yan\\[1ex]
+  %Department of Statistics, University of Connecticut\\
+%}
+%\date{}
+
+\begin{document}
+%\maketitle
+
+\if0\blind
+{
+  \title{\bf On Misuses of the Kolmogorov--Smirnov Test for One-Sample 
+	Goodness-of-Fit}
+  \author{Anthony Zeimbekakis, %\\
 %   \href{mailto:anthony.zeimbekakis@uconn.edu}
 % {\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
-  Elizabeth Schifano\\
+  Elizabeth D. Schifano, %\\
   Jun Yan\\[1ex]
@@
 \date{}
+  \maketitle
+} \fi
 
-\begin{document}
-\maketitle
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf On Misuses of the Kolmogorov--Smirnov Test for One-Sample 
+	Goodness-of-Fit}
+\end{center}
+  \bigskip
+} \fi
 
@@
 goodness-of-fit of a hypothezized continuous distribution to a sample.
-Despite its popularity, the test is frequently in the literature and
+Despite its popularity, the test is frequently misused in the literature and
 practice. While originally intended for independent, continuous data with
@@
 hypothesized distribution has parameters that need to be estimated.
--conservative outcome when estimating such parameters. 
 We demonstrate misuses of the one-sample KS test in
@@
 \end{abstract}
+
+%\doublespace
 
@@
 assumptions within the statistics community that anyone familiar with the
-relevant literature would be ``misusing'' the KS test, there is still a
+relevant literature would not be ``misusing'' the KS test, there is still a
 considerable journey ahead in educating students and practitioners from diverse
@@
 expect that similar bootstrap remedies can be developed. Statisticians living in
-an ivory tower tend to be doubt that anyone would be misusing the KS test as we
+an ivory tower tend to doubt that anyone would be misusing the KS test as we
 illustrated given that such situations are very well-known in the statistics
@@
 avoided by using a computationally easier and theoretically more attractive
-autoregressive sieve, i.e., autore-gressive models the order of which increases
-simultaneously with the sample size at a suitably slower rate than the sample
-size \citep[e.g.,][]{psaradakis2017distance, psaradakis2020normality}.
+autoregressive sieve, i.e., a sequence of autoregressive models the order of 
+which increases
+simultaneously with the sample size although at a suitably slower rate 
+\citep[e.g.,][]{psaradakis2017distance, psaradakis2020normality}.
 When the true serial dependence

### 2023-07-31 manuscript/manuscript.tex
new closing paragraph on education

@@
 dependence and the parameters must be fitted, a combination of the two
-individual remedies shows good results. The misuses of the KS tset are also seen
-in practice with other goodness-of-fit tests based on the empirical distribution
-function, such as the Anderson—Darling test or the Cramér—von Mise test, which
-are known to be superior to KS in certain respects \citep{stephens2017tests}. We
-expect that similar bootstrap remedies can be developed. Statisticians living in
-an ivory tower tend to doubt that anyone would be misusing the KS test as we
-illustrated given that such situations are very well-known in the statistics
-literature. It is our experience, however, that much effort is needed in
-propagating many knowns in the statistics community to the real wild world
-through innovative and impactful education. Such effort may be more valuable
-than developing more advanced methods that no one would use in practice.
+individual remedies shows good results. The misuses of the KS tset also apply
+to other goodness-of-fit tests based on the empirical distribution
+function, such as the Anderson--Darling test or the Cramér-—von Mise test, which
+are known to be superior to KS in certain respects \citep{stephens2017tests}.
+Similar bootstrap remedies can be developed for these tests.
 
@@
 can be well approximated by an ARMA model, the model selection process could be
-avoided by using a computationally easier and theoretically more attractive
+replaced with
 autoregressive sieve, i.e., a sequence of autoregressive models the order of 
@@
 desirable.
+
+Statisticians living in
+an ivory tower tend to doubt that anyone would be misusing the KS test as we
+illustrated given that such situations are very well-known in the statistics
+literature. It is our experience, however, that much effort is needed in
+propagating many knowns in the statistics community to the real wild world
+through innovative and impactful education. Such effort may be more valuable
+than developing more advanced methods that few people would use in practice.
 

### 2024-03-30 manuscript/manuscript.tex
added classroom implementation at graduate level

@@
 % NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{1}
+\newcommand{\blind}{0}
 
@@
 The Kolmogorov--Smirnov (KS) test is widely employed to assess the
-goodness-of-fit of a hypothezized continuous distribution to a sample.
+goodness-of-fit of a hypothesized continuous distribution to a sample.
 Despite its popularity, the test is frequently misused in the literature and
@@
 smaller effective sample size. For example, for testing normality,
-\citet{durilleul1992lack} demonstrates that a naive application of
+\citet{durilleul1992lack} demonstrate that a naive application of
 the KS statistic is too liberal for medium-to-high positive serial dependence,
@@
 interval and the points in the PP-plot would fall along the diagonal line. 
-Clearly, the distribution of the 1000 p-values are very different from what
+Clearly, the distribution of the 1000 p-values is very different from what
 one would expect to see from 1000 draws from the standard uniform
@@
 respectively ($\Gamma(8,1)$), and sample size $n=200$. These parameter values 
-were selected so that mean and variance of the normal and gamma distributions 
+were selected so that the mean and variance of the normal and gamma distributions 
 in the simulations are the same. Likewise, the p-value of the test 
@@
 is still a good measure of deviation from the null hypothesis. Nonetheless, the
-null distribution of $F_n$ changes when there is serial dependence.
+null distribution changes when there is serial dependence.
 When the serial dependence is
@@
 
+\section{Classroom Implementation}
+
+% Since this is a Teacher's Corner submission, I was hoping to read about how
+% these ideas have been presented in specific courses and also how students
+% reacted to this. What background did the students have? What level of detail was
+% given to them? That is, it is one thing to say "use the bootstrap" and another
+% thing to present to students, e.g., a Markdown file with all necessary code
+% included. Was that done? Were students invited to conduct their own simulations?
+% Etc.
+
+% Graduate level
+The misuses of one-sample KS test can be easily incorporated into graduate level
+classroom teaching for courses that cover parametric bootstrap. For example, at
+the University of Connecticut (UConn), JY has always included a demonstration of
+the misuse under unspecified parameters in STAT 5361, Statistical Computing. The
+catalog description of this course includes is: ``Use of computing for statistical
+problems; obtaining features of distributions, fitting models and implementing
+inference. Basic numerical methods, nonlinear statistical methods, numerical
+integration, modern simulation methods.'' Bootstrap is covered under ``modern
+simulation methods.''  The course is open to graduate students in Statistics,
+others with permission. Detailed R code and graphical illustrations available in
+the open-access course notes elucidate the distinctions between employing null
+hypotheses with and without defined parameters (accessible at:
+\url{https://jun-yan.github.io/stat-5361/boot.html#parametric-bootstrap}).
+Students were able to follow the demonstration closely, gaining a clear
+understanding of the implications of using estimated parameters within test
+statistics, and learning about the efficacy of the parametric bootstrap method
+as a corrective measure.
+
+Supplementary materials accompanying this paper present R code that simplifies
+the illustration of the three common misuses of the one-sample KS test in
+classrooms, whether during lectures or as part of homework assignments.
+Addressing the misuses in contexts of serial dependency necessitates familiarity
+with ARMA models in time series analysis---a prerequisite achievable by most
+statistics graduate students. While incorporating copulas to model dependency
+structures extends beyond conventional statistics curricula, it presents an
+opportunity for advanced exploration in courses focused on statistical computing
+or multivariate analysis.
+
+% Undergraduate level (could mention AZ's undergraduate thesis)
+
 \section{Concluding Remarks}
@@
 dependence and the parameters must be fitted, a combination of the two
-individual remedies shows good results. The misuses of the KS tset also apply
+individual remedies shows good results. The misuses of the KS test also apply
 to other goodness-of-fit tests based on the empirical distribution
@@
 
+\section*{Data Availability Statement}
+An R implementation of the proposed methods will be made publicly available upon 
+publication.
+
 \appendix
 
-\section{Nonparametric Bootstrap for KS Test with Fitted Parameters}
+\section{Appendix: Nonparametric Bootstrap for KS Test with Fitted Parameters}
 

### 2024-04-10 manuscript/manuscript.tex
first pass at UG section - will smooth later

@@
 the misuse under unspecified parameters in STAT 5361, Statistical Computing. The
-catalog description of this course includes is: ``Use of computing for statistical
+catalog description of this course includes: ``Use of computing for statistical
 problems; obtaining features of distributions, fitting models and implementing
@@
 % Undergraduate level (could mention AZ's undergraduate thesis)
+At the undergraduate level, so far only the misuses of one-sample KS test have 
+been presented and demonstrated in a classroom setting. At UConn, ES 
+incorporated this material in STAT 3215, Applied Linear Regression in Data 
+Science, in the context of residual diagnostics and testing whether the 
+externally studentized residuals can be viewed as realizations of a standard 
+normal distribution for large samples. The catalog description of this course 
+states the following topics: ``Applied multiple 
+linear regression analysis in data science, with an emphasis on modern 
+statistical regression methods: simple linear regression and correlation 
+analysis, multiple linear regression, analysis of variance, goodness of fit, 
+comparing regression models through partial and sequential F tests, dummy 
+variables, regression assumptions and diagnostics, model selection and penalized 
+regression, prediction and model validation, principles of design of experiments, 
+one-way and two-way analysis of variance.'' Students in this course are required
+to have taken either two semesters of introductory statistics or a 
+Calculus~2-based statistical methods course as a prerequisite.  While students 
+in the class are exposed to the bootstrap in the context of linear regression 
+models, they are not in general familiar with serially dependency.  Thus, the 
+remedies and more complicated serially dependent settings were not presented at 
+the undergraduate level.  Serial dependence is covered in other
+undergraduate courses, and in fact, the contents of this manuscript were the 
+basis of AZ's undergraduate honors thesis. All concepts are certainly within 
+reach of UConn undergraduate Statistics and Statistical Data Science majors.
 

### 2024-04-16 manuscript/manuscript.tex
more details to UG teaching section

--- 2024-03-30 manuscript/manuscript.tex
@@
 % Undergraduate level (could mention AZ's undergraduate thesis)
+At the undergraduate level, so far only the misuses of one-sample KS test have 
+been presented and demonstrated in a classroom setting. At UConn, ES 
+incorporated this material in STAT 3215, Applied Linear Regression in Data 
+Science, as the one-sample KS test is used in residual diagnostics for testing 
+whether the externally studentized residuals can be viewed as realizations of a 
+standard normal distribution for large samples. %The catalog description of this 
+%course states the following topics: ``Applied multiple 
+%linear regression analysis in data science, with an emphasis on modern 
+%statistical regression methods: simple linear regression and correlation 
+%analysis, multiple linear regression, analysis of variance, goodness of fit, 
+%comparing regression models through partial and sequential F tests, dummy 
+%variables, regression assumptions and diagnostics, model selection and penalized 
+%regression, prediction and model validation, principles of design of experiments, 
+%one-way and two-way analysis of variance.'' 
+Students in this applied linear regression course are required
+to have taken either two semesters of introductory statistics or a 
+Calculus~2-based statistical methods course as a prerequisite. In the KS 
+assignment, students were introduced to a more detailed description of the KS 
+test, and were provided R code and output for a simulation study that showed  
+KS test performance (in terms of the distribution of $p$-values) under a 
+scenario where all KS test assumptions were met (independent, continuous data 
+with precisely specified hypothesized distributions). When the scenario was 
+modified to use estimated parameters instead, the students were asked modify the 
+previous simulation code and show the resulting distribution of $p$-values. The 
+assignment is included in the Supplemental Materials.
+
+While students in this course are exposed to the bootstrap in the 
+context of linear regression models (specifically, case resampling and residual 
+bootstrap), they are not in general familiar with serially dependency. Thus, the 
+remedies and more complicated serially dependent settings were not presented in 
+the undergraduate applied linear regression course. Serial dependence is covered 
+in other undergraduate courses, and in fact, the contents of this manuscript 
+were the basis of AZ's undergraduate honors thesis. Consequently, all 
+statistical concepts and methods employed within this paper are certainly within 
+reach of many UConn undergraduate Statistics and Statistical Data Science 
+majors.
 

### 2024-04-16 Code/UG_KStest_Assignment.Rmd
supplemental UG assignment added

---
title: "Misuse of Kolmogorov-Smirnov One-Sample Goodness of Fit Test"
author: "STAT3215"
date: "Fall 2023"
output:
  pdf_document:
    extra_dependencies:
    - amsmath
    - amssymb
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
The Kolmogorov-Smirnov (KS) test is one of the most popular goodness-of-fit
tests for comparing a sample with a hypothesized parametric distribution. 
We used this test earlier this semester (Note 5) to assess whether the 
(externally) studentized residuals from multiple linear regression can be viewed 
as realizations of a standard normal distribution ($N(0,1)$) for large samples 
($n-p \gg 30$, where $n$ is the sample size and $p$ is the number of regression
parameters in the mean function).

Despite its popularity, the test is frequently misused in the literature and
practice. While originally intended for independent, continuous data with
precisely specified hypothesized distributions, it is erroneously applied to
scenarios with dependent, discrete, or rounded data, with hypothesized
distributions requiring estimated parameters. For example, it has been
``discovered'' multiple times that the test is too conservative when the 
hypothesized distribution has parameters that need to be estimated.  We are 
going to explore this scenario in more detail below.

## KS Test Details

Let $X_1, ..., X_n$ be a random sample of size $n$ from a continuous
distribution. The null hypothesis $H_0$ is that $X_i$'s follow distribution $F$.
Let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function. The KS test statistic is
$$D_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.$$
The asymptotic distribution of $D_n$ under $H_0$ is independent of the
distribution $F$.  Critical values have been tabulated for large and 
small samples alike with popular statistical software packages readily able to 
provide associated p-values. In particular, the KS test is available as function 
\texttt{ks.test()} in R package \textsf{stats}.

This standard one-sample KS test applies to independent data with a continuous
hypothesized distribution that is completely specified (meaning the parameters
of the hypothesized distribution are known and not estimated). When the 
hypothesized distribution $F$ contains unspecified parameters, as is
the case in most goodness-of-fit test settings, the standard KS test is not
applicable.  We will illustrate this below with a small simulation study.

## Illustration

### Simulation when KS test conditions are met

We first consider a simulation when the KS test conditions are met, namely, that 
the hypothesized distribution of independent data is continuous and completely 
specified. In this illustration, the hypothesized distribution $F$ is a normal
distribution with both mean and variance parameters set equal to 8 ($N(8,8)$).

We will evaluate the performance of the standard KS test when the null hypothesis 
is true by repeating the following steps $B=10000$ times:

1. Generate a sample of $n=200$ independent observations from a $N(8,8)$ distribution.

2. Perform the standard KS test on the sample generated in Step 1 by calling the
\texttt{ks.test()} function with known hypothesized distribution $N(8,8)$.

3. Save and store the p-value reported from Step 2.

We run these steps in the code below and then plot a histogram of the resulting $B=10000$ p-values.

```{r, fig.height = 3, fig.width = 3.5, fig.align = "center", fig.cap="\\label{fig:hist}Histogram of p-values when KS test conditions are met."}
do1rep <- function(n) {
    x <- rnorm(n, mean = 8, sd = sqrt(8))
    ks <- ks.test(x, "pnorm", mean = 8, sd = sqrt(8))
    ks$p.value
}

n <- 200   # sample size
B <- 10000 # number of simulation replicates

set.seed(0)  # for reproducibility
pvals <- replicate(B, do1rep(n))

hist(pvals, main="")
```

Recall that for each replication, we generated the data so that the null 
hypothesis of the KS test is true. Because the test is being performed under the 
appropriate conditions, the test should be valid in the sense that the resulting 
p-values should have a continuous uniform distribution on the unit interval 
($U(0,1)$). Indeed, the histogram in Figure \ref{fig:hist} reflects this. This 
also means that if we set the significance level at $\alpha=0.05$ so that we
reject $H_0$ when p-value$<\alpha$, this false rejection should happen in 
approximately 5\% of the $B=10000$ simulations. We compute the proportion of 
false rejections from this simulation with the code below.  
```{r}
mean(pvals<0.05)
```

### Assignment: Simulation when KS Conditions are NOT met

We will now consider a simulation when the KS test conditions are NOT met, 
namely, that the hypothesized distribution of independent data is continuous, 
but the parameters of the hypothesized distribution are unknown to the 
researcher, and are replaced with estimated values.  Your assignment is to 
evaluate the performance of the standard KS test under this scenario.

Specifically, you will modify the simulation code from the previous section to 
perform the following four steps, repeated $B=10000$ times:

1. Generate a sample of $n=200$ independent observations from a $N(8,8)$ 
distribution.

2. Estimate the sample mean, $\bar{x}$ and the sample variance, $s^2$, of the sample 
generated in Step 1 using the \texttt{mean()} and \texttt{var()} functions, 
respectively.

3. Perform the standard KS test on the sample generated in Step 1 by calling the
\texttt{ks.test()} function with hypothesized distribution $N(\bar{x},s^2)$.

4. Save and store the p-value reported from Step 3.

After repeating Steps 1-4 $B=10000$ times, plot a histogram of the p-values. If 
the test remains valid when using estimated parameters in the hypothesized 
distribution, we would expect the p-values to uniformly distribute on the unit 
interval as they did in the first simulation (Figure \ref{fig:hist}) and that 
the probability of false rejection of the null hypothesis is the significance 
level $\alpha$.

Do the p-values appear uniformly distributed in the unit interval here, or is 
the distribution skewed to the left or right?

Report the proportion of false rejections in this simulation using significance 
level $\alpha=0.05.$

### 2024-04-17 manuscript/reply.tex
response to reviewers now included in repo

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{natbib}
\usepackage{hyperref}

\usepackage{listings}
\usepackage{rotating, graphicx}
\graphicspath{{./}, {./image/}}
\usepackage{booktabs, natbib}
% \usepackage{breakurl}
% \usepackage [english]{babel}
\usepackage{amsmath, amsbsy, amsthm, epsfig, epsf, psfrag, graphicx, 
amssymb, enumerate}
\usepackage{bm}
\usepackage{multirow, multicol}

\usepackage[dvipsnames]{color}
\definecolor{darkblue}{rgb}{0.1, 0.2, 0.6}

\newcommand{\jy}[1]{\textcolor{red}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{blue}{(EDS: #1)}}
\newcommand{\mc}[1]{\textcolor{green}{(MC: #1)}}

\sloppy

% \usepackage{csquotes}
% \usepackage [autostyle, english = american]{csquotes}
% \MakeOuterQuote{"}

% \usepackage{bibentry}
\newenvironment{comment}%
{\begin{quotation}\noindent\small\it\color{darkblue}\ignorespaces%
}{\end{quotation}}

\begin{document}

\begin{center}
  {\Large\bf Response to the Comments}
\end{center}

We extend our gratitude to the Editor and Associate Editor for 
granting us the opportunity to revise this manuscript. We also want to
express our appreciation to the reviewer for their valuable comments.

The manuscript has been revised accordingly with the most notable change being 
the addition of Section 5 (Classroom Implementation). We believe this revision 
has enhanced the both the quality and utility of this paper.

Point-by-point responses to the comments are as follows, with the
comments quoted in \emph{\color{darkblue} italic and blue}.

\subsection*{To Associate Editor}

\begin{comment}
In this article, the author explains how the Kolmogorov-Smirnov (KS) test is 
often misused in practice and show through simulation, that under the null 
hypothesis the KS p-value is very likely to not have a uniform distribution if 
the parameters are estimated from the data or when the data are serial 
correlated. The authors also give solutions to correct the test in both of these 
situations using the parametric or semiparametric bootstrap.

I found the article informative and well written as the problem and proposed 
solutions were clearly explained and demonstrated. It seemed to me there is 
possibly enough there to warrant publishing the article. However, as it was 
submitted to Teacher’s corner, I wanted an opinion on the value of the article
as a teaching tool.

Therefore, the article was reviewed by one referee who is an educator and could 
assess the impact and usefulness on teaching (I tried for two, but that proved 
hard to come by). This referee also found the article clear and well written, 
but wanted the authors to include a detailed explanation of how to present
this material to students and where/how to include it in the course material.

It would seem that this could be taught while teaching statistical tests and 
methods as a clear warning to students to always assess how well their data fits 
the assumptions of the method. But how to present this? It sounds like, from the 
referee’s opinion, that this would require significant work. One way to do this 
is if the author included a new section dedicated to the implementing of this 
method in the classroom. As the rest of the article seems clear and informative, 
the rest of paper could be left mostly unchanged.
\end{comment}

Thank you very much for your encouraging comments and great suggestion.  
We have now included a new section, \textit{Section 5 Classroom Implementation},
that discusses how elements of this manuscript have been incorporated into both 
graduate- and undergraduate-level teaching at the authors' home university.

For blinding purposes, course numbers, author initials and websites, and 
university name have been redacted, but all this information appears in the 
unblinded version.  In brief, this material has been covered at the graduate
level in a statistical computing course, open to all graduate students in 
Statistics and others with permission, that covers the bootstrap. Detailed R 
code and graphical illustrations were provided to students in the open-access 
course notes to elucidate the distinctions between employing null
hypotheses with and without defined parameters.  This link is included in the 
unblinded version of the paper. \eds{Not sure how we can blind your github 
website for the submission unless we actually don't include it in the blinded 
version. Could we print to PDF the relevant section of the notes and include as 
a supplement for review purposes?}

Similarly at the undergraduate-level, students in an R-based applied regression 
course were provided with an R Markdown file with simulation code in order to 
demonstrate how the KS test fails with estimated parameters in the hypothesized 
distribution. The R Markdown file that was provided to students is included in 
the Supplemental Materials. This R-based applied linear regression course are 
has the following prerequisites: two semesters of introductory statistics OR a 
Calculus~2-based statistical methods course.

At both the graduate and undergraduate level, students were able to follow the 
demonstrations closely and gain a clear understanding of the implications of 
using estimated parameters within test statistics.  At the graduate level, 
students further were able to appreciate the efficacy of the parametric 
bootstrap method as a corrective measure.

\subsection*{To Reviewer}

\begin{comment}
In this paper we read about a misfit between the KS test as it was developed and 
how it is often used in practice. The author shows, via simulation, that the KS 
p-value does not have a uniform distribution (as it should) when H0 is true but 
parameters are estimated from the data, nor when there is serial correlation 
(or both). At least we see this for two settings: the normal and the gamma. The 
problem is clearly presented, as is the solution (use of the parametric or 
semiparametric bootstrap).
\end{comment}

Thank you for this encouraging comment.

\begin{comment}
The figures are easy to read and convey the necessary information. (It would 
help if Table 1 appeared on page 14, rather than page 13.)
\end{comment}

This is a very good point.  We have moved the location of Table 1 to be closer 
to the end of Section 4 (page 15 in the revised manuscript).

\begin{comment}
Since this is a Teacher's Corner submission, I was hoping to read about how 
these ideas have been presented in specific courses and also how students 
reacted to this. What background did the students have? What level of detail 
was given to them? That is, it is one thing to say "use the bootstrap" and 
another thing to present to students, e.g., a Markdown file with all necessary
code included. Was that done? Were students invited to conduct their own 
simulations? Etc.
\end{comment}

Thank you for highlighting this important omission. Taking the suggestion of the 
Associate Editor, we have now included a new section, Section 5 Classroom 
Implementation, that discusses how elements of
this manuscript have been incorporated into both graduate- and 
undergraduate-level teaching at the authors' home university. 
Please see our response to the Associate Editor for additional details.

%\bibliographystyle{chicago}
%\bibliography{citations}

\end{document}

### 2024-04-17 manuscript/manuscript.tex
added blinded version of section 5

@@
 % NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{0}
+\newcommand{\blind}{1}
 
@@
 
+Finally, we report a small study of the power of the one-sample KS test with
+unspecified parameters and serially dependent data. Using the three dependence
+models characterized by ARMA(1, 1), AR(2), and MA(1) in the simulation settings
+in the last section, we generated serially
+dependent data with marginal distributions $N(8, 8)$ left truncated by zero and
+$\Gamma(8, 1)$. 
+Then, for data from $\Gamma(8, 1)$, we tested $H_0$ that the
+data has marginally a normal distribution; for data from $N(8, 8)$ left
+truncated by zero, we tested $H_0$ that the data has marginally a gamma
+distribution.  In both cases, no parameters were specified. Two sample sizes
+were considered, $n \in \{100, 200\}$. Table~\ref{tab:power} summarizes the
+power of rejecting the null hypothesis at significance level~0.05 from
+1000~replicates. The tests
+based on a working copula have substantial power in rejecting the null
+hypothesis and the power increases as sample size increases. The power from the
+naive tests where the serial dependence is ignored, although the unspecified
+parameters are accounted for (i.e., procedure from 
+Section~\ref{sec:fitted}), appear to 
+have higher power than the proposed tests, but these are not reliable since they 
+do not hold their sizes as demonstrated in Figure~\ref{fig:pp_ssf}.
+
 \begin{table}[tbp]
@@
 
-Finally, we report a small study of the power of the one-sample KS test with
-unspecified parameters and serially dependent data. Using the three dependence
-models characterized by ARMA(1, 1), AR(2), and MA(1) in the simulation settings
-in the last section, we generated serially
-dependent data with marginal distributions $N(8, 8)$ left truncated by zero and
-$\Gamma(8, 1)$. 
-Then, for data from $\Gamma(8, 1)$, we tested $H_0$ that the
-data has marginally a normal distribution; for data from $N(8, 8)$ left
-truncated by zero, we tested $H_0$ that the data has marginally a gamma
-distribution.  In both cases, no parameters were specified. Two sample sizes
-were considered, $n \in \{100, 200\}$. Table~\ref{tab:power} summarizes the
-power of rejecting the null hypothesis at significance level~0.05 from
-1000~replicates. The tests
-based on a working copula have substantial power in rejecting the null
-hypothesis and the power increases as sample size increases. The power from the
-naive tests where the serial dependence is ignored, although the unspecified
-parameters are accounted for (i.e., procedure from 
-Section~\ref{sec:fitted}), appear to 
-have higher power than the proposed tests, but these are not reliable since they 
-do not hold their sizes as demonstrated in Figure~\ref{fig:pp_ssf}.
-
 \section{Classroom Implementation}
@@
 
+\if0\blind
+{
 % Graduate level
@@
 previous simulation code and show the resulting distribution of $p$-values. The 
-assignment is included in the Supplemental Materials.
+assignment is included in the Supplemental Materials. Students were able to
+properly simulate and correctly produce results indicating the conservative 
+nature of the test under these conditions.
 
@@
 majors. 
+} \fi
+
+\if1\blind
+{
+% Graduate level
+The misuses of one-sample KS test can be easily incorporated into graduate level
+classroom teaching for courses that cover parametric bootstrap. For example, at
+the University of XX, YY has always included a demonstration of the misuse under 
+unspecified parameters in STAT $\#\#\#\#$, XXXX. The
+catalog description of this course includes: ``Use of computing for statistical
+problems; obtaining features of distributions, fitting models and implementing
+inference. Basic numerical methods, nonlinear statistical methods, numerical
+integration, modern simulation methods.'' Bootstrap is covered under ``modern
+simulation methods.''  The course is open to graduate students in Statistics,
+others with permission. Detailed R code and graphical illustrations available in
+the open-access course notes elucidate the distinctions between employing null
+hypotheses with and without defined parameters (accessible at: 
+\textit{author YY's github website}).
+%\url{https://jun-yan.github.io/stat-5361/boot.html#parametric-bootstrap}).
+Students were able to follow the demonstration closely, gaining a clear
+understanding of the implications of using estimated parameters within test
+statistics, and learning about the efficacy of the parametric bootstrap method
+as a corrective measure.
+
+Supplementary materials accompanying this paper present R code that simplifies
+the illustration of the three common misuses of the one-sample KS test in
+classrooms, whether during lectures or as part of homework assignments.
+Addressing the misuses in contexts of serial dependency necessitates familiarity
+with ARMA models in time series analysis---a prerequisite achievable by most
+statistics graduate students. While incorporating copulas to model dependency
+structures extends beyond conventional statistics curricula, it presents an
+opportunity for advanced exploration in courses focused on statistical computing
+or multivariate analysis.
+
+% Undergraduate level (could mention AZ's undergraduate thesis)
+At the undergraduate level, so far only the misuses of one-sample KS test have 
+been presented and demonstrated in a classroom setting. At XX, ZZ 
+incorporated this material in STAT $\#\#\#\#$, XXXX, as the one-sample KS test 
+is used in residual diagnostics for testing 
+whether the externally studentized residuals can be viewed as realizations of a 
+standard normal distribution for large samples. %The catalog description of this 
+%course states the following topics: ``Applied multiple 
+%linear regression analysis in data science, with an emphasis on modern 
+%statistical regression methods: simple linear regression and correlation 
+%analysis, multiple linear regression, analysis of variance, goodness of fit, 
+%comparing regression models through partial and sequential F tests, dummy 
+%variables, regression assumptions and diagnostics, model selection and penalized 
+%regression, prediction and model validation, principles of design of experiments, 
+%one-way and two-way analysis of variance.'' 
+Students in this applied linear regression course are required
+to have taken either two semesters of introductory statistics or a 
+Calculus~2-based statistical methods course as a prerequisite. In the KS 
+assignment, students were introduced to a more detailed description of the KS 
+test, and were provided R code and output for a simulation study that showed  
+KS test performance (in terms of the distribution of $p$-values) under a 
+scenario where all KS test assumptions were met (independent, continuous data 
+with precisely specified hypothesized distributions). When the scenario was 
+modified to use estimated parameters instead, the students were asked modify the 
+previous simulation code and show the resulting distribution of $p$-values. The 
+assignment is included in the Supplemental Materials. Students were able to
+properly simulate and correctly produce results indicating the conservative 
+nature of the test under these conditions.
+
+While students in this course are exposed to the bootstrap in the 
+context of linear regression models (specifically, case resampling and residual 
+bootstrap), they are not in general familiar with serially dependency. Thus, the 
+remedies and more complicated serially dependent settings were not presented in 
+the undergraduate applied linear regression course. Serial dependence is covered 
+in other undergraduate courses, and in fact, the contents of this manuscript 
+were the basis of WW's undergraduate honors thesis. Consequently, all 
+statistical concepts and methods employed within this paper are certainly within 
+reach of many XX undergraduate Statistics and Data Science majors. 
+} \fi
 

### 2024-04-29 Code/UG_KStest_Assignment.Rmd
blinding

@@
 title: "Misuse of Kolmogorov-Smirnov One-Sample Goodness of Fit Test"
-author: "STAT3215"
+author: "STAT XXXX"
 date: "Fall 2023"

### 2024-04-29 manuscript/TAS_cover_revision.tex
add cover, minor typo fixes to ms and reply

% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
%\topmargin=-0.0in    % Make letterhead start about 1 inch from top of page
%\textheight=8.5in  % text height can be bigger for a longer letter
%\oddsidemargin=0pt % leftmargin is 1 inch
%\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\usepackage[margin=1in]{geometry}

\begin{document}

\signature{Elizabeth D. Schifano \\elizabeth.schifano@uconn.edu \\Corresponding Author}           % name for signature
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{

\textit{The American Statistician} Manuscript Revision}

\begin{flushleft}
{\large\bf Elizabeth D. Schifano, Ph.D.}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill University of Connecticut \\
\hfill Department of Statistics \\ 
\hfill 215 Glenbrook Road U-4120 \\
\hfill Storrs, CT 06269
\end{flushright}
\vfill % forces letterhead to top of page

%\vspace{-2in}
\opening{Dear members of the \textit{The American Statistician} editorial team:}
\vspace{.25in}

\noindent Thank you for the opportunity to revise and resubmit the manuscript 
entitled ``On Misuses of the Kolmogorov–Smirnov Test 
for One-Sample Goodness-of-Fit'' (TAS-23-210) for possible publication in 
\emph{The American Statistician}.\\

We have now included a new section in the revised manuscript, \textit{Section 5 
Classroom Implementation}, that discusses how elements of this manuscript have 
been incorporated into both graduate- and undergraduate-level teaching at the 
authors' home university.

We have also included Supplemental Materials that include an \texttt{R} 
implementation of the proposed methods, as well as teaching materials at the 
undergraduate and graduate level. \\

We hope that you continue to find this manuscript to be a valuable contribution 
to the Teacher's Corner in the \emph{The American Statistician}. Please inform 
me if I can provide any additional information or assistance.  
\\

Thank you very much for your continued consideration. I look forward to hearing 
from you.\\

\closing{Best regards,}

~~\\
%\encl{Online Updating of Statistical Inference in the Big Data Setting\\~~~ Supplemental Material}  				% Enclosures

\end{letter}

\end{document}

### 2024-04-29 manuscript/manuscript.tex
add cover, minor typo fixes to ms and reply

@@
 hypotheses with and without defined parameters (accessible at: 
-\textit{author YY's github website}).
+\textit{author YY's github website; material printed to pdf for blinded review}).
 %\url{https://jun-yan.github.io/stat-5361/boot.html#parametric-bootstrap}).
@@
 \section*{Data Availability Statement}
-An R implementation of the proposed methods will be made publicly available upon 
-publication.
+An R implementation of the proposed methods as well as teaching materials are  
+included in the Supplementary Materials.
 

### 2024-04-29 manuscript/reply.tex
add cover, minor typo fixes to ms and reply

@@
 hypotheses with and without defined parameters.  This link is included in the 
-unblinded version of the paper. \eds{Not sure how we can blind your github 
-website for the submission unless we actually don't include it in the blinded 
-version. Could we print to PDF the relevant section of the notes and include as 
-a supplement for review purposes?}
+unblinded version of the paper; for the blinded review, we printed the 
+relevant portion of the notes to pdf and included this blinded pdf file in the 
+Supplemental Materials. %\eds{Not sure how we can blind your github 
+%website for the submission unless we actually don't include it in the blinded 
+%version. Could we print to PDF the relevant section of the notes and include as 
+%a supplement for review purposes?}
 
@@
 distribution. The R Markdown file that was provided to students is included in 
-the Supplemental Materials. This R-based applied linear regression course are 
+the Supplemental Materials. This R-based applied linear regression course 
 has the following prerequisites: two semesters of introductory statistics OR a 

### 2024-06-13 manuscript/TAS-template.tex
put table label after caption

--- 2024-04-16 manuscript/manuscript.tex
@@
-\documentclass[12pt, letterpaper]{article}
-%\documentclass[12pt, letterpaper, titlepage]{article}
-
+\documentclass[12pt]{article}
 \usepackage{amsmath}
-\usepackage{booktabs}
 \usepackage{amsthm}
 \usepackage{graphicx}
-\usepackage[margin=1in]{geometry}
+\usepackage{enumerate}
+\usepackage{natbib}
+%\usepackage{url} % not crucial - just used below for the URL 
+\usepackage{booktabs}
 \usepackage{hyperref}
 \hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
-\usepackage{natbib}
 \usepackage{enumitem}
-\usepackage{setspace}
 
-\usepackage[]{lineno}
-\linenumbers*[1]
-% %% patches to make lineno work better with amsmath
-\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
- \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
- \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
- \renewenvironment{#1}%
- {\linenomath\csname old#1\endcsname}%
- {\csname oldend#1\endcsname\endlinenomath}}%
-\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
- \patchAmsMathEnvironmentForLineno{#1}%
- \patchAmsMathEnvironmentForLineno{#1*}}%
-
-\AtBeginDocument{%
- \patchBothAmsMathEnvironmentsForLineno{equation}%
- \patchBothAmsMathEnvironmentsForLineno{align}%
- \patchBothAmsMathEnvironmentsForLineno{flalign}%
- \patchBothAmsMathEnvironmentsForLineno{alignat}%
- \patchBothAmsMathEnvironmentsForLineno{gather}%
- \patchBothAmsMathEnvironmentsForLineno{multline}%
-}
-
-% control floats
-\renewcommand\floatpagefraction{.9}
-\renewcommand\topfraction{.9}
-\renewcommand\bottomfraction{.9}
-\renewcommand\textfraction{.1}
-\setcounter{totalnumber}{50}
-\setcounter{topnumber}{50}
-\setcounter{bottomnumber}{50}
-
-\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
-\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
-
+%\pdfminorversion=4
 % NOTE: To produce blinded version, replace "0" with "1" below.
@@
 
-%\title{On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit}
-%
-%\author{Anthony Zeimbekakis\\
-%%   \href{mailto:anthony.zeimbekakis@uconn.edu}
-%% {\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
-  %Elizabeth D.  Schifano\\
-  %Jun Yan\\[1ex]
-  %Department of Statistics, University of Connecticut\\
-%}
-%\date{}
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
 
 \begin{document}
-%\maketitle
+
+%\bibliographystyle{natbib}
+
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 	Goodness-of-Fit}
-  \author{Anthony Zeimbekakis, %\\
+  \author{Anthony Zeimbekakis\\
 %   \href{mailto:anthony.zeimbekakis@uconn.edu}
 % {\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
-  Elizabeth D. Schifano, %\\
+  Elizabeth D. Schifano\\
   Jun Yan\\[1ex]
@@
 }
-\date{}
   \maketitle
@@
 \end{center}
-  \bigskip
+  \medskip
 } \fi
 
-\doublespace
-
+\bigskip
 \begin{abstract}
-The Kolmogorov--Smirnov (KS) test is widely employed to assess the
-goodness-of-fit of a hypothesized continuous distribution to a sample.
-Despite its popularity, the test is frequently misused in the literature and
-practice. While originally intended for independent, continuous data with
-precisely specified hypothesized distributions, it is erroneously applied to
-scenarios with dependent, discrete, or rounded data, with hypothesized
-distributions requiring estimated parameters. For example, it has been
+The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit
+tests for comparing a sample with a hypothesized continuous distribution.
+Nevertheless, it has often been misused. The standard one-sample KS test applies
+to independent, continuous data with a hypothesized distribution that is
+completely specified. It is not uncommon, however, to see in the literature that
+it was applied to dependent, discrete, or rounded data, with hypothesized
+distributions containing estimated parameters. For example, it has been
 ``discovered'' multiple times that the test is too conservative when the 
@@
 3) a combination of the first two scenarios.
-For each scenario, we provide remedies for practical applications using
-appropriate bootstrap approaches.
-The whole demonstration can be used as hands-on education materials on both
-goodness-of-fit tests and bootstrap.
-
-\bigskip
-\noindent{\sc Keywords}:
-nonparametric bootstrap;
-parametric bootstrap;
-working dependence.
+For each scenario, we provide remedies for practical applications.
 \end{abstract}
 
-%\doublespace
+\noindent%
+{\it Keywords:}  nonparametric bootstrap; parametric bootstrap;
+working dependence.
+\vfill
 
+\newpage
+\spacingset{1.45} % DON'T change the spacing!
 \section{Introduction}
@@
 the KS test when applied to discontinuous distributions. The null distribution
-of the KS statistic is no longer distribution-free and depends on the
-hypothesized distribution~$F$. Computing the
+of the KS statistic is no longer distribution free. Computing the
 exact and asymptotic distribution of $D_n$ is challenging. Fortunately, the null
@@
 smaller effective sample size. For example, for testing normality,
-\citet{durilleul1992lack} demonstrate that a naive application of
+\citet{durilleul1992lack} demonstrates that a naive application of
 the KS statistic is too liberal for medium-to-high positive serial dependence,
@@
 modeled by the second-order auto-regressive (AR) process where the AR parameters
-are known. Serial dependence affects the validity of the two-sample KS test too.
-In a recent paper on online diagnosis of performance variation in
-high-performance computing systems, for example, the authors provided no details
-about whether they accounted for serial dependence when applying the two-sample
-KS test \citep{tuncer2019online}. After comparing various strategies for dealing
-with serial dependence, \citet{lanzante2021testing} concludes that a test based
-on Monte-Carlo simulations performed the best.
-When additionally the hypothesized distribution contains unknown
+are known. \citet{lanzante2021testing} tests various strategies for dealing with
+temporal
+dependence and concludes that a test based on Monte-Carlo simulations performed
+the best. When additionally the hypothesized distribution contains unknown
 parameters, the standard KS test becomes even further inapplicable.
@@
 The contribution of this paper is a demonstration of misuses of the one-sample
-KS test in three scenarios and their remedies in practice. Contrary to the
-assumptions within the statistics community that anyone familiar with the
-relevant literature would not be ``misusing'' the KS test, there is still a
-considerable journey ahead in educating students and practitioners from diverse
-fields on the proper utilization of the KS test and similar tests. The scenarios
-that we consider are where:
+KS test in three scenarios and their remedies in practice. The scenarios are
+where:
 1) the hypothesized distribution has unspecified parameters;
@@
 variance (with $n$ in the denominator). This experiment was repeated 1000 times
-and the probability-probability plot (PP-plot) of the 1000 p-values are 
+and the probability-probability plot (PP-plot) of the 1000 p-values is 
 displayed in the top left plot of Figure~\ref{fig:pp_f}. If the test were
@@
 
-\begin{figure}[tbp]
+\begin{figure}
   \centering
@@
 were selected so that the mean and variance of the normal and gamma distributions 
-in the simulations are the same. Likewise, the p-value of the test 
+were the same in the simulations. Likewise, the p-value of the test 
 statistic~$D_n$ in~\eqref{eq:ks_fitted} was obtained by naively calling the
@@
 estimates. The PP-plot of the p-values from 1000 replications of this 
-experiment are displayed in the bottom left plot of Figure~\ref{fig:pp_f}. The
+experiment is displayed in the bottom left plot of Figure~\ref{fig:pp_f}. The
 p-values are again non-uniformly distributed due to the use of the 
@@
 
-Figure~\ref{fig:pp_ssf} shows the PP-plots resulting p-values of the
-procedure performed on data generated from same simulation settings as in
-Section~\ref{sec:dependence}. For comparison, we also displayed the PP-plot of
+Figure~\ref{fig:pp_ssf} shows the resulting PP-plots of p-values from the
+procedure performed on data generated from the same simulation settings as in
+Section~\ref{sec:dependence}. For comparison, we also display the PP-plots from
 a naive bootstrap procedure that adjusts for the unspecified parameters as in
@@
 The p-values from
-naively fitting parameters but not adjusting for dependence clearly deviates
+naively fitting parameters but not adjusting for dependence clearly deviate
 from the standard uniform distribution except in the MA(1) case, where the
@@
 \begin{table}[tbp]
-  \label{tab:power}
   \caption{Power of rejecting the null hypothesis of normal and gamma
@@
     $\Gamma(8, 1)$ and $N(8, 8)$, respectively. }
+  \label{tab:power}
 \centering
@@
 
-\section{Classroom Implementation}
-
-% Since this is a Teacher's Corner submission, I was hoping to read about how
-% these ideas have been presented in specific courses and also how students
-% reacted to this. What background did the students have? What level of detail was
-% given to them? That is, it is one thing to say "use the bootstrap" and another
-% thing to present to students, e.g., a Markdown file with all necessary code
-% included. Was that done? Were students invited to conduct their own simulations?
-% Etc.
-
-% Graduate level
-The misuses of one-sample KS test can be easily incorporated into graduate level
-classroom teaching for courses that cover parametric bootstrap. For example, at
-the University of Connecticut (UConn), JY has always included a demonstration of
-the misuse under unspecified parameters in STAT 5361, Statistical Computing. The
-catalog description of this course includes: ``Use of computing for statistical
-problems; obtaining features of distributions, fitting models and implementing
-inference. Basic numerical methods, nonlinear statistical methods, numerical
-integration, modern simulation methods.'' Bootstrap is covered under ``modern
-simulation methods.''  The course is open to graduate students in Statistics,
-others with permission. Detailed R code and graphical illustrations available in
-the open-access course notes elucidate the distinctions between employing null
-hypotheses with and without defined parameters (accessible at:
-\url{https://jun-yan.github.io/stat-5361/boot.html#parametric-bootstrap}).
-Students were able to follow the demonstration closely, gaining a clear
-understanding of the implications of using estimated parameters within test
-statistics, and learning about the efficacy of the parametric bootstrap method
-as a corrective measure.
-
-Supplementary materials accompanying this paper present R code that simplifies
-the illustration of the three common misuses of the one-sample KS test in
-classrooms, whether during lectures or as part of homework assignments.
-Addressing the misuses in contexts of serial dependency necessitates familiarity
-with ARMA models in time series analysis---a prerequisite achievable by most
-statistics graduate students. While incorporating copulas to model dependency
-structures extends beyond conventional statistics curricula, it presents an
-opportunity for advanced exploration in courses focused on statistical computing
-or multivariate analysis.
-
-% Undergraduate level (could mention AZ's undergraduate thesis)
-At the undergraduate level, so far only the misuses of one-sample KS test have 
-been presented and demonstrated in a classroom setting. At UConn, ES 
-incorporated this material in STAT 3215, Applied Linear Regression in Data 
-Science, as the one-sample KS test is used in residual diagnostics for testing 
-whether the externally studentized residuals can be viewed as realizations of a 
-standard normal distribution for large samples. %The catalog description of this 
-%course states the following topics: ``Applied multiple 
-%linear regression analysis in data science, with an emphasis on modern 
-%statistical regression methods: simple linear regression and correlation 
-%analysis, multiple linear regression, analysis of variance, goodness of fit, 
-%comparing regression models through partial and sequential F tests, dummy 
-%variables, regression assumptions and diagnostics, model selection and penalized 
-%regression, prediction and model validation, principles of design of experiments, 
-%one-way and two-way analysis of variance.'' 
-Students in this applied linear regression course are required
-to have taken either two semesters of introductory statistics or a 
-Calculus~2-based statistical methods course as a prerequisite. In the KS 
-assignment, students were introduced to a more detailed description of the KS 
-test, and were provided R code and output for a simulation study that showed  
-KS test performance (in terms of the distribution of $p$-values) under a 
-scenario where all KS test assumptions were met (independent, continuous data 
-with precisely specified hypothesized distributions). When the scenario was 
-modified to use estimated parameters instead, the students were asked modify the 
-previous simulation code and show the resulting distribution of $p$-values. The 
-assignment is included in the Supplemental Materials.
-
-While students in this course are exposed to the bootstrap in the 
-context of linear regression models (specifically, case resampling and residual 
-bootstrap), they are not in general familiar with serially dependency. Thus, the 
-remedies and more complicated serially dependent settings were not presented in 
-the undergraduate applied linear regression course. Serial dependence is covered 
-in other undergraduate courses, and in fact, the contents of this manuscript 
-were the basis of AZ's undergraduate honors thesis. Consequently, all 
-statistical concepts and methods employed within this paper are certainly within 
-reach of many UConn undergraduate Statistics and Statistical Data Science 
-majors.
-
-\section{Concluding Remarks}
+\section{Conclusion}
 \label{sec:conclusion}
@@
 dependence and the parameters must be fitted, a combination of the two
-individual remedies shows good results. The misuses of the KS test also apply
-to other goodness-of-fit tests based on the empirical distribution
-function, such as the Anderson--Darling test or the Cramér-—von Mise test, which
-are known to be superior to KS in certain respects \citep{stephens2017tests}.
-Similar bootstrap remedies can be developed for these tests.
+individual remedies shows good results.
 
@@
 is not a complete solution and has limitations. When the true serial dependence
-can be well approximated by an ARMA model, the model selection process could be
-replaced with
-autoregressive sieve, i.e., a sequence of autoregressive models the order of 
-which increases
-simultaneously with the sample size although at a suitably slower rate 
-\citep[e.g.,][]{psaradakis2017distance, psaradakis2020normality}.
-When the true serial dependence
 structure cannot be well approximated by an ARMA model with normally distributed
@@
 
-Statisticians living in
-an ivory tower tend to doubt that anyone would be misusing the KS test as we
-illustrated given that such situations are very well-known in the statistics
-literature. It is our experience, however, that much effort is needed in
-propagating many knowns in the statistics community to the real wild world
-through innovative and impactful education. Such effort may be more valuable
-than developing more advanced methods that few people would use in practice.
-
-\section*{Data Availability Statement}
-An R implementation of the proposed methods will be made publicly available upon 
-publication.
-
 \appendix
 
-\section{Appendix: Nonparametric Bootstrap for KS Test with Fitted Parameters}
+\section{Nonparametric Bootstrap for KS Test with Fitted Parameters}
 
@@
 \bibliography{citations}
-
 \end{document}
-%%% LocalWords: nonparametric semiparametric autocorrelation ARMA
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% ispell-personal-dictionary: ".aspell.en.pws"
-%%% fill-column: 80
-%%% eval: (auto-fill-mode 1)
-%%% End:
